### 2015-09-23 ijar-npb-ms.tex
first actual commit

\documentclass[authoryear, 12pt, a4paper]{elsarticle}

% ------------ packages -------------

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{url}
%\usepackage{tikz}
%\usetikzlibrary{shapes.misc,fit}

% ------------ custom defs -------------

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}

\newcommand{\indic}{\mathbb{I}}

\newcommand{\ber}{\operatorname{Bernoulli}} 
\newcommand{\bin}{\operatorname{Binomial}}
\newcommand{\be}{\operatorname{Beta}} 
\newcommand{\bebin}{\operatorname{Beta-binomial}}

\def\tmax{t_\text{max}}
\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\input{nydefs.tex}

%\newcommand{\comments}[1]{{\small\color{gray} #1}}

% ------------ options -------------

\allowdisplaybreaks

%\biboptions{longnamesfirst,angle,semicolon}

\journal{IJAR}

\begin{document}

% ------------ frontmatter -------------

\begin{frontmatter}
\title{IJAR Bayesian Nonparametrics Special Issue Manuscript}

\author[oxf]{Louis J.M. Ashlett}
\ead{louis.aslett@stats.ox.ac.uk}
\author[dur]{Frank P.A. Coolen}
\ead{frank.coolen@durham.ac.uk}
\author[ein]{Gero Walter}
\ead{g.m.walter@tue.nl}

\address[oxf]{Department of Statistics, University of Oxford, Oxford, UK}
\address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}
\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}

\begin{abstract}
Imprecise Bayesian nonparametric approach to system reliability with multiple types of components,
sets of priors through sets of canonical parameters,
leading to sets of system reliability functions,
reflection of prior-data conflict
\end{abstract}

\begin{keyword}
System reliability \sep
Survival signature \sep
Imprecise probability \sep
Bayesian Nonparametrics \sep
Prior-data conflict
\end{keyword}
\end{frontmatter}

% ------------ manuscript -------------

(alphabetical author order, final order to be discussed of course)

\section{Introduction}

System with components of $k=1,\ldots,K$ different types.
There are $m_k$ components of type $k$ in the system.
Components of the same type are i.i.d.\ and independent of components of other types.
Arbitrary system layout, i.e.\ any series / parallel combination, $k$ out of $n$ etc.

\section{Survival Signature}

Alternative to system signature that allows for
straightforward computation of system relaibility $\Rsys(t) = P(\Tsys > t)$
for multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.

Can be seen as applying the law of total probability by partitioning
according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) 
\end{align*}

\section{Nonparametric Bayesian Approach}

The random failure time of component number $i$ of type $k$ is denoted by $T^k_i$, $i = 1, \ldots m_k$.
For its distribution, written in terms of the cdf $F^k(t) = P(T^k_i \le t)$
or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
we consider a set of time points $t$.

For each time point $t$, the functioning of a single component of type $k$ at time $t$ (functioning: 1, failed: 0)
is Bernoulli distributed with a suitable functioning probability (as, $1-$ failure probability) $p^k_t$,
$\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$.

Then, the number of functioning components out of the $m_k$ components of type $k$
is binomial distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.

The set of functioning probabilities $p^k_t$
corresponding to a choosen set of time points ($t \in \{t_1, \ldots, \tmax\}$)
defines a discrete failure time distribution for components of type $k$,
$R^k(t) = p^k_{t_j}$, $t \in [t_j, t_{j+1})$.

***or say we don't know for times between time points, or lower and upper bound already here?***

The $p^k_t$'s could be such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
The only strict constraint is that $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).

However, directly choosing $p^k_t$'s is hard,
and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
To account for this uncertainty, one can express knowledge on $p^k_t$'s though a prior distribution.
A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$.

in terms of $\nz$, $\yz$

posterior, posterior predictive for $C^k_t$

***Illustration prior-data conflict?

\section{Sets of Priors}

***do we need to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{t_j} \ge \yzu_{t_{j+1}}$?
I would say no, and for relatively dense $t$ grids, neighbouring intervals should be overlapping.
What about requiring $\yzu_{t_j} \ge \yzu_{t_{j+1}}$ and $\yzl_{t_j} \ge \yzl_{t_{j+1}}$?
This might not hold for the case when we know, e.g., pretty much what's going on for low $t$
but want to be much more cautious for high $t$.***

\section{Computations}

\section{Example}

\section{Conclusions}

\end{document}

### 2015-09-27 ijar-npb-ms.tex
prior predictive

@@
 
+Based on expert assumptions and data for component failure distribution,
+we calculate the system reliability function $\Rsys(t) = P(\Tsys > t)$.
+
 \section{Survival Signature}
@@
 Alternative to system signature that allows for
-straightforward computation of system relaibility $\Rsys(t) = P(\Tsys > t)$
+straightforward computation of system reliability
 for multiple component types.
@@
  &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
-                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) 
+                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
+ &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
+                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
 \end{align*}
@@
 Then, the number of functioning components out of the $m_k$ components of type $k$
-is binomial distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.
+is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.
 
@@
 
-The $p^k_t$'s could be such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
+(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
+or the NPI bounds for Kaplan-Meier?)
+
+The $p^k_t$'s can be chosen such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
 The only strict constraint is that $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).
 
-However, directly choosing $p^k_t$'s is hard,
+However, directly choosing the $p^k_t$'s is hard,
 and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
-To account for this uncertainty, one can express knowledge on $p^k_t$'s though a prior distribution.
-A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$.
+To account for this uncertainty, one can express knowledge on $p^k_t$ through a prior distribution.
+A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
+leading to the posterior being again Beta:
+
+Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
+at any fixed time $t$ this results in the observation from the Binomial model described above,
+$s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
+The posterior is then $p^k_t \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
+
+The posterior predictive distribution for the number of components surviving at time $t$
+of the $m_k$ components in the system, based on the tifetime data and the prior information,
+is then Beta-binomial distributed,
+$C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
+That is, we have
+\begin{align*}
+P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \alpha^k_t + s^k_t, m_k - l_k + \beta^k_t + n_k - s^k_t)}
+                                                    {B(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)} \,,
+\end{align*}
+where $B(\cdot, \cdot)$ is the beta function.
 
@@
 
-posterior, posterior predictive for $C^k_t$
-
-***Illustration prior-data conflict?
+***Illustration prior-data conflict with $\bebin$?
 

### 2015-09-27 ijar-npb-ms.tex
nz and yz parametrization

@@
 The set of functioning probabilities $p^k_t$
-corresponding to a choosen set of time points ($t \in \{t_1, \ldots, \tmax\}$)
+corresponding to a choosen set of time points ($t \in {\cal T} = \{t_1, \ldots, \tmax\}$)
 defines a discrete failure time distribution for components of type $k$,
@@
 
-in terms of $\nz$, $\yz$
+For each component type $k$, we have to choose $2 \times |{\cal T}|$
+parameters to specify the prior distribution for the discrete survival function of $T^k_i$,
+so in total $2 \times |{\cal T}| \times K$ parameters.
 
-***Illustration prior-data conflict with $\bebin$?
+Let us drop the super- and subscript $k$ and $t$ for a while
+to discuss the role and interpretation of the parameters $\alpha$ and $\beta$
+for each $k$ and $t$.
+The Beta distribution is usually parametrized in terms of $\alpha$ and $\beta$ as used above, 
+but for our generalization to sets of priors,
+we suggest to use a different parametrization in terms of $\nz$, $\yz$:
+\begin{align*}
+\nz &= \alpha + \beta &
+\yz &= \frac{\alpha}{\alpha + \beta} \,,
+\end{align*}
+or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
+From the properties of the Beta distribution,
+we see that $\yz$ is the prior mean for the functioning probability $p$,
+and the higher $\nz$, the more probability weight will be concentrated around that mean.
+Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
+this will be illustrated through revisting the posterior
+based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$:
+
+$p \mid s$ is Beta distributed with the updated parameters
+\begin{align*}
+\nn &= \nz + n &
+\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
+\end{align*}
+so after seeing that $s$ out of $n$ components function (at time $t$),
+the posterior mean $\yn$ for $p$ is a weighted average of
+the prior mean $\yz$ and $s/n$ (the fraction of function components in the data),
+with the weights $\nz$ and $n$, respectively.
+We see that $\nz$ plays the same role for the prior mean $\yz$
+as the sample size $n$ for the observed mean $s/n$,
+thus the notion of pseudocount.
+Also, the higher $\nz$, the higher the weight for $\yz$
+in the weighted average calculation of $\yn$,
+so $\nz$ gives the strength of the prior as compared to the sample size $n$.
+%The parameters $\nz$ and $\yz$ have a more intuitive interprtation,
+
+The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$
+is therefore
+\begin{align*}
+P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn\yn, m_k - l_k + \nn(1-\yn))}
+                                                    {B(\nn\yn, \nn(1-\yn))} \,.
+\end{align*}
+
+The reparametrization enables us to see that in the conjugate setting,
+learning from data amounts to averaging between prior and data.
+While this allows for the tractability of the model,
+it also comes with a serious drawback:
+When prior and data are
+
+***Illustration prior-data conflict with $\bebin$
 

### 2015-09-28 ijar-npb-ms.tex
sets of priors

@@
 
+\author[ein]{Gero Walter}
+\ead{g.m.walter@tue.nl}
 \author[oxf]{Louis J.M. Ashlett}
@@
 \ead{frank.coolen@durham.ac.uk}
-\author[ein]{Gero Walter}
-\ead{g.m.walter@tue.nl}
 
+\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}
 \address[oxf]{Department of Statistics, University of Oxford, Oxford, UK}
 \address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}
-\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}
 
@@
 
-(alphabetical author order, final order to be discussed of course)
+(author order to be discussed of course)
 
@@
 
+***Right-censored observations maybe in a second step?
+Minimal assumption (component can fail immediately after censoring or live forever)
+will lead to high imprecision,
+assumption of exchangeability with other components at moment of censoring
+will be quite complex, maybe too much for this paper,
+and could be covered in a second paper with extensive use-case?***
+
 The $p^k_t$'s can be chosen such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
-The only strict constraint is that $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).
+
+***Constraint: $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).***
 
@@
 A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
-leading to the posterior being again Beta:
+leading to the posterior being again Beta.
 
@@
 The posterior is then $p^k_t \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
+The combination of a Binomial observation model with a Beta prior is often called Beta-binomial model.
 
 The posterior predictive distribution for the number of components surviving at time $t$
-of the $m_k$ components in the system, based on the tifetime data and the prior information,
-is then Beta-binomial distributed,
+of the $m_k$ components in the system, based on the lifetime data and the prior information,
+is then a so-called Beta-binomial distribution,
 $C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
@@
 
+The posterior predictive basically averages over $p^k_t \in [0,1]$,
+weighted with the posterior on $p^k_t$.
+
 For each component type $k$, we have to choose $2 \times |{\cal T}|$
@@
 so in total $2 \times |{\cal T}| \times K$ parameters.
+
+***main contribution of the paper besides the set of priors thing:
+guidelines on how to choose the parameters?***
 
@@
 but for our generalization to sets of priors,
-we suggest to use a different parametrization in terms of $\nz$, $\yz$:
+it is useful to consider a different parametrization in terms of $\nz$, $\yz$:
 \begin{align*}
@@
 From the properties of the Beta distribution,
-we see that $\yz$ is the prior mean for the functioning probability $p$,
-and the higher $\nz$, the more probability weight will be concentrated around that mean.
+we see that $\yz = \E[p]$ is the prior mean for the functioning probability $p$,
+and that the higher $\nz$, the more probability weight will be concentrated around that mean,
+as $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
 Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
-this will be illustrated through revisting the posterior
+this will be illustrated through revisiting the posterior
 based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$:
@@
 
-The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$
+The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$,
+now again with indicators $t$ and $k$,
 is therefore
 \begin{align*}
-P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn\yn, m_k - l_k + \nn(1-\yn))}
-                                                    {B(\nn\yn, \nn(1-\yn))} \,.
+P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
+                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
 \end{align*}
@@
 it also comes with a serious drawback:
-When prior and data are
+When observed data are very much different from what is assumed in the prior,
+this conflict is simply averaged out,
+and is not reflected in the posterior or the posterior predictive.
 
-***Illustration prior-data conflict with $\bebin$
+***Illustration of such prior-data conflict with $\bebin$ distribution:
+different priors updated to same posterior,
+or same prior updated to different posteriors with same variance,
+show corresponding $C^k_t$ distribution.***
 
@@
 
-***do we need to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{t_j} \ge \yzu_{t_{j+1}}$?
-I would say no, and for relatively dense $t$ grids, neighbouring intervals should be overlapping.
-What about requiring $\yzu_{t_j} \ge \yzu_{t_{j+1}}$ and $\yzl_{t_j} \ge \yzl_{t_{j+1}}$?
+As shown in Walter \& Augustin (2009),
+we can have both tractability and meaningful reaction to prior-data conflict
+by using sets of priors $\MktZ$ produced by parameter set $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
+Then we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.
+
+Lower and upper bounds for $\Rsys(t)$ by min and max over $\PZ_{1,t}, \ldots, \PZ_{K,t}$.
+
+Monotonicity in $\yz_{k,t}$, so we get
+\begin{align*}
+\lRsys(t)
+ &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} \Rsys(t) \\
+ &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
+    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
+                                                 \prod_{k=1}^K P(C^k_t = l_k \mid s^k_t) \\
+ &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
+    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \\ & \hspace*{12ex}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
+                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,.
+\end{align*}
+
+***do we need to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$?
+I would say no, and for relatively dense $t$ grids, neighbouring intervals should be able to overlap after all.
+What about requiring $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$?
 This might not hold for the case when we know, e.g., pretty much what's going on for low $t$
@@
 \section{Computations}
+
+***publish code as seperate \textbf{R} package, or include in Louis' package \texttt{ReliabilityTheory}
+(which contains the function to calculate the survival signature)***
 

### 2015-09-29 ijar-npb-ms.tex
some more stuff

@@
 
+***e.g., what to do in extreme tail of component distributions?
+How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***
+
 Let us drop the super- and subscript $k$ and $t$ for a while
@@
 by using sets of priors $\MktZ$ produced by parameter set $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
-Then we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.
+For such a rectangular prior parameter set $\PktZ$,
+the posterior parameter set $\PktN$ is not rectangular anymore.
+
+In case of no prior-data conflict ($s^k_t/n^k_t \in [\yktzl, \yktzu]$),
+the set shrinks in the $\ykt$ dimension
+(how much it shrinks depends on $\nktz$, leading to the so-called spotlight shape),
+leading to smaller $\Rsys(t)$ intervals.
+
+In case of prior-data conflict ($s^k_t/n^k_t \not\in [\yktzl, \yktzu]$),
+$\PktN$ has the so-called banana shape,
+giving a wider $\yktn$ interval as compared to the non-conflict case. 
+As a consequence, we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.
 
@@
 
+***Will ask Simme Douwe Flapper (Prof at TU Eindhoven) for real-world example,
+otherwise some toy example will do.***
+
+Show $\Rsys(t)$ intervals for prior-data conflict and non-conflict data
+to show effect of prior-data conflict.
+
+Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
+or show effect of replacement of failed components in a system
+(replaced components constitute a new type with shifted component reliability function)
+
 \section{Conclusions}

### 2015-10-20 ijar-npb-ms.tex
minor changes sec1-3

@@
 
+(some sentences may be useful for the abstract)
+
 System with components of $k=1,\ldots,K$ different types.
@@
 Based on expert assumptions and data for component failure distribution,
-we calculate the system reliability function $\Rsys(t) = P(\Tsys > t)$.
+the goal is to calculate the system reliability function $\Rsys(t) = P(\Tsys > t)$.
+Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
+naturally a Bayesian model for the functioning probability at each time point arises.
+To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict,
+we propose an impürecise or interval probability approach
+based on sets of prior distributions defined through sets of canonical parameters.
+
+Our method produces a set of discrete system reliability functions,
+or, for each time point $t$, an interval for the system survival probability
+that appropriately reflects uncertainty due to vague prior information, the amount of data, and prior-data conflict.
 
@@
 
-Alternative to system signature that allows for
-straightforward computation of system reliability
-for multiple component types.
+The survival signature allows for straightforward computation of system reliability
+for systems with complex layouts and multiple component types.
 It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.
@@
 or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
-we consider a set of time points $t$.
+we consider a set of time points $t$, $t \in {\cal T} = \{t_1, \ldots, \tmax\}$.
 
 For each time point $t$, the functioning of a single component of type $k$ at time $t$ (functioning: 1, failed: 0)
-is Bernoulli distributed with a suitable functioning probability (as, $1-$ failure probability) $p^k_t$,
-$\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$.
+is Bernoulli distributed with a suitable functioning probability (as, $1-$failure probability) $p^k_t$, so
+\begin{align*}
+P\big(\indic(T^k_i > t) = 1\big) &= p^k_t\,, \\
+P\big(\indic(T^k_i > t) = 0\big) &= 1 - p^k_t\,,
+\end{align*}
+in short, $\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$.
 
-Then, the number of functioning components out of the $m_k$ components of type $k$
+Then, due to the assumption of independence of components of the same type, 
+the number of functioning components out of the $m_k$ components of type $k$
 is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.
@@
 ***or say we don't know for times between time points, or lower and upper bound already here?***
+***illustrate with a graph?***
 
-(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
-or the NPI bounds for Kaplan-Meier?)
+%(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
+%or the NPI bounds for Kaplan-Meier?)
+%
 
-***Right-censored observations maybe in a second step?
-Minimal assumption (component can fail immediately after censoring or live forever)
-will lead to high imprecision,
-assumption of exchangeability with other components at moment of censoring
-will be quite complex, maybe too much for this paper,
-and could be covered in a second paper with extensive use-case?***
-
-The $p^k_t$'s can be chosen such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
-
-***Constraint: $p^k_{t_j} \ge p^k_{t_{j+1}}$ must hold (assuming no repair).***
+The $p^k_t$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
+Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).***
 
@@
 Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
-at any fixed time $t$ this results in the observation from the Binomial model described above,
+at any fixed time $t \in {\cal T}$ this results in the observation from the Binomial model described above,
 $s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
@@
 
-***main contribution of the paper besides the set of priors thing:
-guidelines on how to choose the parameters?***
-
-***e.g., what to do in extreme tail of component distributions?
-How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***
-
 Let us drop the super- and subscript $k$ and $t$ for a while
@@
 but for our generalization to sets of priors,
-it is useful to consider a different parametrization in terms of $\nz$, $\yz$:
+it is useful to consider a different parametrization in terms of $\nz$ and $\yz$, where
 \begin{align*}
 \nz &= \alpha + \beta &
+&\text{and} &
 \yz &= \frac{\alpha}{\alpha + \beta} \,,
@@
 or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
+$\nz$ and $\yz$ are sometimes known as the \emph{canonical} parameters,
+identified from rewriting the density in a canonical form.
+(This canonical form gives a joint structure to all conjugate priors.)
+
 From the properties of the Beta distribution,
-we see that $\yz = \E[p]$ is the prior mean for the functioning probability $p$,
+we see that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
 and that the higher $\nz$, the more probability weight will be concentrated around that mean,
@@
 \begin{align*}
-\nn &= \nz + n &
+\nn &= \nz + n\,, &
 \yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
@@
 
+***main contribution of the paper besides the set of priors thing:
+guidelines on how to choose the parameters?***
+
+***e.g., what to do in extreme tail of component distributions?
+How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***
+
 \section{Computations}
@@
 
+Also calculate $\Rsys(t)$ intervals for vacuous prior ($[\yktzl, \yktzu] = [0,1]$, some fixed $\nktz$)?***
+
 Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
@@
 
-\section{Conclusions}
+\section{Conclusions and Outlook}
+
+Extend the model to deal with right-censored observations which are common in realibility setting.
+We assume that a minimal assumption (component can fail immediately after censoring or live forever)
+will be simple to implememt but will lead to high imprecision,
+whereas assuming exchangeability with other components at moment of censoring
+will be more complex to accomodate but will lead to les imprecision.
 

### 2015-10-20 ijar-npb-ms.tex
extended set of prior workings in sec4, minor changes in rest

@@
 $p \mid s$ is Beta distributed with the updated parameters
-\begin{align*}
+\begin{align}
 \nn &= \nz + n\,, &
 \yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
-\end{align*}
+\label{eq:nyupdate}
+\end{align}
 so after seeing that $s$ out of $n$ components function (at time $t$),
@@
 
-As shown in Walter \& Augustin (2009),
+As was shown in Walter \& Augustin (2009),
 we can have both tractability and meaningful reaction to prior-data conflict
-by using sets of priors $\MktZ$ produced by parameter set $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
-For such a rectangular prior parameter set $\PktZ$,
-the posterior parameter set $\PktN$ is not rectangular anymore.
+by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
+In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
+corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
+The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
+Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
+obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
+and so can be described efficiently through the set of updated parameters
+\begin{align*}
+\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
+\end{align*}
+Such rectangular prior parameter sets $\PktZ$ have been shown
+to balance desirable model properties and ease of elicitation quite well.
 
-In case of no prior-data conflict ($s^k_t/n^k_t \in [\yktzl, \yktzu]$),
-the set shrinks in the $\ykt$ dimension
-(how much it shrinks depends on $\nktz$, leading to the so-called spotlight shape),
-leading to smaller $\Rsys(t)$ intervals.
+For each component type $k$ and time point $t$,
+one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
+(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
+prior knowledge on the survival function of components of type $k$);
+notwithstanding this, the model has favourable inference properties.
+
+Central to these inference properties is that
+while the prior parameter set $\PktZ$ is rectangular,
+the posterior parameter set $\PktN$ is not rectangular anymore;
+indeed, the shape of $\PktN$ depends on the presence of prior-data conflict,
+which is naturally operationalized as $s^k_t/n^k_t \not\in [\yktzl, \yktzu]$:
+prior-data conflict is present when the observed fraction of functioning components
+is outside its expected range.
+
+In absence of prior-data conflict, 
+$\PktN$ shrinks in the $\ykt$ dimension;
+how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
+leading to the so-called spotlight shape depicted in Figure***.
+As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
+shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
+Also, the variance interval for $p_t^k$ will decrease
+as the Beta distributions in $\MktN$ will be more pointed
+due to the increase of $\nktz$ to $\nktn$.s
 
 In case of prior-data conflict ($s^k_t/n^k_t \not\in [\yktzl, \yktzu]$),
-$\PktN$ has the so-called banana shape,
-giving a wider $\yktn$ interval as compared to the non-conflict case. 
-As a consequence, we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.
+$\PktN$ has instead the so-called banana shape,
+arising from $\yktn$ intervals being shifted closer towards $s^k_t/n^k_t$
+for lower $\nktn$ values than for higher $\nktn$ values, see Figure***.
+Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
+reflecting the extra uncertainty due to prior-data conflict,
+thus making more cautious probability statements about $p_t^k$.
 
-Lower and upper bounds for $\Rsys(t)$ by min and max over $\PZ_{1,t}, \ldots, \PZ_{K,t}$.
+***Lower and upper bounds for $\Rsys(t)$ by min and max over $\PtZi{1}, \ldots, \PtZi{K}$.
 
-Monotonicity in $\yz_{k,t}$, so we get
+***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
 \begin{align*}
-\lRsys(t)
- &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} \Rsys(t) \\
+\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)}\\
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \\
  &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k \mid s^k_t) \\
+                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \\
  &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
@@
 \end{align*}
+
+***How to choose the sets of priors for the survival function of type $k$ components,
+i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***
 
@@
 
-\section{Computations}
+\section{Computations \& Toy Example}
 
-***publish code as seperate \textbf{R} package, or include in Louis' package \texttt{ReliabilityTheory}
+***publish code in Louis' package \texttt{ReliabilityTheory}
 (which contains the function to calculate the survival signature)***
 
-\section{Example}
+***Show $\Rsys(t)$ intervals for prior-data conflict and non-conflict data
+to show effect of prior-data conflict.***
 
-***Will ask Simme Douwe Flapper (Prof at TU Eindhoven) for real-world example,
-otherwise some toy example will do.***
+***Also calculate $\Rsys(t)$ intervals for vacuous prior ($[\yktzl, \yktzu] = [0,1]$ for some fixed $\nktz$)?***
 
-Show $\Rsys(t)$ intervals for prior-data conflict and non-conflict data
-to show effect of prior-data conflict.
-
-Also calculate $\Rsys(t)$ intervals for vacuous prior ($[\yktzl, \yktzu] = [0,1]$, some fixed $\nktz$)?***
-
-Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
+***Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
 or show effect of replacement of failed components in a system
-(replaced components constitute a new type with shifted component reliability function)
+(replaced components constitute a new type with shifted component reliability function)?***
 
@@
 
-Extend the model to deal with right-censored observations which are common in realibility setting.
+***Extend the model to deal with right-censored observations which are common in the relaibility setting.
 We assume that a minimal assumption (component can fail immediately after censoring or live forever)
 will be simple to implememt but will lead to high imprecision,
-whereas assuming exchangeability with other components at moment of censoring
-will be more complex to accomodate but will lead to les imprecision.
+whereas assuming exchangeability with other surviving components at moment of censoring
+will be more complex to accomodate but will lead to less imprecision.
 

### 2015-10-21 ijar-npb-ms.tex
minor stuff

@@
 
-\author[ein]{Gero Walter}
+\author[ein]{Gero Walter\fnref{fn1}}
 \ead{g.m.walter@tue.nl}
@@
 \address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}
+
+\fntext[fn1]{Gero Walter was supported by the Dinalog project
+``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).}
 
@@
 
-***Also calculate $\Rsys(t)$ intervals for vacuous prior ($[\yktzl, \yktzu] = [0,1]$ for some fixed $\nktz$)?***
+***Also calculate $\Rsys(t)$ intervals for vacuous prior
+($[\yktzl, \yktzu] = [0,1]$ for both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***
 

### 2015-10-21 ijar-npb-ms.tex
intro, what calculations

@@
 
-Based on expert assumptions and data for component failure distribution,
-the goal is to calculate the system reliability function $\Rsys(t) = P(\Tsys > t)$.
+Based on expert assumptions for component failure distribution and component test data,
+we make predictive inference for a system with components that are exchangeable
+with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
 Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
@@
 To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict,
-we propose an impürecise or interval probability approach
+we propose an imprecise or interval probability approach
 based on sets of prior distributions defined through sets of canonical parameters.
@@
 or, for each time point $t$, an interval for the system survival probability
-that appropriately reflects uncertainty due to vague prior information, the amount of data, and prior-data conflict.
+that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.
 
@@
 
-\section{Computations \& Toy Example}
+\section{Computations \& Examples}
 
-***publish code in Louis' package \texttt{ReliabilityTheory}
+***publish code in Louis' \textbf{R} spackage \texttt{ReliabilityTheory}
 (which contains the function to calculate the survival signature)***
 
-***Show $\Rsys(t)$ intervals for prior-data conflict and non-conflict data
-to show effect of prior-data conflict.***
+***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
+informative prior set for some component types, different degree of imprecision,
+noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
+combine with prior-data conflict and non-conflict test data,
+to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***
 
-***Also calculate $\Rsys(t)$ intervals for vacuous prior
-($[\yktzl, \yktzu] = [0,1]$ for both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***
+***Vacuous prior sets: $[\yktzl, \yktzu] = [0,1]$ combined with both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***
 
-***Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
-or show effect of replacement of failed components in a system
-(replaced components constitute a new type with shifted component reliability function)?***
+***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
+(could nicely illustrate decision making with intervals:
+do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
+or do I rather add redundancy such that effect is smaller but more certain?***
+
+***Other interesting extra illustration:
+show effect of replacement of components in a system at certain time points
+(failed component or preventive replacement),
+replaced components constitute a new type with shifted component reliability function***
 
@@
 
-***Extend the model to deal with right-censored observations which are common in the relaibility setting.
+***Extend the model to deal with right-censored observations which are common in the reliability setting.
 We assume that a minimal assumption (component can fail immediately after censoring or live forever)

### 2015-10-21 ijar-npb-ms.tex
ref to risk analysis paper in intro

@@
 that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.
+
+This paper implements the nonparametric approach described in Section~4 of ***Risk Analysis paper***
+and extends it to sets of priors.
 
@@
 
-***publish code in Louis' \textbf{R} spackage \texttt{ReliabilityTheory}
+***publish code in Louis' \textbf{R} package \texttt{ReliabilityTheory}
 (which contains the function to calculate the survival signature)***
@@
 ***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
-(could nicely illustrate decision making with intervals:
+(could nicely illustrate challenges in decision making with intervals:
 do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
@@
 ***Other interesting extra illustration:
-show effect of replacement of components in a system at certain time points
-(failed component or preventive replacement),
+show effect of replacement of components in system at certain time points
+(could be corrective (component failed) or preventive replacement),
 replaced components constitute a new type with shifted component reliability function***

### 2015-10-30 ijar-npb-ms.tex
Just fixing my surname and committing to check push access works!  (also updated .gitignore for software I use)
bibliography and sandbox for code for examples etc

@@
 %\usetikzlibrary{shapes.misc,fit}
+
+\usepackage[bookmarks]{hyperref}
 
@@
 \ead{g.m.walter@tue.nl}
-\author[oxf]{Louis J.M. Ashlett}
+\author[oxf]{Louis J.M. Aslett}
 \ead{louis.aslett@stats.ox.ac.uk}
@@
 
-This paper implements the nonparametric approach described in Section~4 of ***Risk Analysis paper***
+This paper implements the nonparametric approach described in Section~4 of \citet{2015:bayessurvsign}
 and extends it to sets of priors.
@@
 
-As was shown in Walter \& Augustin (2009),
+As was shown in \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
 we can have both tractability and meaningful reaction to prior-data conflict
 by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
+(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
 In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
@@
 
+% ------------ bibliography -------------
+
+\section*{References}
+
+\bibliographystyle{elsarticle-harv}
+\bibliography{ijar-npb-refs}
+
 \end{document}

### 2015-10-30 sandbox.R

@@ -1,0 +1,88 @@
+# playing around
+
+setwd("../ijar-npb")
+library("ReliabilityTheory")
+library(ggplot2)
+
+# Risk Analysis paper example
+g <- graph.formula(s -- 1 -- 2:4:5, 2 -- 3 -- t, 4:5 -- 6 -- t,
+                   s -- 7 -- 8 -- t, s -- 9 -- 10 -- 11 -- t, 7 -- 10 -- 8)
+V(g)$compType <- NA
+V(g)$compType[match(c("1","6","11"), V(g)$name)] <- "T1"
+V(g)$compType[match(c("2","3","9"), V(g)$name)] <- "T2"
+V(g)$compType[match(c("4","5","10"), V(g)$name)] <- "T3"
+V(g)$compType[match(c("7","8"), V(g)$name)] <- "T4"
+
+sig <- computeSystemSurvivalSignature(g)
+
+set.seed(233)
+t1 <- rexp(100, rate=0.55)
+t2 <- rweibull(100, scale=1.8, shape=2.2)
+t3 <- rlnorm(100, 0.4, 0.9)
+t4 <- rgamma(100, scale=0.9, shape=3.2)
+
+d <- ggplot(data.frame(Failuretimes=c(t1,t2,t3,t4),
+                       Item=c(rep(c("T1", "T2", "T3", "T4"), each=100))))
+d <- d + geom_histogram(aes(x=Failuretimes), binwidth=0.5) + facet_grid(Item ~ .)
+d <- d + coord_cartesian(xlim=c(0,11)) + xlab("Failure times")
+d
+
+t <- seq(0, 5, length.out=300)
+
+# prior survival function
+no.test.data <- list("T1"=NULL, "T2"=NULL, "T3"=NULL, "T4"=NULL)
+s0 <- nonParBayesSystemInference(t, sig, no.test.data)
+pr <- ggplot(data.frame(Time=t, Probability=s0))
+pr <- pr + geom_line(aes(x=Time, y=Probability)) + coord_cartesian(ylim=c(0,1))
+pr <- pr + xlab("Time") + ylab("Survival Probability")
+pr
+
+# posterior survival function
+test.data <- list("T1"=t1, "T2"=t2, "T3"=t3, "T4"=t4)
+yS <- nonParBayesSystemInference(t, sig, test.data)
+p <- ggplot(data.frame(Time=t, Probability=yS))
+p <- p + geom_line(aes(x=Time, y=Probability))
[…]

### 2015-11-17 ijar-npb-ms.tex
title suggestion and rewrite of nonpar Bayes section, reparametrisation in new section

@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{todonotes}
+\usepackage{etoolbox}
 \usepackage{url}
@@
 %\newcommand{\comments}[1]{{\small\color{gray} #1}}
+\newtoggle{td}
+\newcommand{\td}[1]{%
+  \iftoggle{td}{%
+    \todo[inline]{#1}%
+  }{}%
+}
 
@@
 \allowdisplaybreaks
+
+\toggletrue{td} % show todo's
+%\togglefalse{td} % hide todo's
 
@@
 \begin{frontmatter}
-\title{IJAR Bayesian Nonparametrics Special Issue Manuscript}
+\title{Bayesian Nonparametric System Reliability\\ using Sets of Priors}
 
@@
 The random failure time of component number $i$ of type $k$ is denoted by $T^k_i$, $i = 1, \ldots m_k$.
-For its distribution, written in terms of the cdf $F^k(t) = P(T^k_i \le t)$
+The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
 or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
+also known as the survival function.
+For a nonparametric description of $R^k(t)$,
 we consider a set of time points $t$, $t \in {\cal T} = \{t_1, \ldots, \tmax\}$.
@@
 \end{align*}
-in short, $\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$.
+in short, $\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
 
-Then, due to the assumption of independence of components of the same type, 
+The set of functioning probabilities $\{ p^k_t, t \in {\cal T}\}$
+defines a discrete failure time distribution for components of type $k$ through
+\begin{align*}
+R^k(t_j) &= p^k_{t_j},\ t \in {\cal T} = \{t_1, \ldots, \tmax\}\,.
+\end{align*}
+We can express this failure time distribution also through the probability mass function (pmf) and the discrete hazard function,
+\begin{align*}
+q_k(t_j) &= P(T^k = t_j) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
+h_k(t_j) &= P(T^k = t_j \mid T^k \ge t_j) = \frac{q_k(t_j)}{R(t_j)}\,.
+\end{align*}
+We assume the time grid $\cal T$ is dense enough for the application at hand,
+otherwise it would be possible to assume, e.g.,
+$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
+or taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.
+
+\td{***illustrate discrete distribution with a graph of R, q, h?***}
+
+Due to the independence assumption for components of the same type, 
 the number of functioning components out of the $m_k$ components of type $k$
 is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.
-
-The set of functioning probabilities $p^k_t$
-corresponding to a choosen set of time points ($t \in {\cal T} = \{t_1, \ldots, \tmax\}$)
-defines a discrete failure time distribution for components of type $k$,
-$R^k(t) = p^k_{t_j}$, $t \in [t_j, t_{j+1})$.
-
-***or say we don't know for times between time points, or lower and upper bound already here?***
-***illustrate with a graph?***
-
 %(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
 %or the NPI bounds for Kaplan-Meier?)
-%
 
-The $p^k_t$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate.
-Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).***
+The $p^k_t$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate $h_k(t)$.
+Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
 
@@
 \end{align*}
-where $B(\cdot, \cdot)$ is the beta function.
+where $B(\cdot, \cdot)$ is the Beta function.
+This posterior predictive distribution is basically a Binomial distribution
+where the functioning probability $p^k_t$ takes values in $[0,1]$
+with the probability given by the posterior on $p^k_t$.
 
-The posterior predictive basically averages over $p^k_t \in [0,1]$,
-weighted with the posterior on $p^k_t$.
+To wrap up, to calculate the system reliability according to ***eqnumber***,
+for each component type $k$,
+we need lifetime data $\vec{t}^k$,
+and have to choose $2 \times |{\cal T}|$ parameters
+to specify the prior distribution for the discrete survival function of $T^k_i$.
+In total, values for $2 \times |{\cal T}| \times K$ parameters must be chosen.
 
-For each component type $k$, we have to choose $2 \times |{\cal T}|$
-parameters to specify the prior distribution for the discrete survival function of $T^k_i$,
-so in total $2 \times |{\cal T}| \times K$ parameters.
+\section{Reparametrisation of the Beta}
 
-Let us drop the super- and subscript $k$ and $t$ for a while
-to discuss the role and interpretation of the parameters $\alpha$ and $\beta$
-for each $k$ and $t$.
-The Beta distribution is usually parametrized in terms of $\alpha$ and $\beta$ as used above, 
-but for our generalization to sets of priors,
-it is useful to consider a different parametrization in terms of $\nz$ and $\yz$, where
-\begin{align*}
+The parametrisation of the Beta distribution used above is common,
+and allows to interpret $\alpha^k_t$ and $\beta^k_t$ as
+hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
+However, for our generalisation to sets of priors,
+it is useful to consider a different parametrisation.
+
+For discussing this reparametrisation, we will drop the super- and subscript $k$ and $t$ for a while.
+Instead of $\alpha$ and $\beta$, we consider the parameters $\nz$ and $\yz$, where
+\begin{align}
 \nz &= \alpha + \beta &
@@
 \yz &= \frac{\alpha}{\alpha + \beta} \,,
-\end{align*}
+\label{eq:reparam}
+\end{align}
 or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
-$\nz$ and $\yz$ are sometimes known as the \emph{canonical} parameters,
-identified from rewriting the density in a canonical form.
-(This canonical form gives a joint structure to all conjugate priors.)
+The upper index ${}\uz$ is used to identify $\nz$ and $\yz$ as prior parameter values,
+in contrast to their posterior values $\nn$ and $\yn$
+obtained after observing $n$ failure times, see below.
+$\nz$ and $\yz$ are sometimes called \emph{canonical} parameters,
+identified from rewriting the density in a canonical form;
+see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}.
+This canonical form gives a joint structure to all conjugate priors in exponential families.
 
@@
 we see that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
-and that the higher $\nz$, the more probability weight will be concentrated around that mean,
+and that the higher $\nz$, the more probability weight will be concentrated around $\yz$,
 as $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
 Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
-this will be illustrated through revisiting the posterior
-based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$:
+this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
+and will be further illustrated below through revisiting the posterior
+based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
 
@@
 the posterior mean $\yn$ for $p$ is a weighted average of
-the prior mean $\yz$ and $s/n$ (the fraction of function components in the data),
+the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
 with the weights $\nz$ and $n$, respectively.
@@
 thus the notion of pseudocount.
-Also, the higher $\nz$, the higher the weight for $\yz$
+Indeed, the higher $\nz$, the higher the weight for $\yz$
 in the weighted average calculation of $\yn$,
@@
 \end{align*}
+\td{leave this equation out???}
 
-The reparametrization enables us to see that in the conjugate setting,
+The parametrization in terms of prior mean and prior strength
+enables us to see that in this conjugate setting,
 learning from data amounts to averaging between prior and data.

### 2015-11-17 ijar-npb-ms.tex
par on near-noninformative prior sets, sets of R_sys in separate section

@@
 \usepackage{amsthm}
-\usepackage{bm}
 
@@
 \newcommand{\bs}[1]{\boldsymbol{#1}}
-\renewcommand{\vec}[1]{{\bm#1}}
+\renewcommand{\vec}[1]{{\bs#1}}
 
@@
 
-\section{Reparametrisation of the Beta}
+\section{Reparametrisation of the Beta Distribution}
 
@@
 is therefore
-\begin{align*}
+\begin{align}
 P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                     {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
-\end{align*}
+\label{eq:postpredCny}
+\end{align}
 \td{leave this equation out???}
@@
 
-***Illustration of such prior-data conflict with $\bebin$ distribution:
+\td{***Illustration of such prior-data conflict with $\bebin$ distribution:
 different priors updated to same posterior,
 or same prior updated to different posteriors with same variance,
-show corresponding $C^k_t$ distribution.***
+show corresponding $C^k_t$ distribution.***}
 
-\section{Sets of Priors}
+\section{Sets of Beta Priors}
 
@@
 to balance desirable model properties and ease of elicitation quite well.
-
+%
 For each component type $k$ and time point $t$,
@@
 
+Furthermore, with sets of Beta priors it is also possible
+to express prior ignorance in a more adequate way,
+by letting $\yktzl \to 0$ and $\yktzu \to 1$
+for some or all $t \in {\cal T}$.
+(It is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
+as this can lead to improper posterior predictive distributions.
+E.g., for any $t < \min(\vec{t}^k)$,
+we would get $\yktnu = 1$, leading to one argument of the Beta function
+in the denominator of \eqref{eq:postpredCny} being zero.)
+Choosing these limits for $\yktz$ means that we are prepared to give trivial bounds for the functioning probability only,
+and do not wish to make any commitments about $p^k_t$ a priori.
+Compare this to the uniform prior over $[0,1]$, a usual choice of `noninformative' prior,
+being a Beta prior with $\alpha^k_t = \beta^k_t = 1$, i.e., $\nktz = 2$, $\yktz = 0.5$.
+Taking this for all $t \in {\cal T}$ means that we expect the component reliability function
+to be on average 1/2 for all $t$, a very peculiar assumption,
+and, in our view, quite incompatible with the notion of prior ignorance.
+
+In this near-noninformative setting, the choice of $\nktzl$ not relevant,
+as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
+indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
+$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
+Logically, one cannot have prior-data conflict in case of prior near ignorance.
+
+\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
+benavoli zaffalon papers***}
+
+\section{Sets of System Reliability Functions}
+
 ***Lower and upper bounds for $\Rsys(t)$ by min and max over $\PtZi{1}, \ldots, \PtZi{K}$.
@@
 ***e.g., what to do in extreme tail of component distributions?
-How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***
+How sensitive is the method to choosing prior (lower, upper) mean near-zero for $p^k_t$ at high $t$'s?***
+
+***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
+to get proper posteriors!?!***
 
@@
 
-***Vacuous prior sets: $[\yktzl, \yktzu] = [0,1]$ combined with both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***
+***Vacuous prior sets: $[\yktzl, \yktzu] = (0,1)$ combined with interval $[\nktzl, \nktzu]$)***
 

### 2015-11-17 ijar-npb-ms.tex
notes in sections 6 and 7

@@
 
+***main contribution of the paper:
+set of priors thing,
+guidelines on how to choose the parameters;
+this is easier in terms of $(\nz, \yz)$ than in terms of $(\alpha, \beta)$***
+
 ***How to choose the sets of priors for the survival function of type $k$ components,
@@
 
-***do we need to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$?
-I would say no, and for relatively dense $t$ grids, neighbouring intervals should be able to overlap after all.
-What about requiring $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$?
-This might not hold for the case when we know, e.g., pretty much what's going on for low $t$
-but want to be much more cautious for high $t$.***
+***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
+as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
 
-***main contribution of the paper besides the set of priors thing:
-guidelines on how to choose the parameters?***
-
-***e.g., what to do in extreme tail of component distributions?
-How sensitive is the method to choosing prior (lower, upper) mean near-zero for $p^k_t$ at high $t$'s?***
+***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$?
+What if we know, e.g., pretty much what's going on for low $t$
+but want to be much more cautious for high $t$?
+$\yktzl$ can then drop to 0, but are we ok that $\yktzu$ cannot increase?
+(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
+but does this need to hold for the prior guess range bound $\yktzu$?)***
 
@@
 
+***what to do in extreme tail of component distributions?
+How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
+
 \section{Computations \& Examples}
 
-***publish code in Louis' \textbf{R} package \texttt{ReliabilityTheory}
+***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory}
 (which contains the function to calculate the survival signature)***
@@
 
-***Vacuous prior sets: $[\yktzl, \yktzu] = (0,1)$ combined with interval $[\nktzl, \nktzu]$)***
+***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
+informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***
 
@@
 ***Extend the model to deal with right-censored observations which are common in the reliability setting.
-We assume that a minimal assumption (component can fail immediately after censoring or live forever)
+We believe that a minimal assumption (component can fail immediately after censoring or live forever)
 will be simple to implememt but will lead to high imprecision,
@@
 will be more complex to accomodate but will lead to less imprecision.
+
+***right-censoring will also allow to use data from running system,
+to calculate its remaining useful life (RUL).
 

### 2015-11-18 sandbox.R
some ggplot honing

@@ -156,14 +156,24 @@ g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, color=variable))
 g2 <- g2 + ylab("Survival Probability") + coord_cartesian(ylim=c(-0.05,1.05))
 g2
 
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+
 g2df <- rbind(cbind(melt(g2T1, "Time"), Part="T1"), cbind(melt(g2T2, "Time"), Part="T2"),
               cbind(melt(data.frame(Time=g2pt, Prior=g2pprio, Posterior=g2ppost), "Time"), Part="System"))
-g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, color=Part, linetype=variable))
-g2 <- g2 + ylab("Survival Probability") + coord_cartesian(ylim=c(-0.05,1.05))
+g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, color=Part, linetype=variable), size=1)
+g2 <- g2 + ylab("Survival Probability") + # coord_cartesian(ylim=c(-0.05,1.05)) +
+  rightlegend + # theme_minimal() +
+#  scale_colour_manual(values=c("red", "orange", "yellow"))
+#  scale_colour_brewer(palette="Set1")
+  #  scale_colour_manual(values=rainbow(3))
+  scale_colour_manual(values=heat.colors(3))
 g2
 
-g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, linetype=variable)) + facet_grid(Part ~ .)
-g2 <- g2 + ylab("Survival Probability") #+ coord_cartesian(ylim=c(-0.05,1.05))
+g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, linetype=variable)) + 
+  facet_grid(Part ~ .)
+#  facet_wrap(Part ~) # for, e.g., 3 component types, this will arrange the 4 facets in 2x2 
+g2 <- g2 + ylab("Survival Probability") + bottomlegend
 g2
 
 # ----------------------------------------------

### 2015-11-19 pdc-illu.R
prior-data conflict illustration example

@@ -1,0 +1,70 @@
+# Illustration prior-data conflict in Beta-Binomial model
+# plots of posterior predictive
+
+library(ggplot2)
+library(reshape2)
+
+updateLuckY <- function (n0, y0, tau, n){ (n0*y0+tau)/(n0+n) }
+updateLuckN <- function (n0, n){ n0+n }
+
+nyupdate <- function (pr, data){
+  nn <- updateLuckN(pr[1], data[2])
+  yn <- updateLuckY(pr[1], pr[2], data[1], data[2])
+  c(nn,yn)
+}
+
+dbetany <- function(x, ny, ...){
+  dbeta(x, shape1=ny[1]*ny[2], shape2=ny[1]*(1-ny[2]), ...)
+}
+
+dbebinvec <- function(pos, m, l = NULL){
+  if (is.null(l))
+    l <- 0:m
+  sapply(l, function(li, m, n, y){
+    choose(m,li) * beta(li+n*y, m-li+n*(1-y)) / beta(n*y, n*(1-y)) 
+  }, m=m, n=pos[1], y=pos[2])
+}
+
+# one prior updated to posteriors with same variance
+sgpr <- c(8, 0.75) # n0, y0
+data1 <- c(12,16)  #  s,  n
+data2 <- c( 0,16)
+
+pos1 <- nyupdate(sgpr, data1)
+pos2 <- nyupdate(sgpr, data2)
+
+# beta densities
+betavec <- seq(0,1, length.out=200)
+bdsgpr <- dbetany(betavec, sgpr)
+bdpos1 <- dbetany(betavec, pos1)
+bdpos2 <- dbetany(betavec, pos2)
+
+bddf <- melt(data.frame(x=betavec, Prior=bdsgpr, "Posterior 1"=bdpos1, "Posterior 2"=bdpos2), "x")
+
+betadens <- ggplot(bddf, aes(x, value, group=variable, linetype=variable)) + geom_line() +
+  bottomlegend + xlab(expression(p[t]^k)) + ylab(expression(f(p[t]^k)))
+betadens
+
+
+# beta-binomial distributions
+#dbebinvec(pos1,2,1)
+m <- 4
+bebinpr <- dbebinvec(sgpr, m)
+bebin1 <- dbebinvec(pos1, m)
+bebin2 <- dbebinvec(pos2, m)
+
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
[…]

### 2015-11-19 sandbox.R

@@ -171,8 +171,8 @@ g2 <- g2 + ylab("Survival Probability") + # coord_cartesian(ylim=c(-0.05,1.05)) 
 g2
 
 g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, linetype=variable)) + 
-  facet_grid(Part ~ .)
-#  facet_wrap(Part ~) # for, e.g., 3 component types, this will arrange the 4 facets in 2x2 
+#  facet_grid(Part ~ .) # arranges facets in a column
+  facet_wrap(~ Part, ncol=2) # for, e.g., 3 component types, this will arrange the 4 facets in 2x2 
 g2 <- g2 + ylab("Survival Probability") + bottomlegend
 g2
 

### 2015-11-20 ijar-npb-ms.tex
some corrections for pmf and discrete hazard
renaming the pmf to f
prior-data conflict illustration example
figure for pdc example in sec 4 ready

@@
 \begin{align*}
-R^k(t_j) &= p^k_{t_j},\ t \in {\cal T} = \{t_1, \ldots, \tmax\}\,.
+R^k(t_j) &= P(T^k > t_j) = p^k_{t_j},\ t_j = t_1, \ldots, \tmax\,.
 \end{align*}
@@
 \begin{align*}
-q_k(t_j) &= P(T^k = t_j) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
-h_k(t_j) &= P(T^k = t_j \mid T^k \ge t_j) = \frac{q_k(t_j)}{R(t_j)}\,.
+f^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\big) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
+h^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\mid T^k > t_j\big) = \frac{f^k(t_j)}{R^k(t_j)}\,. % or R^k(t_{j-1}) ???
 \end{align*}
@@
 and is not reflected in the posterior or the posterior predictive.
+
+As a simple example, see Figure~\ref{fig:singleprior-pdc} ***
+
+\begin{figure}
+\includegraphics[width=\textwidth]{singleprior-pdc}
+\caption{Beta densities (left) and corresponding Beta-binomial probability mass functions (right)
+for a prior with $\nktz = 8, \yktz = 0.75$,
+and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior 1) and $s^k_t=0$ (Posterior 2), respectively.
+For Posterior 2, the conflict between prior assumptions and data is averaged out;
+both posterior density and posterior predictive have the same spread as Posterior 1 for which there is no conflict,
+giving a false sense of certainty.}
+\label{fig:singleprior-pdc}
+\end{figure}
 

### 2015-11-20 pdc-illu.R

@@ -3,6 +3,8 @@
 
 library(ggplot2)
 library(reshape2)
+library(grid)
+library(gridExtra)
 
 updateLuckY <- function (n0, y0, tau, n){ (n0*y0+tau)/(n0+n) }
 updateLuckN <- function (n0, n){ n0+n }
@@ -39,32 +41,62 @@ bdsgpr <- dbetany(betavec, sgpr)
 bdpos1 <- dbetany(betavec, pos1)
 bdpos2 <- dbetany(betavec, pos2)
 
-bddf <- melt(data.frame(x=betavec, Prior=bdsgpr, "Posterior 1"=bdpos1, "Posterior 2"=bdpos2), "x")
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+
+bddf <- data.frame(x=betavec, Prior=bdsgpr, "Posterior1"=bdpos1, "Posterior2"=bdpos2)
+names(bddf)[c(3,4)] <- c("Posterior 1", "Posterior 2")
+bddf <- melt(bddf, "x")
 
 betadens <- ggplot(bddf, aes(x, value, group=variable, linetype=variable)) + geom_line() +
   bottomlegend + xlab(expression(p[t]^k)) + ylab(expression(f(p[t]^k)))
 betadens
 
+betadens2 <- ggplot(bddf, aes(x, value, group=variable, linetype=variable)) + geom_line() +
+  guides(linetype="none") + xlab(expression(p[t]^k)) + ylab(expression(f(p[t]^k)))
+betadens2
 
 # beta-binomial distributions
 #dbebinvec(pos1,2,1)
-m <- 4
+m <- 5
 bebinpr <- dbebinvec(sgpr, m)
 bebin1 <- dbebinvec(pos1, m)
 bebin2 <- dbebinvec(pos2, m)
 
-bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
-rightlegend <- theme(legend.title = element_blank())
+pdcilludf <- data.frame(x=rep(0:m), Prior=bebinpr, "Posterior1"=bebin1, "Posterior2"=bebin2)
+names(pdcilludf)[c(3,4)] <- c("Posterior 1", "Posterior 2")
+pdcilludf$x <- ordered(pdcilludf$x)
+pdcilludf <- melt(pdcilludf, "x")
[…]

### 2015-11-20 ijar-npb-ms.tex
improved caption for pdc illu figure

@@
 As a simple example, see Figure~\ref{fig:singleprior-pdc} ***
+giving a false sense of certainty***
 
@@
 for a prior with $\nktz = 8, \yktz = 0.75$,
-and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior 1) and $s^k_t=0$ (Posterior 2), respectively.
-For Posterior 2, the conflict between prior assumptions and data is averaged out;
-both posterior density and posterior predictive have the same spread as Posterior 1 for which there is no conflict,
-giving a false sense of certainty.}
+and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior~1) and $s^k_t=0$ (Posterior~2), respectively.
+Data for Posterior~1 confirm prior assumptions,
+while data for Posterior~2 are in conflict with the prior.
+However, this conflict is averaged out,
+and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf and the posterior predictive pmf,
+such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}
 \label{fig:singleprior-pdc}

### 2015-11-20 ijar-npb-ms.tex
text for pdc illu example

@@
 \def\tpnow{t^+_\text{now}}
+
+\newcommand{\ptk}{p^k_t}
 
@@
 For each time point $t$, the functioning of a single component of type $k$ at time $t$ (functioning: 1, failed: 0)
-is Bernoulli distributed with a suitable functioning probability (as, $1-$failure probability) $p^k_t$, so
+is Bernoulli distributed with a suitable functioning probability (as, $1-$failure probability) $\ptk$, so
 \begin{align*}
-P\big(\indic(T^k_i > t) = 1\big) &= p^k_t\,, \\
-P\big(\indic(T^k_i > t) = 0\big) &= 1 - p^k_t\,,
+P\big(\indic(T^k_i > t) = 1\big) &= \ptk\,, \\
+P\big(\indic(T^k_i > t) = 0\big) &= 1 - \ptk\,,
 \end{align*}
-in short, $\indic(T^k_i > t) \sim \ber(p^k_t)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
+in short, $\indic(T^k_i > t) \sim \ber(\ptk)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
 
-The set of functioning probabilities $\{ p^k_t, t \in {\cal T}\}$
+The set of functioning probabilities $\{ \ptk, t \in {\cal T}\}$
 defines a discrete failure time distribution for components of type $k$ through
@@
 the number of functioning components out of the $m_k$ components of type $k$
-is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(p^k_t, m_k)$.
+is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(\ptk, m_k)$.
 %(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
@@
 
-The $p^k_t$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate $h_k(t)$.
+The $\ptk$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
 Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
 
-However, directly choosing the $p^k_t$'s is hard,
+However, directly choosing the $\ptk$'s is hard,
 and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
-To account for this uncertainty, one can express knowledge on $p^k_t$ through a prior distribution.
-A convenient and natural choice is $p^k_t \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
+To account for this uncertainty, one can express knowledge on $\ptk$ through a prior distribution.
+A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
 leading to the posterior being again Beta.
@@
 $s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
-The posterior is then $p^k_t \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
+The posterior is then $\ptk \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
 The combination of a Binomial observation model with a Beta prior is often called Beta-binomial model.
@@
 This posterior predictive distribution is basically a Binomial distribution
-where the functioning probability $p^k_t$ takes values in $[0,1]$
-with the probability given by the posterior on $p^k_t$.
+where the functioning probability $\ptk$ takes values in $[0,1]$
+with the probability given by the posterior on $\ptk$.
 
@@
 From the properties of the Beta distribution,
-we see that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
+it follows that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
 and that the higher $\nz$, the more probability weight will be concentrated around $\yz$,
@@
 \end{align}
-\td{leave this equation out???}
+%\td{leave this equation out???}
 
@@
 
-As a simple example, see Figure~\ref{fig:singleprior-pdc} ***
-giving a false sense of certainty***
+As a simple example, assume that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
+so we choose $\yktz = 0.75$,
+and that we value this choice of mean functioning probability with $\nktz = 8$,
+i.e., like having seen $8$ observations with a mean $0.75$.
+Assume further that there are $n^k = 16$ components of type $k$ in the test data.
+When we observe $s^k_t = 12$ components functioning at time $t$,
+so $s^k_t/n^k = 0.75$ as we expect,
+then the updated parameters are $\nktn = 24, \yktn=0.75$.
+Unexpectedly observing that no component functions at time $t$ instead
+leads to parameters $\nktn = 24, \yktn=0.25$.
+The prior and the posteriors based on these two observation scenarios
+are depicted in Figure~\ref{fig:singleprior-pdc}
+through their Beta densities (left)
+and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$
+for the case of $m_k = 5$ (right).
+
+Due to symmetry, we see that both posteriors have the same variance or spread,
+although arising from two fundamentally different scenarios.
+Posterior 1 is based on data exactly according to prior expectations;
+the increase in confidence on $\ptk \approx 0.75$
+is reflected in a more pointed posterior density,
+and the posterior predictive is changed only slightly.
+It is quite disturbing to see the same degree of confidence in Posterior 2,
+being based on data in sharp conflict with prior expectations.
+Posterior 2 places most probability weight around $0.25$,
+averaging between prior expectation and data,
+with the same variance or spread as Posterior 1.
+Instead of acknowledging the conflict between observed functioning probability zero
+and expected functioning probability $0.75$ by increased variance,
+Posterior 2 gives a false sense of certainty,
+also reflected in the posterior predictive,
+where both Posterior 1 and 2 have the same variance as well.
 
@@
 
-\td{***Illustration of such prior-data conflict with $\bebin$ distribution:
-different priors updated to same posterior,
-or same prior updated to different posteriors with same variance,
-show corresponding $C^k_t$ distribution.***}
+To counter this unwanted behaviour,
+we propose to use an imprecise probability approach
+based on sets of Beta priors, described next.
 

### 2015-11-20 ijar-npb-ms.tex
elicitation ideas

@@
 
-In this near-noninformative setting, the choice of $\nktzl$ not relevant,
+In this near-noninformative setting, the choice of $\nktzl$ is not relevant,
 as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
@@
 
-***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$?
-What if we know, e.g., pretty much what's going on for low $t$
-but want to be much more cautious for high $t$?
-$\yktzl$ can then drop to 0, but are we ok that $\yktzu$ cannot increase?
-(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
-but does this need to hold for the prior guess range bound $\yktzu$?)***
+***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
+If we know, e.g., pretty much what's going on for low $t$
+but want to be much more cautious for high $t$,
+then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
+Better to express certainty of prior guess via $\nktz$ bounds?
+With strongly differing $\nktz$ values, it could however happen that, e.g., $\yzu_{k,t_j} \le \yzu_{k,t_{j+1}}$!
+So require same $\nktz$ bounds for all $t$?
+%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
+%but does this need to hold for the prior guess range bound $\yktzu$?)***
 
@@
 How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
+
+***we should also cover the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
+as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
+(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
+Idea: ``fill up the $t$ grid at all $t$'' with least-committal bounds, i.e.: 
+at all $t$ not elicited, take $\yktzu$ equal to last (in time sequence) elicited $\yktzu$,
+and $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
+
+***possible elicitation procedure: starting with $\yktz$ bounds for `middle' or `typical' $t$,
+then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
+refine further as possible.
 

### 2015-11-23 sandbox-sets.R
rugplot for component plots, start sandbox for sets

@@ -1,0 +1,79 @@
+#play around with sets
+
+#install.packages("devtools")
+#library("devtools")
+#install_github("louisaslett/ReliabilityTheory")
+library("ReliabilityTheory")
+library(ggplot2)
+library(reshape2)
+
+
+# Risk Analysis paper example with sets of priors
+# First specify the system layout, numbered as per Figure 4
+g <- graph.formula(s -- 1 -- 2:4:5, 2 -- 3 -- t, 4:5 -- 6 -- t,
+                   s -- 7 -- 8 -- t, s -- 9 -- 10 -- 11 -- t, 7 -- 10 -- 8)
+# Then specify the component types (within the circles of Figure 4)
+V(g)$compType <- NA
+V(g)$compType[match(c("1","6","11"), V(g)$name)] <- "T1"
+V(g)$compType[match(c("2","3","9"), V(g)$name)] <- "T2"
+V(g)$compType[match(c("4","5","10"), V(g)$name)] <- "T3"
+V(g)$compType[match(c("7","8"), V(g)$name)] <- "T4"
+# Compute the survival signature table from Appendix
+sig <- computeSystemSurvivalSignature(g)
+# Simulate the test data (same seed as used in the paper)
+set.seed(233)
+t1 <- rexp(100, rate=0.55)
+t2 <- rweibull(100, scale=1.8, shape=2.2)
+t3 <- rlnorm(100, 0.4, 0.9)
+t4 <- rgamma(100, scale=0.9, shape=3.2)
+# Compile into a list as required by this function
+test.data <- list("T1"=t1, "T2"=t2, "T3"=t3, "T4"=t4)
+no.test.data <- list("T1"=NULL, "T2"=NULL, "T3"=NULL, "T4"=NULL)
+# Create a vector of times at which to evaluate the posterior predictive
+# survival probability and compute using this function
+t <- seq(0, 5, length.out=300)
+yS <- nonParBayesSystemInference(t, sig, test.data) # with fixed prior as before
+# Set of prior R(t)'s
+yS0 <- nonParBayesSystemInferencePriorSets(t, sig, no.test.data, nLower=1, nUpper=50, yLower=0.4, yUpper=0.7)
+# Set of posterior R(t)'s
+yS2 <- nonParBayesSystemInferencePriorSets(t, sig, test.data, nLower=1, nUpper=50, yLower=0.4, yUpper=0.7)
+# Plot
+p <- ggplot(data.frame(Time=rep(t,3), Probability=c(yS, yS2$lower, yS2$upper),
[…]

### 2015-11-23 sandbox.R

@@ -1,6 +1,9 @@
 # playing around
 
-setwd("../ijar-npb")
+#setwd("../ijar-npb")
+#install.packages("devtools")
+#library("devtools")
+#install_github("louisaslett/ReliabilityTheory")
 library("ReliabilityTheory")
 library(ggplot2)
 library(reshape2)
@@ -171,6 +174,7 @@ g2 <- g2 + ylab("Survival Probability") + # coord_cartesian(ylim=c(-0.05,1.05)) 
 g2
 
 g2 <- ggplot(g2df) + geom_line(aes(x=Time, y=value, linetype=variable)) + 
+  geom_rug(aes(x=x), data=rbind(data.frame(x=g2ptestdata$"T1", Part="T1"), data.frame(x=g2ptestdata$"T2", Part="T2"))) +
 #  facet_grid(Part ~ .) # arranges facets in a column
   facet_wrap(~ Part, ncol=2) # for, e.g., 3 component types, this will arrange the 4 facets in 2x2 
 g2 <- g2 + ylab("Survival Probability") + bottomlegend

### 2015-11-24 sandbox-sets.R
first simple example with set of priors

@@ -64,16 +64,91 @@ oneCompSurvSign <- function(name){
 # for component of type "name" based on nonParBayesSystemInferencePriorSets() inputs
 # for all components except survival signature; nLower, nUpper, yLower, yUpper must be data frames
 # where each column corresponds to the component type, so there must be a match 
-oneCompPriorPost <- function(name, at.times, test.data, alpha, beta){
+oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLower, yUpper){
   sig <- oneCompSurvSign(name)
   nodata <- list(name=NULL)
   names(nodata) <- name
-  avec <- alpha[, match(name, names(alpha))]
-  bvec <- beta[, match(name, names(beta))]
+  nL <- nLower[, match(name, names(nLower))]
+  nU <- nUpper[, match(name, names(nUpper))]
+  yL <- yLower[, match(name, names(yLower))]
+  yU <- yUpper[, match(name, names(yUpper))]
   data <- test.data[match(name, names(test.data))]
-  prio <- nonParBayesSystemInference(at.times, sig, nodata, avec, bvec)
-  post <- nonParBayesSystemInference(at.times, sig, data, avec, bvec)
-  data.frame(Time=at.times, Prior=prio, Posterior=post)
+  prio <- nonParBayesSystemInferencePriorSets(at.times, sig, nodata, nL, nU, yL, yU)
+  post <- nonParBayesSystemInferencePriorSets(at.times, sig,   data, nL, nU, yL, yU)
+  data.frame(Time=rep(at.times,2), Lower=c(prio$lower,post$lower), Upper=c(prio$upper,post$upper),
+             Item=rep(c("Prior", "Posterior"), each=length(at.times)))
 }
+
+# ----------------------------------------------
+
+# parallel system with two components, T1 prior informative, T2 prior near ignorance
+g2p <- graph.formula(s -- 1:2 -- t)
+V(g2p)$compType <- NA
[…]

### 2015-11-24 sandbox.R

@@ -129,7 +129,7 @@ V(g2p)$compType <- NA
 V(g2p)$compType[match(c("1"), V(g2p)$name)] <- "T1"
 V(g2p)$compType[match(c("2"), V(g2p)$name)] <- "T2"
 g2pnulldata <- list("T1"=NULL, "T2"=NULL)
-g2ptestdata <- list("T1"=1:4, "T2"=1:4)
+g2ptestdata <- list("T1"=1:4, "T2"=1:4+0.5)
 g2psig <- computeSystemSurvivalSignature(g2p)
 g2pt <- seq(0, 5, length.out=11)
 g2T1ab <- ny2ab(rep(1,11), seq(0.99, 0.01, length.out=11))

### 2015-11-25 ijar-npb-ms.tex
pdc-illu with cdf and cmf, and Rsys set examples with 301 timepoints

@@
 are depicted in Figure~\ref{fig:singleprior-pdc}
-through their Beta densities (left)
-and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$
+through their Beta densities and cdfs (left)
+and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
 for the case of $m_k = 5$ (right).
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{singleprior-pdc}
-\caption{Beta densities (left) and corresponding Beta-binomial probability mass functions (right)
+\includegraphics[width=\textwidth]{singleprior-pdc2}
+\caption{Beta densities (top left) and cdfs (bottom left),
+with the corresponding Beta-binomial probability mass functions (top right) and cumulative mass functions (bottom right),
 for a prior with $\nktz = 8, \yktz = 0.75$,
@@
 However, this conflict is averaged out,
-and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf and the posterior predictive pmf,
+and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf/cdf and the posterior predictive pmf/cmf,
 such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}

### 2015-11-25 pdc-illu.R

@@ -19,6 +19,10 @@ dbetany <- function(x, ny, ...){
   dbeta(x, shape1=ny[1]*ny[2], shape2=ny[1]*(1-ny[2]), ...)
 }
 
+pbetany <- function(x, ny, ...){
+  pbeta(x, shape1=ny[1]*ny[2], shape2=ny[1]*(1-ny[2]), ...)
+}
+
 dbebinvec <- function(pos, m, l = NULL){
   if (is.null(l))
     l <- 0:m
@@ -35,18 +39,26 @@ data2 <- c( 0,16)
 pos1 <- nyupdate(sgpr, data1)
 pos2 <- nyupdate(sgpr, data2)
 
-# beta densities
 betavec <- seq(0,1, length.out=200)
+# beta densities
 bdsgpr <- dbetany(betavec, sgpr)
 bdpos1 <- dbetany(betavec, pos1)
 bdpos2 <- dbetany(betavec, pos2)
+# beta cdfs
+bpsgpr <- pbetany(betavec, sgpr)
+bppos1 <- pbetany(betavec, pos1)
+bppos2 <- pbetany(betavec, pos2)
 
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
 rightlegend <- theme(legend.title = element_blank())
 
 bddf <- data.frame(x=betavec, Prior=bdsgpr, "Posterior1"=bdpos1, "Posterior2"=bdpos2)
+bpdf <- data.frame(x=betavec, Prior=bpsgpr, "Posterior1"=bppos1, "Posterior2"=bppos2)
 names(bddf)[c(3,4)] <- c("Posterior 1", "Posterior 2")
+names(bpdf)[c(3,4)] <- c("Posterior 1", "Posterior 2")
 bddf <- melt(bddf, "x")
+bpdf <- melt(bpdf, "x")
+bdf <- rbind(data.frame(bddf, Item="pdf"), data.frame(bpdf, Item="cdf"))
 
 betadens <- ggplot(bddf, aes(x, value, group=variable, linetype=variable)) + geom_line() +
   bottomlegend + xlab(expression(p[t]^k)) + ylab(expression(f(p[t]^k)))
@@ -56,20 +68,41 @@ betadens2 <- ggplot(bddf, aes(x, value, group=variable, linetype=variable)) + ge
[…]

### 2015-11-25 sandbox-sets.R

@@ -125,11 +125,11 @@ g3testdata <- list("T1"=c(2, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1
 g3testdata <- list("T1"=c(2, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)-0.5) # T3 fitting failures
 g3dat <- melt(g3testdata); names(g3dat) <- c("x", "Part")
 g3sig <- computeSystemSurvivalSignature(g3)
-g3t <- seq(0, 5, length.out=101)
-g3nL <- data.frame(T1=rep(1,101), T2=rep(1,101), T3=rep(1,101))
-g3nU <- data.frame(T1=rep(2,101), T2=rep(2,101), T3=rep(4,101))
-g3yL <- data.frame(T1=rep(0.01, 101), T2=rep(0.01, 101), T3=c(rep(c(0.625,0.375,0.250, 0.125, 0.01), each=20), 0.01))
-g3yU <- data.frame(T1=rep(0.99, 101), T2=rep(0.99, 101), T3=c(rep(c(0.990,0.875,0.500, 0.375, 0.25), each=20), 0.25))
+g3t <- seq(0, 5, length.out=301)
+g3nL <- data.frame(T1=rep(1,301), T2=rep(1,301), T3=rep(1,301))
+g3nU <- data.frame(T1=rep(2,301), T2=rep(2,301), T3=rep(4,301))
+g3yL <- data.frame(T1=rep(0.01, 301), T2=rep(0.01, 301), T3=c(rep(c(0.625,0.375,0.250,0.125,0.010), each=60), 0.01))
+g3yU <- data.frame(T1=rep(0.99, 301), T2=rep(0.99, 301), T3=c(rep(c(0.990,0.875,0.500,0.375,0.250), each=60), 0.25))
 
 g3T1 <- oneCompPriorPostSet("T1", g3t, g3testdata, g3nL, g3nU, g3yL, g3yU)
 g3T2 <- oneCompPriorPostSet("T2", g3t, g3testdata, g3nL, g3nU, g3yL, g3yU)
@@ -140,6 +140,7 @@ g3post <- nonParBayesSystemInferencePriorSets(g3t, g3sig, g3testdata, g3nL, g3nU
 g3df <- rbind(data.frame(g3T1, Part="T1"), data.frame(g3T2, Part="T2"), data.frame(g3T3, Part="T3"),
[…]

### 2015-11-25 bebin-stochdom.R
dabbling around with beta-binomial for stochastic dominance along y

@@ -1,0 +1,27 @@
+dbebinvec <- function(pos, m, l = NULL){
+  if (is.null(l))
+    l <- 0:m
+  sapply(l, function(li, m, n, y){
+    choose(m,li) * beta(li+n*y, m-li+n*(1-y)) / beta(n*y, n*(1-y)) 
+  }, m=m, n=pos[1], y=pos[2])
+}
+
+pbebinvec <- function(...)
+  cumsum(dbebinvec(...))
+
+# beta-binomial is stochastically ordered along y:
+yvec <- (1:9)/10
+pbebinmat <- sapply(yvec, function(y,n,m){
+  pbebinvec(c(n,y),m=m)
+}, n=1, m=5)
+matplot(0:5, pbebinmat, type="l")
+all(apply(pbebinmat[-6,], 1, order) == matrix(9:1, nrow=9, ncol=5))
+
+# ...but not along n:
+nvec <- 1:9/10
+pbebinmat <- sapply(nvec, function(n,y,m){
+  pbebinvec(c(n,y),m=m)
+}, y=0.5, m=5)
+matplot(0:5, pbebinmat, type="l")
+
+#

### 2015-11-25 ijar-npb-ms.tex
text on monotonicity in y

@@
 
+We need to optimize over $\nktz$'s only,
+as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
+Remember that $\yktz$ gives the prior expected survival probability for a component of type $k$ at time $t$.
+As seen in Figures *** and ***, the posterior parameter set bounds are the transformed prior parameter set bounds,
+i.e., $\yktzu$ corresponds to the upper bound of $\PktN$ for all $\nktz \in \PktZ$.
+
+Now, a higher posterior expected survival probability means
+higher probability for many components surviving out of $m_k$
+(i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower).
+***Indeed, the Beta-binomial distribution is stochastically ordered for varying y, i.e.,
+its cdf is decreasing in $\yktn$ for fixed $l_k$, and the cdfs for different $\yktn$ do not cross each other.***
+This means that for $\yktn$ the probability weights given to the high values of $l_k$ are maximised.
+As $\Phi$ is non-decreasing in each of its arguments $l_k, k=1,\ldots,K$ (for coherent systems),
+$\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values.
+
+%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
+%keeping all other component type expressions fixed.
+
 ***main contribution of the paper:

### 2015-11-26 ijar-npb-ms.tex
survival signature intro by Frank

@@
 
-Based on expert assumptions for component failure distribution and component test data,
-we make predictive inference for a system with components that are exchangeable
-with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
-Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
-naturally a Bayesian model for the functioning probability at each time point arises.
-To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict,
-we propose an imprecise or interval probability approach
-based on sets of prior distributions defined through sets of canonical parameters.
-
-Our method produces a set of discrete system reliability functions,
-or, for each time point $t$, an interval for the system survival probability
-that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.
-
-This paper implements the nonparametric approach described in Section~4 of \citet{2015:bayessurvsign}
-and extends it to sets of priors.
-
-\section{Survival Signature}
-
 The survival signature allows for straightforward computation of system reliability
 for systems with complex layouts and multiple component types.
-It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.
-
-Can be seen as applying the law of total probability by partitioning
-according to the number of components of type $k$ functioning at time $t$,
-denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$:
+It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
+by partitioning the event $\Tsys > t$ according to the number of components of type $k$ functioning at time $t$,
+denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$, and applying the law of total probability:
 \begin{align*}
@@
 \end{align*}
+
+Based on expert assumptions for component failure distribution and component test data,
+we make predictive inference for a system with components that are exchangeable
+with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
+Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
+naturally a Bayesian model for the functioning probability at each time point arises.
+To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict (see Section~***),
+we propose an imprecise or interval probability approach
+based on sets of prior distributions defined through sets of canonical parameters.
+This approach also allows to adequately model weak or partial prior information.
+Especially prior near ignorance can be modelled much more meaningfully than through usual so-called noninformative priors.
+
+Our method produces a set of discrete system reliability functions,
+or, for each time point $t$, an interval for the system survival probability,
+that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.
+
+This paper implements the nonparametric approach described in Section~4 of \citet{2015:bayessurvsign}
+and extends it to sets of priors.
+
+The paper is organised as follows.
+In Section~\ref{sec:survsign}, we describe ***
+
+\section{Survival Signature}
+\label{sec:survsign}
+
+In mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
+of its components and the structure of the system. The mathematical concept which is central to this theory is the 
+\emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
+$\underline{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
+and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\underline{x}$. 
+The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\underline{x}$, takes 
+the value 1 if the system functions and 0 if the system does not function for state vector $\underline{x}$. 
+Most practical systems are coherent, which means that $\phi(\underline{x})$ 
+is non-decreasing in any of the components of $\underline{x}$, so system functioning cannot be improved by worse performance 
+of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
+quantification for system reliability. It is further logical to assume that $\phi(\underline{0})=0$ and $\phi(\underline{1})=1$, 
+so the system fails if all its components fail and it functions if all its components function.
+
+For larger systems, working with the full structure function may be complicated, and one may particularly
+only need a summary of the structure function in case the system has exchangeable components of one or more
+types. We use the term `exchangeable components' to indicate that the failure times of the components in the system
+are exchangeable \citep{DF74}. \citet{2012:survsign} introduced such a summary,
+called the \emph{survival signature}, 
+to facilitate reliability analyses for systems with multiple types of components. In case of just a single type of components, 
+the survival signature is closely related to the system signature \citep{Sa07}, which is well-established and the topic of many
+research papers during the last decade. However, generalization of the signature to systems with
+multiple types of components is extremely complicated (as it involves ordering order statistics of different
+distributions), so much so that it cannot be applied to most practical systems. In addition to the 
+possible use for such systems, where the benefit only occurs if there are multiple components of the 
+same types, the survival signature is arguably also easier to interpret than the signature.
+
+Consider a system with $K\ge 1$ types of components, with $m_k$ components of type $k \in \{1,\ldots,K\}$ and 
+$\sum_{k=1}^K m_k = m$. Assume that the random failure times of components of the same type are exchangeable \citep{DF74}.
+Due to the arbitrary ordering of the components in the state vector, components of the same type can be grouped together, 
+leading to a state vector that can be written as 
+$\underline{x} = (\underline{x}^1,\underline{x}^2,\ldots,\underline{x}^K)$, with 
+$\underline{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.
+
+The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
+for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
+$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}. 
+There are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
+denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
+all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
+exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
+$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
+\begin{align}
+\label{eq:surv-sig}
+\Phi(l_1,\ldots,l_K)
+ &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
+\end{align}
+
+Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
+Then, for system failure time $\Tsys$,
+\begin{align*}
+P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
+\end{align*}
+It should be emphasized that when using the survival signature,
+there are no restrictions on dependence of the failure times of components of different types,
+as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
+for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
+However, there is a substantial simplification
+if one can assume that the failure times of components of different types are independent,
+and even more so if one can assume that the failure times of components of type $k$ 
+are conditionally independent and identically distributed with CDF $F_k(t)$.
+With these assumptions, we get
+\begin{align*}
+\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
+            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
+\end{align*}
+
+The main advantage of the survival signature, in line with this property of the signature for systems with a single type of 
+components \citep{Sa07}, is that the information about the system structure is fully 
+separated from the information about functioning of the components, which simplifies related statistical inference as well as
+considerations of optimal system design. In particular for study of system reliability over time, with the structure of the system, 
+and hence the survival signature, not changing, this separation also enables relatively straightforward statistical inferences.
+
+There are several relatively straightforward generalizations of the use of the survival signature.
+The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
+as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
+where lower and upper probabilities for the events $C_k = l_k$
+are inferred from test data on components of the same types as those in the system.
+This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
+***This step is less trivial here as we must ensure to have probability distributions for these events,
+thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
+***covered because of parametric distribution, min and max over parameter sets (see section 6)***
+***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
+see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
+Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
+to reflect uncertainty about system functioning for known states of its components.
+A further suggestion was to generalize this to lower and upper structure functions,
+within the theory of imprecise probability \citep{itip,CU11}.
+These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
+which in the latter case also becomes an imprecise probability.
+
+The survival signature is a powerful but rather basic concept.
+As such, further generalizations are conceptually easy,
+for example one can straightforwardly generalize the survival signature to multi-state systems
+such that it again summarizes the structure function
+in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
 
@@
 
+Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
+However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
+and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.
+
 ***Extend the model to deal with right-censored observations which are common in the reliability setting.

### 2015-12-03 ijar-npb-ms.tex
rewritten write-out of monotonicity in y argument

@@
 
-The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$,
+The Beta-binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
 now again with indicators $t$ and $k$,
@@
 P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
-                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
+                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,,
 \label{eq:postpredCny}
 \end{align}
-%\td{leave this equation out???}
+and the corresponding cumulative mass function (cmf) is given by
+\begin{align}
+F_{C^k_t\mid s^k_t}(l_k) &= P(C^k_t \le l_k \mid s^k_t) = \sum_{j_k=0}^{l_k} P(C^k_t = j_k \mid s^k_t)\,.
+\label{eq:postpredCnycmf}
+\end{align}
 
@@
 
-***Lower and upper bounds for $\Rsys(t)$ by min and max over $\PtZi{1}, \ldots, \PtZi{K}$.
+To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
+we now need to minimise and maximise Equation~*** over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
+where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.
+It turns out that we need to optimise over $\nktz$ ($k=1,\ldots,K$) only,
+as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
 
-***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
+To see this,
+remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
+From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
+%the posterior parameter set bounds are the transformed prior parameter set bounds,
+%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
+such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
+%
+Now, a higher posterior expected functioning probability means
+higher probability for many components out of $m_k$ surviving,
+i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
+***Indeed, the Beta-binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
+its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
+such that the cmfs for different values of $\yktn$ do not cross each other.***
+This means that for each fixed $\nktz$, the Beta-binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
+such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
+For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
+thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
+which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
+We therefore have
+%
+%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
+%keeping all other component type expressions fixed.
+%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
 \begin{align*}
@@
 \end{align*}
-
-We need to optimize over $\nktz$'s only,
-as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
-Remember that $\yktz$ gives the prior expected survival probability for a component of type $k$ at time $t$.
-As seen in Figures *** and ***, the posterior parameter set bounds are the transformed prior parameter set bounds,
-i.e., $\yktzu$ corresponds to the upper bound of $\PktN$ for all $\nktz \in \PktZ$.
-
-Now, a higher posterior expected survival probability means
-higher probability for many components surviving out of $m_k$
-(i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower).
-***Indeed, the Beta-binomial distribution is stochastically ordered for varying y, i.e.,
-its cdf is decreasing in $\yktn$ for fixed $l_k$, and the cdfs for different $\yktn$ do not cross each other.***
-This means that for $\yktn$ the probability weights given to the high values of $l_k$ are maximised.
-As $\Phi$ is non-decreasing in each of its arguments $l_k, k=1,\ldots,K$ (for coherent systems),
-$\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values.
-
-%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
-%keeping all other component type expressions fixed.
 

### 2015-12-03 ijar-npb-ms.tex
minor changes in elicitation notes, more details for the n interval question

@@
 then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
-Better to express certainty of prior guess via $\nktz$ bounds?
-With strongly differing $\nktz$ values, it could however happen that, e.g., $\yzu_{k,t_j} \le \yzu_{k,t_{j+1}}$!
-So require same $\nktz$ bounds for all $t$?
+
+***Better to express certainty of prior guess via $\nktz$ bounds?\\
+With (strongly) differing $\nktz$ values, it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
+E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
+$s^k_t/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so no prior-data conflict) and no failures in $[t_j, t_{j+1}]$,\\
+then with $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we have $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$,\\
+ and with $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we have $\ynl_{k,t_j} > \ynl_{k,t_{j+1}}$.\\
+(weighted average between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
+So we need to require same $\nktz$ bounds for all $t$!
 %(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
@@
 ***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
-to get proper posteriors!?!***
+to get proper posteriors***
 
@@
 
-***we should also cover the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
+***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
 as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.

### 2015-12-04 brakingsystem.R
braking system example

@@ -1,0 +1,89 @@
+# small automobile breaking system example form Ebeling (1997, pp. 91f)
+
+#install.packages("devtools")
+#library("devtools")
+#install_github("louisaslett/ReliabilityTheory")
+library("ReliabilityTheory")
+library(ggplot2)
+library(reshape2)
+
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+
+# produces survival signature matrix for one component of type "name",
+# for use in nonParBayesSystemInference()
+oneCompSurvSign <- function(name){
+  res <- data.frame(name=c(0,1), Probability=c(0,1))
+  names(res)[1] <- name
+  res
+}
+
+# produces data frame with prior and posterior lower & upper component survival function
+# for component of type "name" based on nonParBayesSystemInferencePriorSets() inputs
+# for all components except survival signature; nLower, nUpper, yLower, yUpper must be data frames
+# where each column corresponds to the component type, so there must be a match 
+oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLower, yUpper){
+  sig <- oneCompSurvSign(name)
+  nodata <- list(name=NULL)
+  names(nodata) <- name
+  nL <- nLower[, match(name, names(nLower))]
+  nU <- nUpper[, match(name, names(nUpper))]
+  yL <- yLower[, match(name, names(yLower))]
+  yU <- yUpper[, match(name, names(yUpper))]
+  data <- test.data[match(name, names(test.data))]
+  prio <- nonParBayesSystemInferencePriorSets(at.times, sig, nodata, nL, nU, yL, yU)
+  post <- nonParBayesSystemInferencePriorSets(at.times, sig,   data, nL, nU, yL, yU)
+  data.frame(Time=rep(at.times,2), Lower=c(prio$lower,post$lower), Upper=c(prio$upper,post$upper),
[…]

### 2015-12-16 ijar-npb-ms.tex
slight rework of sec1 and sec2

@@
 
-(some sentences may be useful for the abstract)
+(some sentences may be useful for the abstract instead)
 
@@
 It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
-by partitioning the event $\Tsys > t$ according to the number of components of type $k$ functioning at time $t$,
-denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$, and applying the law of total probability:
-\begin{align*}
-P(\Tsys > t)
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
-                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
-\end{align*}
+by partitioning the event $\Tsys > t$ according to the number of components of each type functioning at time $t$.
 
@@
 $m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}.
-There are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
+Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$, such that $\Rsys(t) = P(\Tsys > t)$
+can be calculated using the law of total probability:
+\begin{align*}
+P(\Tsys > t)
+ &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \\
+ &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
+ &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
+                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \,,
+%                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
+\end{align*}
+where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
+the random number of components of type $k$ functioning at time $t$.
+
+For calculating the survival signature based on the structure function, observe that
+there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
 denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
@@
 \end{align}
-
-Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
-Then, for system failure time $\Tsys$,
-\begin{align*}
-P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
-\end{align*}
+%
+%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
+%Then, for system failure time $\Tsys$,
+%\begin{align*}
+%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
+%\end{align*}
 It should be emphasized that when using the survival signature,
@@
 \end{align*}
+We will employ both assumptions in this paper,
+such that $C^k_t$ is Beta-Binomially distributed,
+giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.
 
@@
 see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
+\td{Leave out the sentences framed with `***'?}
 Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
@@
 
-\section{Nonparametric Bayesian Approach}
+\section{Nonparametric Bayesian Approach for Component Reliability}
 

### 2015-12-16 ijar-npb-ms.tex
minor work on secs 3 and 4

@@
 \newcommand{\be}{\operatorname{Beta}} 
-\newcommand{\bebin}{\operatorname{Beta-binomial}}
+\newcommand{\bebin}{\operatorname{Beta-Binomial}}
 
@@
 can be calculated using the law of total probability:
-\begin{align*}
+\begin{align}
+\label{eq:rsyswithsurvsign}
 P(\Tsys > t)
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \\
- &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
+ &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \nonumber\\
+ &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
  &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
@@
 %                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
-\end{align*}
+\end{align}
 where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
@@
 We will employ both assumptions in this paper,
-such that $C^k_t$ is Beta-Binomially distributed,
+leading to $C^k_t$ having a Beta-Binomial distribution,
 giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.
@@
 
-The random failure time of component number $i$ of type $k$ is denoted by $T^k_i$, $i = 1, \ldots m_k$.
+Let us denote the random failure time of component number $i$ of type $k$ by $T^k_i$, $i = 1, \ldots m_k$.
 The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
@@
 
-\td{***illustrate discrete distribution with a graph of R, q, h?***}
+\td{***illustrate discrete distribution with a graph of R, f, h?***}
 
@@
 The posterior is then $\ptk \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
-The combination of a Binomial observation model with a Beta prior is often called Beta-binomial model.
+The combination of a Binomial observation model with a Beta prior is often called Beta-Binomial model.
 
@@
 of the $m_k$ components in the system, based on the lifetime data and the prior information,
-is then a so-called Beta-binomial distribution,
+is then a so-called Beta-Binomial distribution,
 $C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
@@
 
-To wrap up, to calculate the system reliability according to ***eqnumber***,
+To wrap up, to calculate the system reliability according to \eqref{eq:rsyswithsurvsign},
 for each component type $k$,
@@
 and will be further illustrated below through revisiting the posterior
-based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
-
+%based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
+given $s$ of $n$ components functioning.
+We have that
 $p \mid s$ is Beta distributed with the updated parameters
@@
 \nn &= \nz + n\,, &
-\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,,
+\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,.
 \label{eq:nyupdate}
 \end{align}
-so after seeing that $s$ out of $n$ components function (at time $t$),
+After seeing that $s$ out of $n$ components function (at time $t$),
 the posterior mean $\yn$ for $p$ is a weighted average of
@@
 
-The Beta-binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
+The Beta-Binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
 now again with indicators $t$ and $k$,
@@
 
-As was shown in \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
+As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
 we can have both tractability and meaningful reaction to prior-data conflict
@@
 The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
+This element-by-element updating may seem ad-hoc, but can be rigorously justified
+as ensuring coherence \citep[\S ***]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6***]{1991:walley}.
 Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
@@
 as the Beta distributions in $\MktN$ will be more pointed
-due to the increase of $\nktz$ to $\nktn$.s
+due to the increase of $\nktz$ to $\nktn$.
 
@@
 thus making more cautious probability statements about $p_t^k$.
+
+\td{Figure with $\PN$s and sets of beta cdfs for conflict and no conflict case.}
 
@@
 
-In this near-noninformative setting, the choice of $\nktzl$ is not relevant,
+While for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
+in a near-noninformative setting, the choice of $\nktzl$ is not relevant,
 as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
@@
 $\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
-Logically, one cannot have prior-data conflict in case of prior near ignorance.
+Obviously, one cannot have prior-data conflict in case of prior near ignorance.
 
@@
 To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
-we now need to minimise and maximise Equation~*** over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
+we now need to minimise and maximise Equation~\eqref{} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
 where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.

### 2015-12-16 ijar-npb-ms.tex
writing out parameter choice guidelines

@@
 
+***main contribution of the paper:
+set of priors thing,
+guidelines on how to choose the parameters;
+this is easier in terms of $(\nz, \yz)$ than in terms of $(\alpha, \beta)$***
+
 This paper implements the nonparametric approach described in Section~4 of \citet{2015:bayessurvsign}
@@
 \section{Nonparametric Bayesian Approach for Component Reliability}
+\label{sec:nonparamapproach}
 
@@
 
-While for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
-in a near-noninformative setting, the choice of $\nktzl$ is not relevant,
+For an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
+as then one of the bounds for $\ykt$ is attained for $\nktzl$.
+In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
 as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
@@
 To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
-we now need to minimise and maximise Equation~\eqref{} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
-where the posterior predictive probabilities for $C^k_t$ are given by the beta-binomial pmf \eqref{eq:postpredCny}.
-It turns out that we need to optimise over $\nktz$ ($k=1,\ldots,K$) only,
+we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
+where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
+It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
 as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
@@
 i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
-***Indeed, the Beta-binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
+Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
 its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
-such that the cmfs for different values of $\yktn$ do not cross each other.***
-This means that for each fixed $\nktz$, the Beta-binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
+such that the cmfs for different values of $\yktn$ do not cross each other.
+This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
 such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
@@
 \end{align*}
+In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
+which define the set of prior discrete reliability functions for components of type $k$.
+We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
+%***How to choose the sets of priors for the survival function of type $k$ components,
+%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***
 
-***main contribution of the paper:
-set of priors thing,
-guidelines on how to choose the parameters;
-this is easier in terms of $(\nz, \yz)$ than in terms of $(\alpha, \beta)$***
-
-***How to choose the sets of priors for the survival function of type $k$ components,
-i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***
-
-***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
-as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
-
-***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
-If we know, e.g., pretty much what's going on for low $t$
-but want to be much more cautious for high $t$,
-then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
-
-***Better to express certainty of prior guess via $\nktz$ bounds?\\
-With (strongly) differing $\nktz$ values, it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
-E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
-$s^k_t/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so no prior-data conflict) and no failures in $[t_j, t_{j+1}]$,\\
-then with $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we have $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$,\\
- and with $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we have $\ynl_{k,t_j} > \ynl_{k,t_{j+1}}$.\\
-(weighted average between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
-So we need to require same $\nktz$ bounds for all $t$!
+As mentioned in Section~\ref{sec:nonparamapproach}, for the actual functioning probabilities $\ptk$
+it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. ***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$.
+%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
+%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
 %(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
 %but does this need to hold for the prior guess range bound $\yktzu$?)***
+This naturally translates to conditions on the prior guess for $\ptk$,
+such that we propose that 
+$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
+Due to $s^k_t/n_k$ decrasing in $t$ and the weighted average property of the update step for $\ykt$,
+this ensures that 
+$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
+In a situation where we are quite sure about the functioning probability for low $t$,
+but are unsure about what happens for larger $t$ and so want to be maximally cautious for those $t$,
+then we can let $\yktzl$ drop to (almost) 0, but $\yktzu$ should not increase.
+%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
+%If we know, e.g., pretty much what's going on for low $t$
+%but want to be much more cautious for high $t$,
+%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
 
-***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
-to get proper posteriors***
+We think it is not advisable to express certainty about expected functioning probabilities
+with $\nktz$ bounds that vary strongly over $t$.
+%***Better to express certainty of prior guess via $\nktz$ bounds?\\
+With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
+%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
+E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
+and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
+and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
+\begin{itemize}
+\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
+\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
+\end{itemize}
+Again, this follows from the weighted average property of $\yktn$;
+for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
+% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
+Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to have it change with $t$ gradually only.
+
+%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
+%to get proper posteriors***
+Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
 

### 2015-12-20 ijar-npb-ms.tex
work on sec 6 and notation n_k

@@
 i.e., like having seen $8$ observations with a mean $0.75$.
-Assume further that there are $n^k = 16$ components of type $k$ in the test data.
+Assume further that there are $n_k = 16$ components of type $k$ in the test data.
 When we observe $s^k_t = 12$ components functioning at time $t$,
-so $s^k_t/n^k = 0.75$ as we expect,
+so $s^k_t/n_k = 0.75$ as we expect,
 then the updated parameters are $\nktn = 24, \yktn=0.75$.
@@
 \section{Sets of Beta Priors}
+\label{sec:setsofbetapriors}
 
@@
 This element-by-element updating may seem ad-hoc, but can be rigorously justified
-as ensuring coherence \citep[\S ***]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6***]{1991:walley}.
+as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
 Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
@@
 indeed, the shape of $\PktN$ depends on the presence of prior-data conflict,
-which is naturally operationalized as $s^k_t/n^k_t \not\in [\yktzl, \yktzu]$:
-prior-data conflict is present when the observed fraction of functioning components
+which is naturally operationalized as $s^k_t/n_k \not\in [\yktzl, \yktzu]$:
+prior-data conflict is present when, at time $t$, the observed fraction of functioning components
 is outside its expected range.
@@
 
-In case of prior-data conflict ($s^k_t/n^k_t \not\in [\yktzl, \yktzu]$),
+In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
 $\PktN$ has instead the so-called banana shape,
-arising from $\yktn$ intervals being shifted closer towards $s^k_t/n^k_t$
+arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
 for lower $\nktn$ values than for higher $\nktn$ values, see Figure***.
@@
 As mentioned in Section~\ref{sec:nonparamapproach}, for the actual functioning probabilities $\ptk$
-it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. ***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$.
+it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
 %***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
@@
 % one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
+It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
 Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to have it change with $t$ gradually only.
+
+Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
+low values for $\nktz$ as compared to the test sample size $n_k$
+give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
+and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
+Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
+in a no-conflict situation, when $\nktzu = n_k$ $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
+In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
+which means more cautious posterior inferences.
+The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
+as is clear from Figure~***, the wider the $\nktz$ interval,
+the wider $[\yktnl, \yktnu]$ in case of conflict.
+So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
+while choosing $\nktzu$ with help of the half-width rule as described above.
 
@@
 %to get proper posteriors***
-Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
+As mentioned in Section~\ref{sec:setsofbetapriors},
+it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
+For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
+this can lead to improper posterior predictive distributions if $l_k=0$ or $l_k=m_k$.
+%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
+But it is possible to choose values close to $0$ and $1$, respectively,
+and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
+posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
+%***what to do in extreme tail of component distributions?
+%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
+Likewise, our nonparametric method does not bring unintuitive tail behaviour
+as some parametric methods do;
+there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.
 
-***what to do in extreme tail of component distributions?
-How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
-
-***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
-as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
-(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
-Idea: ``fill up the $t$ grid at all $t$'' with least-committal bounds, i.e.: 
-at all $t$ not elicited, take $\yktzu$ equal to last (in time sequence) elicited $\yktzu$,
-and $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
-
-***possible elicitation procedure: starting with $\yktz$ bounds for `middle' or `typical' $t$,
-then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
-refine further as possible.
+%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
+%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
+While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
+in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
+%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
+Switching to a coarser time grid will waste information from data,
+as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
+We rather propose to elicit bounds only for a subset of ${\cal T}$,
+and to fill up the $t$ grid with the least committal bounds, i.e.,
+taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
+an likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
+A possible elicitation procedure in this vein could be
+to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
+filling up the grid as described above accordingly,
+and then to further refine the obtained bounds if necessary.
+%`middle' or `typical' $t$,
+%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
 
@@
 
-***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory}
-(which contains the function to calculate the survival signature)***
+***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
+function \texttt{nonParBayesSystemInferencePriorSets()};
+the package also contains the function \texttt{computeSystemSurvivalSignature()}
+to calculate the survival signature for a given system layout (reliability block diagramm)***
 

### 2015-12-20 bridgesystem.R
bridgesystem, mostly copy of sandbox-sets

@@ -1,0 +1,75 @@
+# bridge system, 3 component types
+
+#install.packages("devtools")
+#library("devtools")
+#install_github("louisaslett/ReliabilityTheory")
+library("ReliabilityTheory")
+library(ggplot2)
+library(reshape2)
+
+# produces survival signature matrix for one component of type "name",
+# for use in nonParBayesSystemInference()
+oneCompSurvSign <- function(name){
+  res <- data.frame(name=c(0,1), Probability=c(0,1))
+  names(res)[1] <- name
+  res
+}
+
+# produces data frame with prior and posterior lower & upper component survival function
+# for component of type "name" based on nonParBayesSystemInferencePriorSets() inputs
+# for all components except survival signature; nLower, nUpper, yLower, yUpper must be data frames
+# where each column corresponds to the component type, so there must be a match 
+oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLower, yUpper){
+  sig <- oneCompSurvSign(name)
+  nodata <- list(name=NULL)
+  names(nodata) <- name
+  nL <- nLower[, match(name, names(nLower))]
+  nU <- nUpper[, match(name, names(nUpper))]
+  yL <- yLower[, match(name, names(yLower))]
+  yU <- yUpper[, match(name, names(yUpper))]
+  data <- test.data[match(name, names(test.data))]
+  prio <- nonParBayesSystemInferencePriorSets(at.times, sig, nodata, nL, nU, yL, yU)
+  post <- nonParBayesSystemInferencePriorSets(at.times, sig,   data, nL, nU, yL, yU)
+  data.frame(Time=rep(at.times,2), Lower=c(prio$lower,post$lower), Upper=c(prio$upper,post$upper),
+             Item=rep(c("Prior", "Posterior"), each=length(at.times)))
+}
+
+# ----------------------------------------------
+
+b3 <- graph.formula(s -- 1 -- 2:3 -- 4 -- 5:6 --t, 2 -- 5, 3 -- 6)
[…]

### 2015-12-21 ijar-npb-ms.tex
work on toy example

@@
 
-***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
-function \texttt{nonParBayesSystemInferencePriorSets()};
+%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
+The method is implemented in the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}
+with the function \texttt{nonParBayesSystemInferencePriorSets()};
 the package also contains the function \texttt{computeSystemSurvivalSignature()}
-to calculate the survival signature for a given system layout (reliability block diagramm)***
+to calculate the survival signature for a given system layout (reliability block diagramm).
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
+ cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
+ hv path/.style={thick, to path={-| (\tikztotarget)}},
+ vh path/.style={thick, to path={|- (\tikztotarget)}}]
+%\begin{scope}[scale=0.75]
+\node[type1] (T1)   at ( 0  , 0) {T1};
+\node[type2] (T2)   at ( 2.8, 0) {T2};
+\node[type3] (T3-2) at ( 1.4, 1) {T3};
+\node[type3] (T3-3) at ( 1.4,-1) {T3};
+\node[type3] (T3-5) at ( 4.2, 1) {T3};
+\node[type3] (T3-6) at ( 4.2,-1) {T3};
+\coordinate (start) at (-1,0);
+\coordinate (end)   at (5.6,0);
+\coordinate (bista) at (0.7,0);
+\coordinate (biend) at (4.9,0);
+\path (start)     edge[thick]   (T1.west)
+      (T1.east)   edge[thick]   (bista)
+      (bista)     edge[vh path] (T3-2.west)
+                  edge[vh path] (T3-3.west)
+      (T3-2.east) edge[hv path] (T2.north)
+      (T3-3.east) edge[hv path] (T2.south)
+      (T2.north)  edge[vh path] (T3-5.west)
+      (T2.south)  edge[vh path] (T3-6.west)
+      (T3-5.east) edge[hv path] (biend)
+      (T3-6.east) edge[hv path] (biend)
+      (biend)     edge[thick]   (end);
+%\end{scope}
+\end{tikzpicture}
+\caption{Reliability block diagram for a `bridge' system with three component types.}
+\label{fig:bridge-layout}
+\end{figure}
+
+As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
+as depicted in Figure~\ref{fig:bridge-layout}.
+For components type T1 and T2, we consider a near-noninformative set of prior reliability functions.
+For components of type T3, we consider an informative set of prior reliability functions
+as given in Table~\ref{tab:bridge-T3prior}.
+This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
+and filling up the rest.
+These prior assumptions, together with sets of posterior reliability functions
+resulting from three different scenarios for test data for component type T3,
+are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
+test data for components of type T1 and T2 are invariably
+$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.
+
+\begin{table}
+\centering
+\begin{tabular}{c|rrrrr}
+$t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
+\hline
+$\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
+$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250
+\end{tabular}
+\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system.}
+\label{tab:bridge-T3prior}
+\end{table}
+
+In Figure~\ref{fig:bridge-fitting}, 
+test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
+and so in line with expectations.
+The posterior set of reliability functions for each component type and the whole system
+is considerably smaller as compared to the prior set
+(due to the low prior strength intervals
+$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
+and so giving more precise reliability statements.
+We see that posterior lower and upper functioning probabilities drop at those times $t$
+when there is a failure time in the test data,
+or a drop in the prior functioning probability bounds.
+Note that the lower bound for prior system reliability function is zero
+due to the prior lower bound for T1;
+for the system to function, the component of type T1 must function.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{bridge-fittingfailures}
+\caption{Prior and posterior sets of reliability functions for the `bridge' system and its three component types,
+with failure times as expected for component type T3.
+Test data failure times are denoted with tick marks near the time axis.}
+\label{fig:bridge-fitting}
+\end{figure}
+
+In Figure~\ref{fig:bridge-early},
+test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
+and so earlier than expected.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{bridge-earlyfailures}
+\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
+with failure times earlier as expected for component type T3.}
+\label{fig:bridge-early}
+\end{figure}
+
+In Figure~\ref{fig:bridge-late}, 
+test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
+and so later than expected.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{bridge-latefailures}
+\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
+with failure times later as expected for component type T3.}
+\label{fig:bridge-late}
+\end{figure}
 

### 2015-12-21 bridgesystem.R

@@ -51,7 +51,7 @@ b3t <- seq(0, 5, length.out=301)
 b3nL <- data.frame(T1=rep(1,301), T2=rep(1,301), T3=rep(1,301))
 b3nU <- data.frame(T1=rep(2,301), T2=rep(2,301), T3=rep(4,301))
 b3yL <- data.frame(T1=rep(0.001, 301), T2=rep(0.001, 301), T3=c(rep(c(0.625,0.375,0.250,0.125,0.010), each=60), 0.01))
-b3yU <- data.frame(T1=rep(0.999, 301), T2=rep(0.999, 301), T3=c(rep(c(0.990,0.875,0.500,0.375,0.250), each=60), 0.25))
+b3yU <- data.frame(T1=rep(0.999, 301), T2=rep(0.999, 301), T3=c(rep(c(0.999,0.875,0.500,0.375,0.250), each=60), 0.25))
 
 b3T1 <- oneCompPriorPostSet("T1", b3t, b3testdata, b3nL, b3nU, b3yL, b3yU)
 b3T2 <- oneCompPriorPostSet("T2", b3t, b3testdata, b3nL, b3nU, b3yL, b3yU)
@@ -65,10 +65,10 @@ b3df <- rbind(data.frame(b3T1, Part="T1"), data.frame(b3T2, Part="T2"), data.fra
 b3df$Item <- ordered(b3df$Item, levels=c("Prior", "Posterior"))
 
 p3 <- ggplot(b3df) + geom_ribbon(aes(x=Time, ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
-p3 <- p3 + facet_wrap(~Part, ncol=2) + geom_rug(aes(x=x), data=g3dat) + xlab("Time") + ylab("Survival Probability")
-#pdf("3comp-latefailures.pdf", width=8, height=5)
-#pdf("3comp-earlyfailures.pdf", width=8, height=5)
-pdf("3comp-fittingfailures.pdf", width=8, height=5)
+p3 <- p3 + facet_wrap(~Part, ncol=2) + geom_rug(aes(x=x), data=b3dat) + xlab("Time") + ylab("Survival Probability")
+pdf("bridge-latefailures.pdf", width=8, height=5)
+pdf("bridge-earlyfailures.pdf", width=8, height=5)
+pdf("bridge-fittingfailures.pdf", width=8, height=5)
 p3
 dev.off()
 

### 2015-12-21 ijar-npb-ms.tex
text for bridge system example, breaking system example

@@
 as depicted in Figure~\ref{fig:bridge-layout}.
-For components type T1 and T2, we consider a near-noninformative set of prior reliability functions.
+For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
 For components of type T3, we consider an informative set of prior reliability functions
@@
 are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
-test data for components of type T1 and T2 are invariably
+test data for components of type T1 and T2 are invariably taken as
 $\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.
@@
 Note that the lower bound for prior system reliability function is zero
-due to the prior lower bound for T1;
+due to the prior lower bound of zero for T1;
 for the system to function, the component of type T1 must function.
@@
 and so earlier than expected.
+Compared to Figure~\ref{fig:bridge-fitting},
+posterior functioning intervals for T3 are wider between $t=1$ and $t=3.5$,
+reflecting additional imprecision due to prior-data conflict.
+For $t > 1$, it is clearly visible how $\ytnu{3}$ is halfway between $\ytzu{3}$ and $s_t^3/n_3 = 0$
+(weights $\ntzu{3} = 4$ and $n_3 = 4$),
+while $\ytnl{3}$ is one-fifth of $\ytzl{3}$
+(weights $\ntzl{3} = 1$ and $n_3 = 4$).
+Note that the posterior system functioning probability is constant for $t \in [1,2]$
+because the prior functioning probability is constant for $t \in [1,2]$
+and there are no failure times $\in [1,2]$ in the test data.
 
@@
 test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
-and so later than expected.
+and so observed failures are later than expected.
+Here we see that for $t \in [2,4]$,
+posterior functioning bounds for T3 are even wider than prior functioning bounds.
+The width turns back to being half the prior width
+only after the four failures.
+The imprecision carries over to the system bounds,
+where we see wider bounds as compared to the other scenarios
+especially between $t=2$ and $t=4$.
 
@@
 
-***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
-informative prior set for some component types, different degree of imprecision,
-noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
-combine with prior-data conflict and non-conflict test data,
-to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***
+***Another example: simplified automotive breaking system, Figure~\ref{fig:breakingsystem}.
+Prior sets and data exemplary only, prior bounds more smooth curves?
+The master breaking cylinder (M) activates all four wheel braking cylinders (C1 -- C4),
+which in turn actuate a braking pad assembly each (P1 -- P4).
+The hand break mechanism (H) goes directly to two brake pad assemblies P3 and P4;
+the car breaks when at least one brake pad assembly is actuated.***
 
-***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
-informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***
+\begin{figure}
+\includegraphics[width=\textwidth]{breakingsystem-1}
+\caption{A simplified automotive breaking system. ***System layout goes to empty space in lower row.}
+\label{fig:breakingsystem}
+\end{figure}
+
+%***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
+%informative prior set for some component types, different degree of imprecision,
+%noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
+%combine with prior-data conflict and non-conflict test data,
+%to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***
+
+%***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
+%informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***
 

### 2015-12-21 brakingsystem.R

@@ -85,5 +85,8 @@ abdf$Item <- ordered(abdf$Item, levels=c("Prior", "Posterior"))
 ab1 <- ggplot(abdf) + geom_ribbon(aes(x=Time, ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
 ab1 <- ab1 + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=abdat) + xlab("Time") + ylab("Survival Probability")
 ab1 <- ab1 + bottomlegend
+
+pdf("breakingsystem-1.pdf", width=8, height=5)
 ab1
+dev.off()
 #

### 2015-12-30 ijar-npb-ms.tex
block diagram for automotive breaking system example

@@
 \begin{figure}
-\includegraphics[width=\textwidth]{breakingsystem-1}
-\caption{A simplified automotive breaking system. ***System layout goes to empty space in lower row.}
+\begin{tikzpicture}
+[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
+ typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
+ typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
+ typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
+ cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
+ hv path/.style={thick, to path={-| (\tikztotarget)}},
+ vh path/.style={thick, to path={|- (\tikztotarget)}}]
+\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-1}};
+\begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
+\node[typeM] (M)    at ( 0  , 0  ) {M};
+\node[typeC] (C1)   at ( 1  , 1.5) {C1};
+\node[typeC] (C2)   at ( 1  , 0.5) {C2};
+\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
+\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
+\node[typeP] (P1)   at ( 2  , 1.5) {P1};
+\node[typeP] (P2)   at ( 2  , 0.5) {P2};
+\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
+\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
+\node[typeH] (H)    at ( 0  ,-1  ) {H};
+\coordinate (start)  at (-0.7, 0);
+\coordinate (startC) at ( 0.5, 0);
+\coordinate (startH) at (-0.4, 0);
+\coordinate (Hhop1)  at ( 0.4,-1);
+\coordinate (Hhop2)  at ( 0.6,-1);
+\coordinate (endP)   at ( 2.5, 0);
+\coordinate (end)    at ( 2.8, 0);
+\path (start)     edge[hv path] (M.west)
+      (M.east)    edge[hv path] (startC)
+      (startC)    edge[vh path] (C1.west)
+                  edge[vh path] (C2.west)
+                  edge[vh path] (C3.west)
+                  edge[vh path] (C4.west)
+      (C1.east)   edge[hv path] (P1.west)
+      (C2.east)   edge[hv path] (P2.west)
+      (C3.east)   edge[hv path] (P3.west)
+      (C4.east)   edge[hv path] (P4.west)
+      (endP)      edge[vh path] (P1.east)
+                  edge[vh path] (P2.east)
+                  edge[vh path] (P3.east)
+                  edge[vh path] (P4.east)
+                  edge[hv path] (end)
+      (startH)    edge[vh path] (H.west)
+      (H.east)    edge[hv path] (Hhop1)
+      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
+      (Hhop2)     edge[hv path] (P3.south)
+                  edge[hv path] (P4.north);
+\end{scope}
+\end{tikzpicture}
+\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
+with layout as depicted in the lower right panel.}
 \label{fig:breakingsystem}

### 2015-12-30 pdc-illu.R
sets of beta cdfs plot

@@ -5,6 +5,9 @@ library(ggplot2)
 library(reshape2)
 library(grid)
 library(gridExtra)
+library(luck)
+source("../../lund_1512/lund-1512/course/04-01_BinomialData.R")
+source("../../lund_1512/lund-1512/course/04-02_Binomial.R")
 
 updateLuckY <- function (n0, y0, tau, n){ (n0*y0+tau)/(n0+n) }
 updateLuckN <- function (n0, n){ n0+n }
@@ -133,5 +136,74 @@ pdcillupmfcmf   <- pdcillupmfcmf + theme(plot.margin = unit(c(0,0,  0,-0.75), "l
 pdf("singleprior-pdc2.pdf", width=8, height=5)
 grid.arrange(betapdfcdf, pdcillupmfcmf, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
+
+# ------------------- sets of Beta pdfs, sets of Beta-Bin cmfs -------------------------
+
+setpr <- BinomialLuckModel(n0=c(1,8), y0=c(0.7, 0.8))
+setpos1 <- setpr
+data(setpos1) <- BinomialData(s=12, n=16)
+setpos2 <- setpr
+data(setpos2) <- BinomialData(s= 0, n=16)
+
+betavec <- seq(0,1, length.out=200)
+
+cdfplot(setpos1, xvec=betavec)
+cdfplot(setpos1, xvec=betavec, control=controlList(posterior=TRUE))
+cdfplot(setpos2, xvec=betavec, control=controlList(posterior=TRUE))
+
+betapriolow <- sapply(betavec, function(x){
+  optim(par=c(4, 0.7), fn=function(.n0y0, x){
+    pbetany(x, .n0y0)
+  }, method="L-BFGS-B", control=list(fnscale=1),
+  lower=c(n0(setpr)[1], y0(setpr)[1]),
+  upper=c(n0(setpr)[2], y0(setpr)[2]), x=x)$value
+})
+
+betaprioupp <- sapply(betavec, function(x){
+  optim(par=c(4, 0.8), fn=function(.n0y0, x){
+    pbetany(x, .n0y0)
+  }, method="L-BFGS-B", control=list(fnscale=-1),
+  lower=c(n0(setpr)[1], y0(setpr)[1]),
+  upper=c(n0(setpr)[2], y0(setpr)[2]), x=x)$value
+})
+
[…]

### 2015-12-30 pdc-illu.R
parameter sets plot

@@ -18,6 +18,20 @@ nyupdate <- function (pr, data){
   c(nn,yn)
 }
 
+luck4cny <- function(luck, posterior=FALSE){
+  c1 <- c(n0(luck)[1], y0(luck)[1])
+  c2 <- c(n0(luck)[1], y0(luck)[2])
+  c3 <- c(n0(luck)[2], y0(luck)[1])
+  c4 <- c(n0(luck)[2], y0(luck)[2])
+  if(posterior){
+    c1 <- nyupdate(c1, c(tau(data(luck)), n(data(luck))))
+    c2 <- nyupdate(c2, c(tau(data(luck)), n(data(luck))))
+    c3 <- nyupdate(c3, c(tau(data(luck)), n(data(luck))))
+    c4 <- nyupdate(c4, c(tau(data(luck)), n(data(luck))))
+  }
+  list(c1=c1, c2=c2, c3=c3, c4=c4)
+}
+
 dbetany <- function(x, ny, ...){
   dbeta(x, shape1=ny[1]*ny[2], shape2=ny[1]*(1-ny[2]), ...)
 }
@@ -137,7 +151,8 @@ pdf("singleprior-pdc2.pdf", width=8, height=5)
 grid.arrange(betapdfcdf, pdcillupmfcmf, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
 
-# ------------------- sets of Beta pdfs, sets of Beta-Bin cmfs -------------------------
+
+# ------------------- sets of Beta pdfs, parameter sets, sets of Beta-Binomial cmfs -------------------------
 
 setpr <- BinomialLuckModel(n0=c(1,8), y0=c(0.7, 0.8))
 setpos1 <- setpr
@@ -145,11 +160,12 @@ data(setpos1) <- BinomialData(s=12, n=16)
 setpos2 <- setpr
 data(setpos2) <- BinomialData(s= 0, n=16)
 
-betavec <- seq(0,1, length.out=200)
+# Beta cdfs
+betavec <- seq(0,1, length.out=201)
 
-cdfplot(setpos1, xvec=betavec)
-cdfplot(setpos1, xvec=betavec, control=controlList(posterior=TRUE))
-cdfplot(setpos2, xvec=betavec, control=controlList(posterior=TRUE))
+#cdfplot(setpos1, xvec=betavec)
+#cdfplot(setpos1, xvec=betavec, control=controlList(posterior=TRUE))
[…]

### 2015-12-30 pdc-illu.R
bebin cmf sets (unfinished)

@@ -48,6 +48,15 @@ dbebinvec <- function(pos, m, l = NULL){
   }, m=m, n=pos[1], y=pos[2])
 }
 
+pbebinvec <- function(pos, m, l = NULL){
+  res <- dbebinvec(pos=pos, m=m, l=NULL)
+  res <- cumsum(res)
+  if(!is.null(l))
+    return(res[l+1])
+  else
+    return(res)
+}
+
 # one prior updated to posteriors with same variance
 sgpr <- c(8, 0.75) # n0, y0
 data1 <- c(12,16)  #  s,  n
@@ -281,7 +290,73 @@ paramset2 + theme(plot.margin = unit(c(0,0.5,0,-0.25), "lines"), legend.margin =
 dev.off()
 
 # sets of Beta-Binomial cmfs
+m <- 5
+lvec <- 0:m
 
-head(betasetdf)
+bebinpriolow <- sapply(lvec, function(x){
+  optim(par=c(4, 0.7), fn=function(.n0y0, m, x){
+    pbebinvec(.n0y0, m=m, l=x)
+  }, method="L-BFGS-B", control=list(fnscale=1),
+  lower=c(n0(setpr)[1], y0(setpr)[1]),
+  upper=c(n0(setpr)[2], y0(setpr)[2]), m=m, x=x)$value
+})
+
+bebinprioupp <- sapply(lvec, function(x){
+  optim(par=c(4, 0.8), fn=function(.n0y0, m, x){
+    pbebinvec(.n0y0, m=m, l=x)
+  }, method="L-BFGS-B", control=list(fnscale=-1),
+  lower=c(n0(setpr)[1], y0(setpr)[1]),
+  upper=c(n0(setpr)[2], y0(setpr)[2]), m=m, x=x)$value
+})
+
+bebinpriocorners <- sapply(luck4cny(setpr), function(x){
+  pbebinvec(x, m=m)
+})
+
+bebinpos1low <- sapply(lvec, function(x){
+  optim(par=c(4, 0.7), fn=function(.n0y0, m, x){
+    pbebinvec(nyupdate(pr=.n0y0, data=c(tau(data(setpos1)), n(data(setpos1)))), m=m, l=x)
+  }, method="L-BFGS-B", control=list(fnscale=1),
+  lower=c(n0(setpr)[1], y0(setpr)[1]),
+  upper=c(n0(setpr)[2], y0(setpr)[2]), m=m, x=x)$value
+})
+
[…]

### 2016-01-02 ijar-npb-ms.tex
Start writing software bits

@@
 %***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
-\begin{align*}
-\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)}\\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \\
+\begin{align}
+\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
  &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \\
+                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \nonumber \\
  &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \\ & \hspace*{12ex}
+    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
     \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
-                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,.
-\end{align*}
+                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,. \label{eq:LwrSysPost}
+\end{align}
 In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
@@
 %***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
-The method is implemented in the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}
-with the function \texttt{nonParBayesSystemInferencePriorSets()};
-the package also contains the function \texttt{computeSystemSurvivalSignature()}
-to calculate the survival signature for a given system layout (reliability block diagramm).
+
+\subsection{Software}
+
+The methods of this paper have been implemented in the \textbf{R}
+\citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
+providing an easy to use interface for reliability practitioners.  The
+primary function, which computes the upper and lower posterior
+predictive system survival probabilities as in \eqref{eq:LwrSysPost}, is
+named \texttt{nonParBayesSystemInferencePriorSets()}.  The user
+specifies the times at which to evaluate the bounds, the survival
+signature ($\Phi(\cdot)$), the component test data ($\vec{t}^1, \ldots,
+\vec{t}^K$), and the prior parameter set for each component type and
+time ($\PtZi{k}$, via $\nzu_{k,t}, \nzl_{k,t}, \yzu_{k,t}$, and
+$\yzl_{k,t}$).  All computations of $\lRsys$
+and $\uRsys$ at different time points are performed in parallel
+automatically where the CPU has multiple cores.
+
+Note that computation of the system signature itself can be simplified by
+expressing the structure of the system as an undirected graph using the
+\texttt{computeSystemSurvivalSignature()} function in the same package,
+leaving only data and prior to be handled.  These publicly available
+functions have been used in computing all the following examples for
+reproducibility.  \ref{ap:software} details how to use this software.
+
+\subsection{Examples}
 
@@
 
+\section*{Appendix}
+\appendix
+\renewcommand*{\thesection}{\Alph{section}}
+\section{Software details}
+\label{ap:software}
+
+Functions which make it easy to use the methods of this paper have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
+There are two functions of particular note: \texttt{computeSystemSurvivalSignature} and \texttt{nonParBayesSystemInferencePriorSets}
+
+\subsection{Computing the survival signature}
+
+The function \texttt{computeSystemSurvivalSignature} allows easy 
+computation of the survival signature if the system is expressed as an
+undirected graph with `start' and `terminal' nodes (which are not
+considered components for survival signature computation).  The system
+is considered to work if there is a path from the start to the terminal
+node passing only through functioning components.
+
+Graph representations of systems are most simply defined by using the 
+\texttt{graph.formula} function.  The `start' node should be denoted
+\texttt{s} and the `terminal' node should be denoted \texttt{t} and
+intermediate nodes (representing actual components) should be numbered and
+connected by edges denoted by \texttt{-}, where the numbering denotes physically
+distinct components.  Component numbers can be repeated to include
+multiple links.  For example, to build a simple three component series
+system:
+
+\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t)}
+
+and to build a three component parallel system:
+
+\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,t, s\,-\,2\,-\,t, s\,-\,3\,-\,t)}
+
+There is an additional shorthand which indicates a link exists to a list of multiple components separated by the \texttt{:} operator, so that the parallel system can be also be expressed more compactly by:
+
+\noindent\texttt{sys <- graph.formula(s\,-\,1:2:3\,-\,t)}
+
+Therefore, the simple bridge system of Figure \ref{fig:bridge-layout} can be constructed with:
+
+\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,1\,-\,4\,-\,5\,-\,t, 2:4\,-\,6\,-\,3:5)}
+\begin{itemize}
+  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component and going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
+  \item \texttt{s\,-\,1\,-\,4\,-\,5\,-\,t} signifies the bottom route through the block diagram;
+  \item \texttt{2:4\,-\,6\,-\,3:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
+\end{itemize}
+Naturally such as expression is not necessarily unique, so that completely equivalently one may write:
+
+\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2:4\,-\,6\,-\,3:5\,-\,t, 2\,-\,3, 4\,-\,5)}
+
+\
+
+With the structure defined and the individual components numbered, it 
+just remains to specify the types of each component.  This can be done
+using the \texttt{setCompTypes} function.  This function takes the
+system graph and a list of component type names and corresponding
+component numbers.  Thus, completing the example for Figure
+\ref{fig:bridge-layout}:
+\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}
+
+\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(2,3,4,5)))}
+
+\
+
+Computing the survival signature then involves a simple function call:
+\noindent\texttt{survsig <- computeSystemSurvivalSignature(sys)}
+
+\subsection{Computing sets of system survival probabilities}
+
+*** to be completed
+
 \end{document}

### 2016-01-04 ijar-npb-ms.tex
figure parameter sets

@@
 Such rectangular prior parameter sets $\PktZ$ have been shown
-to balance desirable model properties and ease of elicitation quite well.
+to balance desirable model properties and ease of elicitation quite well
+\citep[pp.~123f]{2013:diss-gw}; \citep{Troffaes2013a-short}.
 %
@@
 notwithstanding this, the model has favourable inference properties.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{paramsets}
+\caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
+for data $s^k_t/n_k = 12/16$ (left) and $s^k_t/n_k = 0/16$ (right).
+For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
+in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right).}
+\label{fig:paramsets}
+\end{figure}
 
@@
 how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
-leading to the so-called spotlight shape depicted in Figure***.
+leading to the so-called spotlight shape depicted in Figure~\ref{fig:paramsets} (left).
 As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
@@
 arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
-for lower $\nktn$ values than for higher $\nktn$ values, see Figure***.
+for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
 Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
@@
 
-\td{Figure with $\PN$s and sets of beta cdfs for conflict and no conflict case.}
+\td{Figure with sets of beta cdfs and beta-binom cmfs for conflict and no conflict case.}
 
@@
 \ref{fig:bridge-layout}:
+
 \noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}

### 2016-01-04 pdc-illu.R

@@ -289,6 +289,15 @@ pdf("paramsets.pdf", width=6, height=5)
 paramset2 + theme(plot.margin = unit(c(0,0.5,0,-0.25), "lines"), legend.margin = unit(-0.5, "cm"))
 dev.off()
 
+# in two separate facets
+paramset3 <- ggplot(paramsetdf) + geom_ribbon(aes(x=n0, ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
+paramset3 <- paramset3 + facet_grid(. ~ Facet) + xlab(expression(n^(0))) + ylab(expression(y^(0))) + rightlegend
+
+pdf("paramsets.pdf", width=6, height=2.5) # plot.margin: t r b f
+paramset3 + theme(plot.margin = unit(c(0,0.5,0,0), "lines"), legend.margin = unit(-0.0, "cm"))
+dev.off()
+
+
 # sets of Beta-Binomial cmfs
 m <- 5
 lvec <- 0:m

### 2016-01-04 ijar-npb-ms.tex
figure with sets of beta cdfs and sets of bebin cmfs, more small improvements in sections 5 and 6

@@
 identified from rewriting the density in a canonical form;
-see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}.
+see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}, or \citet[\S 1.2.3.1]{2013:diss-gw}.
 This canonical form gives a joint structure to all conjugate priors in exponential families.
@@
 and so can be described efficiently through the set of updated parameters
-\begin{align*}
+\begin{align}
 \PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
-\end{align*}
+\label{eq:paramsets}
+\end{align}
+Examples for parameter sets $\PktZ$ and $\PktN$ as in \eqref{eq:paramsets} are depicted in Figure~\ref{fig:paramsets}.
 Such rectangular prior parameter sets $\PktZ$ have been shown
@@
 \caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
-for data $s^k_t/n_k = 12/16$ (left) and $s^k_t/n_k = 0/16$ (right).
+for data $s^k_t/n_k = 12/16$ (Posterior 1, left) and $s^k_t/n_k = 0/16$ (Posterior 2, right).
 For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
-in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right).}
+in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right),
+leading to a large degree of imprecision in the $\yktn$ dimension of $\PktN$,
+thus reflecting increased uncertainty about the functioning probability $p^k_t$
+due to the conflict between prior assumptions and observed data.}
 \label{fig:paramsets}
@@
 for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
-Overall, this results in a wider $\yktn$ interval as compared to the non-conflict case, 
+Overall, this results in a wider $\yktn$ interval as compared to the no conflict case, 
 reflecting the extra uncertainty due to prior-data conflict,
@@
 
-\td{Figure with sets of beta cdfs and beta-binom cmfs for conflict and no conflict case.}
+Based on these shapes and \eqref{eq:nyupdate}, it is possible to deduce the following expressions
+for the lower and upper bounds of $\yktn$:
+\begin{align}
+\begin{aligned}
+\min_{\PktN} \yktn &=
+ \begin{cases}
+ %\dfrac{\nktzu \yktzl + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \ge \yktzl \\
+ \big(\nktzu \yktzl + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \ge \yktzl \\
+ %\dfrac{\nktzl \yktzl + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k <   \yktzl
+ \big(\nktzl \yktzl + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k <   \yktzl
+ \end{cases}\,,\\
+\max_{\PktN} \yktn &=
+ \begin{cases}
+ %\dfrac{\nktzu \yktzu + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \le \yktzu \\
+ \big(\nktzu \yktzu + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \le \yktzu \\
+ %\dfrac{\nktzl \yktzu + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k >   \yktzu
+ \big(\nktzl \yktzu + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k >   \yktzu
+ \end{cases}\,.
+\end{aligned}
+\label{eq:ysetupdate}
+\end{align}
+The lower bound for $\yktn$ is always attained for $\yktzl$, the upper bound for $\yktzu$.
+Note that when $s^k_t/n_k \in [\yktzl, \yktzu]$,
+both the lower and the upper bound for $\yktn$ are attained using $\nktzu$,
+this corresponds to the spotlight shape.
+When $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
+due to the banana shape
+we will get one of the bounds for $\yktn$ using $\nktzl$.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{betaset-binomset1}
+\caption{Sets of Beta pdfs (left) and Beta-Binomial cmfs (right, for $m_k=5$)
+corresponding to the prior and posterior parameter sets in Figure~\ref{fig:paramsets}.
+The sets are depicted as shaded areas,
+with the distributions corresponding to the four corners
+of the prior parameter set $\PktZ$ (or their posterior counterparts) as solid lines.
+The top row depicts the set of prior cdfs/cmfs and the set of posterior cdfs/cmfs for the case where data confirm prior assumptions
+(see left panel of Figure~\ref{fig:paramsets});
+the bottom row depicts the (identical) set of prior cdfs/cmfs and the set of posterior cdfs/cmfs in case of prior-data conflict
+(see right panel of Figure~\ref{fig:paramsets}).
+%The set of posteriors and the set of posterior predictive distributions
+The set of posterior cdfs and cmfs
+is much larger in case of prior-data conflict:
+uncertainty due to this conflict is reflected through increased imprecision.}
+\label{fig:betaset-binomset}
+\end{figure}
+
+The different locations and sizes of $\PktN$ in the conflict versus the no conflict case are then, in turn,
+also reflected in the corresponding sets of Beta cdfs and Beta-Binomial cmfs.
+As an example, the sets corresponding to the parameter sets in Figure~\ref{fig:paramsets}
+are depicted in Figure~\ref{fig:betaset-binomset}.
+
+In the no conflict case (Posterior 1, top row),
+the reduction of the $\yktn$ range in $\PktN$ leads to a much smaller set
+of Beta and Beta-Binomial distributions.
+E.g., the range of predictive probabilities
+that two out of a set of five components of type $k$ function at time $t$ 
+has changed from $[0.10, 0.28]$ to $[0.11,0.14]$.
+This reflects the gain in precision due to test data in accordance with prior assumptions.
+
+In the prior-data conflict case (Posterior 2, bottom row),
+the wide $\yktn$ range in $\PktN$ leads to a set of Beta and Beta-Binomial distributions
+that is much larger than in the no conflict case.
+Here, the range of posterior predictive probabilities
+that two out of a set of five components of type $k$ function at time $t$
+is now $[0.86, 1.00]$, i.e., less precise than in the no conflict case.
+Using sets of Beta priors, the resulting set of posterior predictive Beta-Binomial distributions
+adequately reflects the precision of prior information,
+the amount of data, and prior-data conflict.
 
 Furthermore, with sets of Beta priors it is also possible
-to express prior ignorance in a more adequate way,
+to express prior ignorance in an appropriate way,
 by letting $\yktzl \to 0$ and $\yktzu \to 1$
@@
 in the denominator of \eqref{eq:postpredCny} being zero.)
-Choosing these limits for $\yktz$ means that we are prepared to give trivial bounds for the functioning probability only,
+Choosing these limits for $\yktz$ means that we are prepared to give only trivial bounds for the functioning probability,
 and do not wish to make any commitments about $p^k_t$ a priori.
@@
 
-For an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
-as then one of the bounds for $\ykt$ is attained for $\nktzl$.
-In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
-as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
+%With the bounded domain for $\yktz$ 
+%\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
+%benavoli zaffalon papers***}
+%
+%As a note regarding the bounds for $\nktz$,
+%for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
+%as then one of the bounds for $\ykt$ is attained for $\nktzl$.
+%In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
+In a near-noninformative setting, the choice of $\nktzl$ is not relevant,
+as due to \eqref{eq:ysetupdate}, both lower and upper bound for $\yktn$ are obtained with $\nktzu$; 
 indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
@@
 Obviously, one cannot have prior-data conflict in case of prior near ignorance.
-
-\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
-benavoli zaffalon papers***}
 
@@
 It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
-Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to have it change with $t$ gradually only.
+Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to let them change with $t$ gradually only.
 
@@
 Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
-in a no-conflict situation, when $\nktzu = n_k$ $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
+in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
 In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
@@
 The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
-as is clear from Figure~***, the wider the $\nktz$ interval,
+as is clear from Figure~\ref{fig:paramsets} and \eqref{eq:ysetupdate}, the wider the $\nktz$ interval,
 the wider $[\yktnl, \yktnu]$ in case of conflict.
@@
 For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
-this can lead to improper posterior predictive distributions if $l_k=0$ or $l_k=m_k$.
+this can lead to improper posterior predictive distributions
+due to zero arguments for the Beta functions in the denominator of \eqref{eq:LwrSysPost}.
 %Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
@@
 as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
-We rather propose to elicit bounds only for a subset of ${\cal T}$,
-and to fill up the $t$ grid with the least committal bounds, i.e.,
+We rather propose to elicit bounds for a subset of ${\cal T}$ only,
+and to fill up the time grid with the least committal bounds, i.e.,
 taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
-an likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
+and likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
 A possible elicitation procedure in this vein could be
@@
 filling up the grid as described above accordingly,
-and then to further refine the obtained bounds if necessary.
+and then to further refine the obtained bounds as deemed necessary by the expert.
 %`middle' or `typical' $t$,

### 2016-01-04 pdc-illu.R

@@ -368,4 +368,27 @@ bebinsetdf <- rbind(data.frame(x=lvec, Lower=bebinpriolow, Upper=bebinprioupp, b
                     data.frame(x=lvec, Lower=bebinpos2low, Upper=bebinpos2upp, bebinpos2corners, Item="Posterior 2", Facet="Prior & Posterior 2"))
 bebinsetdf$Item <- ordered(bebinsetdf$Item, levels=c("Prior", "Posterior 1", "Posterior 2"))
 
+bebinset1 <- ggplot(bebinsetdf, aes(group=Item, colour=Item)) + geom_ribbon(aes(x=x, ymin=Lower, ymax=Upper, fill=Item), alpha=0.3)
+bebinset1 <- bebinset1 + #geom_point() +
+  geom_line(aes(x=x, y=c1)) + geom_point(aes(x=x, y=c1)) +
+  geom_line(aes(x=x, y=c2)) + geom_point(aes(x=x, y=c2)) +
+  geom_line(aes(x=x, y=c3)) + geom_point(aes(x=x, y=c3)) +
+  geom_line(aes(x=x, y=c4)) + geom_point(aes(x=x, y=c4))
+bebinset1 <- bebinset1 + facet_grid(Facet ~ .) + rightlegend + xlab(expression(l[k])) + ylab("cmf")
+bebinset1
+
+# plot.margin: t r b l
+betaset1  <- betaset1  + theme(plot.margin = unit(c(0,0.5,0,-0.0), "lines")) + 
+  guides(linetype="none", fill="none", group="none", colour="none")
+bebinset1 <- bebinset1 + theme(plot.margin = unit(c(0,0,  0,-0.0), "lines"),
+                                         legend.margin = unit(-0.0, "cm"))
+pdf("betaset-binomset1.pdf", width=8, height=5)
+grid.arrange(betaset1, bebinset1, nrow=1, ncol=2, widths=c(1,1.2))
+dev.off()
+
+# prior and posterior functioning probability ranges for l_k = 3:
+subset(bebinsetdf, (x==2) & (Facet=="Prior & Posterior 1") & (Item=="Prior"))
+subset(bebinsetdf, (x==2) & (Facet=="Prior & Posterior 1") & (Item=="Posterior 1"))
+subset(bebinsetdf, (x==2) & (Facet=="Prior & Posterior 2") & (Item=="Posterior 2"))
+
 #

### 2016-01-06 ijar-npb-ms.tex
setCompType() used, T1 <-> T3 in Fig 4

@@
 %\begin{scope}[scale=0.75]
-\node[type1] (T1)   at ( 0  , 0) {T1};
+\node[type1] (T3)   at ( 0  , 0) {T3};
 \node[type2] (T2)   at ( 2.8, 0) {T2};
-\node[type3] (T3-2) at ( 1.4, 1) {T3};
-\node[type3] (T3-3) at ( 1.4,-1) {T3};
-\node[type3] (T3-5) at ( 4.2, 1) {T3};
-\node[type3] (T3-6) at ( 4.2,-1) {T3};
+\node[type3] (T1-2) at ( 1.4, 1) {T1};
+\node[type3] (T1-3) at ( 1.4,-1) {T1};
+\node[type3] (T1-5) at ( 4.2, 1) {T1};
+\node[type3] (T1-6) at ( 4.2,-1) {T1};
 \coordinate (start) at (-1,0);
@@
 \coordinate (biend) at (4.9,0);
-\path (start)     edge[thick]   (T1.west)
-      (T1.east)   edge[thick]   (bista)
-      (bista)     edge[vh path] (T3-2.west)
-                  edge[vh path] (T3-3.west)
-      (T3-2.east) edge[hv path] (T2.north)
-      (T3-3.east) edge[hv path] (T2.south)
-      (T2.north)  edge[vh path] (T3-5.west)
-      (T2.south)  edge[vh path] (T3-6.west)
-      (T3-5.east) edge[hv path] (biend)
-      (T3-6.east) edge[hv path] (biend)
+\path (start)     edge[thick]   (T3.west)
+      (T3.east)   edge[thick]   (bista)
+      (bista)     edge[vh path] (T1-2.west)
+                  edge[vh path] (T1-3.west)
+      (T1-2.east) edge[hv path] (T2.north)
+      (T1-3.east) edge[hv path] (T2.south)
+      (T2.north)  edge[vh path] (T1-5.west)
+      (T2.south)  edge[vh path] (T1-6.west)
+      (T1-5.east) edge[hv path] (biend)
+      (T1-6.east) edge[hv path] (biend)
       (biend)     edge[thick]   (end);

### 2016-01-06 brakingsystem.R

@@ -42,11 +42,7 @@ oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLowe
 
 ab <- graph.formula(s -- M -- C1:C2:C3:C4, P1:P2:P3:P4 -- t,
                     C1 -- P1, C2 -- P2, C3 -- P3, C4 -- P4, s -- H -- P3:P4)
-V(ab)$compType <- NA
-V(ab)$compType[match(c("M"), V(ab)$name)] <- "M"
-V(ab)$compType[match(c("H"), V(ab)$name)] <- "H"
-V(ab)$compType[match(c("C1", "C2", "C3", "C4"), V(ab)$name)] <- "C"
-V(ab)$compType[match(c("P1", "P2", "P3", "P4"), V(ab)$name)] <- "P"
+ab <- setCompTypes(ab, list("M"=c("M"), "H"=c("H"), "C"=c("C1", "C2", "C3", "C4"), "P"=c("P1", "P2", "P3", "P4")))
 # data
 set.seed(233)
 Mdata <- rexp(5, rate=0.25)
@@ -82,11 +78,13 @@ abdf <- rbind(data.frame(abM, Part="M"), data.frame(abH, Part="H"), data.frame(a
                          Item=rep(c("Prior", "Posterior"), each=length(abt)), Part="System"))
 abdf$Item <- ordered(abdf$Item, levels=c("Prior", "Posterior"))
 #the plot
-ab1 <- ggplot(abdf) + geom_ribbon(aes(x=Time, ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
+ab1 <- ggplot(abdf, aes(x=Time))
+ab1 <- ab1 +  geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))
+ab1 <- ab1 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
 ab1 <- ab1 + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=abdat) + xlab("Time") + ylab("Survival Probability")
 ab1 <- ab1 + bottomlegend
 
-pdf("breakingsystem-1.pdf", width=8, height=5)
+pdf("breakingsystem-2.pdf", width=8, height=5)
 ab1
 dev.off()
 #

### 2016-01-06 bridgesystem.R

@@ -37,10 +37,7 @@ oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLowe
 # ----------------------------------------------
 
 b3 <- graph.formula(s -- 1 -- 2:3 -- 4 -- 5:6 --t, 2 -- 5, 3 -- 6)
-V(b3)$compType <- NA
-V(b3)$compType[match(c("1"), V(b3)$name)] <- "T1"
-V(b3)$compType[match(c("4"), V(b3)$name)] <- "T2"
-V(b3)$compType[match(c("2", "3", "5", "6"), V(b3)$name)] <- "T3"
+b3 <- setCompTypes(b3, list("T1"=c(1), "T2"=c(4), "T3"=c(2,3,5,6)))
 b3nulldata <- list("T1"=NULL, "T2"=NULL, "T3"=NULL)
 b3testdata <- list("T1"=c(2.0, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)/10+4) # T3 late failures
 b3testdata <- list("T1"=c(2.0, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)/10+0.5) # T3 early failures

### 2016-01-06 ijar-npb-ms.tex
T3 to the right in Fig 4

@@
 %\begin{scope}[scale=0.75]
-\node[type1] (T3)   at ( 0  , 0) {T3};
+\node[type1] (T3)   at ( 5.6, 0) {T3};
 \node[type2] (T2)   at ( 2.8, 0) {T2};
@@
 \node[type3] (T1-6) at ( 4.2,-1) {T1};
-\coordinate (start) at (-1,0);
-\coordinate (end)   at (5.6,0);
+\coordinate (start) at (0  ,0);
+\coordinate (end)   at (6.3,0);
 \coordinate (bista) at (0.7,0);
 \coordinate (biend) at (4.9,0);
-\path (start)     edge[thick]   (T3.west)
-      (T3.east)   edge[thick]   (bista)
-      (bista)     edge[vh path] (T1-2.west)
+\path (bista)     edge[hv path] (start)
+                  edge[vh path] (T1-2.west)
                   edge[vh path] (T1-3.west)
@@
       (T2.south)  edge[vh path] (T1-6.west)
-      (T1-5.east) edge[hv path] (biend)
-      (T1-6.east) edge[hv path] (biend)
-      (biend)     edge[thick]   (end);
+      (biend)     edge[vh path] (T1-5.east)
+                  edge[vh path] (T1-6.east)
+                  edge[hv path] (T3.west)
+      (T3.east)   edge[hv path] (end);
 %\end{scope}

### 2016-01-06 ijar-npb-ms.tex
Figs 5,6,7,8 updated (ggplot2 changes), text adjusted to T1 <-> T3 change

@@
 test data for components of type T1 and T2 are invariably taken as
-$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.
+$\vec{t}^1 = (2.2, 2.4, 2.6, 2.8)$ and $\vec{t}^2 = (3.2, 3.4, 3.6, 3.8)$, respectively.
 
@@
 due to the prior lower bound of zero for T1;
-for the system to function, the component of type T1 must function.
+for the system to function, at least two components of type T1 must function.
 
@@
 The imprecision carries over to the system bounds,
-where we see wider bounds as compared to the other scenarios
+where we see wider bounds as compared to the other two scenarios
 especially between $t=2$ and $t=4$.
@@
  vh path/.style={thick, to path={|- (\tikztotarget)}}]
-\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-1}};
+\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-2}};
 \begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]

### 2016-01-06 brakingsystem.R

@@ -52,6 +52,7 @@ Pdata <- rgamma(20, scale=0.9, shape=3.2)
 abnulldata <- list("M"=NULL, "H"=NULL, "C"=NULL, "P"=NULL)
 abtestdata <- list("M"=Mdata, "H"=Hdata, "C"=Cdata, "P"=Pdata)
 abdat <- melt(abtestdata); names(abdat) <- c("x", "Part")
+abdat$Part <- ordered(abdat$Part, levels=c("M", "H", "C", "P", "System"))
 absig <- computeSystemSurvivalSignature(ab)
 abt <- seq(0, 10, length.out=301)
 # priors
@@ -77,6 +78,7 @@ abdf <- rbind(data.frame(abM, Part="M"), data.frame(abH, Part="H"), data.frame(a
               data.frame(Time=rep(abt,2), Lower=c(abprio$lower,abpost$lower), Upper=c(abprio$upper,abpost$upper),
                          Item=rep(c("Prior", "Posterior"), each=length(abt)), Part="System"))
 abdf$Item <- ordered(abdf$Item, levels=c("Prior", "Posterior"))
+abdf$Part <- ordered(abdf$Part, levels=c("M", "H", "C", "P", "System"))
 #the plot
 ab1 <- ggplot(abdf, aes(x=Time))
 ab1 <- ab1 +  geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))

### 2016-01-06 bridgesystem.R

@@ -7,6 +7,9 @@ library("ReliabilityTheory")
 library(ggplot2)
 library(reshape2)
 
+bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
+rightlegend <- theme(legend.title = element_blank())
+
 # produces survival signature matrix for one component of type "name",
 # for use in nonParBayesSystemInference()
 oneCompSurvSign <- function(name){
@@ -36,13 +39,14 @@ oneCompPriorPostSet <- function(name, at.times, test.data, nLower, nUpper, yLowe
 
 # ----------------------------------------------
 
-b3 <- graph.formula(s -- 1 -- 2:3 -- 4 -- 5:6 --t, 2 -- 5, 3 -- 6)
-b3 <- setCompTypes(b3, list("T1"=c(1), "T2"=c(4), "T3"=c(2,3,5,6)))
+b3 <- graph.formula(s -- 2:3 -- 4 -- 5:6 -- 1 -- t, 2 -- 5, 3 -- 6)
+b3 <- setCompTypes(b3, list("T1"=c(2,3,5,6), "T2"=c(4), "T3"=c(1)))
 b3nulldata <- list("T1"=NULL, "T2"=NULL, "T3"=NULL)
-b3testdata <- list("T1"=c(2.0, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)/10+4) # T3 late failures
-b3testdata <- list("T1"=c(2.0, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)/10+0.5) # T3 early failures
-b3testdata <- list("T1"=c(2.0, 2.2, 2.4, 2.6), "T2"=c(3.0, 3.2, 3.4, 3.6), "T3"=(1:4)-0.5) # T3 fitting failures
+b3testdata <- list("T1"=c(2.2, 2.4, 2.6, 2.8), "T2"=c(3.2, 3.4, 3.6, 3.8), "T3"=(1:4)/10+4) # T3 late failures
+b3testdata <- list("T1"=c(2.2, 2.4, 2.6, 2.8), "T2"=c(3.2, 3.4, 3.6, 3.8), "T3"=(1:4)/10+0.5) # T3 early failures
[…]

### 2016-01-06 ijar-npb-ms.tex
Table 1 as booktab
switch to numbered citations

@@
-\documentclass[authoryear, 12pt, a4paper]{elsarticle}
+\documentclass[12pt, a4paper]{elsarticle}
 
@@
 \usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{booktabs}
 \usepackage{todonotes}
@@
 as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
-for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
+for example one can include common-cause failures quite straightforwardly into this approach \cite{CCM15}. %\citep[see][]{CCM15}.
 However, there is a substantial simplification
@@
 to balance desirable model properties and ease of elicitation quite well
-\citep[pp.~123f]{2013:diss-gw}; \citep{Troffaes2013a-short}.
+(see \citet[pp.~123f]{2013:diss-gw} or \citet{Troffaes2013a-short}).
 %
@@
 \centering
-\begin{tabular}{c|rrrrr}
+\begin{tabular}{crrrrr}
+\toprule
 $t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
-\hline
+\midrule
 $\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
-$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250
+$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250 \\
+\bottomrule
 \end{tabular}

### 2016-01-11 ijar-npb-ms.tex
Section 3 language tweaks -- feel free to roll back any/all of them!

@@
 
-In mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
+In the mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
 of its components and the structure of the system. The mathematical concept which is central to this theory is the 
@@
 
-For each time point $t$, the functioning of a single component of type $k$ at time $t$ (functioning: 1, failed: 0)
-is Bernoulli distributed with a suitable functioning probability (as, $1-$failure probability) $\ptk$, so
+At each time point $t$, the operational state of a single component of type $k$
+is Bernoulli distributed (functioning: 1, failed: 0) with parameter $\ptk$, so that
 \begin{align*}
@@
 \end{align*}
-in short, $\indic(T^k_i > t) \sim \ber(\ptk)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
-
-The set of functioning probabilities $\{ \ptk, t \in {\cal T}\}$
+That is, $\indic(T^k_i > t) \sim \ber(\ptk)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
+
+The set of probabilities $\{ \ptk, t \in {\cal T}\}$
 defines a discrete failure time distribution for components of type $k$ through
@@
 \end{align*}
-We can express this failure time distribution also through the probability mass function (pmf) and the discrete hazard function,
+We can also express this failure time distribution through the probability mass function (pmf) and discrete hazard function,
 \begin{align*}
@@
 \end{align*}
-We assume the time grid $\cal T$ is dense enough for the application at hand,
-otherwise it would be possible to assume, e.g.,
+The time grid $\cal T$ can be chosen to be appropriately dense for the application at hand,
+with the natural extension between grid points by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
 $R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
-or taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.
+or by taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.
 
@@
 
-Due to the independence assumption for components of the same type, 
-the number of functioning components out of the $m_k$ components of type $k$
+The independence assumption for components of the same type immediately implies that 
+the number of functioning components of type $k$ in the system
 is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(\ptk, m_k)$.
@@
 
-The $\ptk$'s can be taken such that they reflect, e.g., a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
+The $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
+$[0,\infty)$, for example matching a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
 Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
-
-However, directly choosing the $\ptk$'s is hard,
-and fixing values for all $p^k_t$ would furthermore neglect any inherent uncertainty in the particular choice.  
-To account for this uncertainty, one can express knowledge on $\ptk$ through a prior distribution.
-A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, a conjugate prior,
-leading to the posterior being again Beta.
-
-Having observed the lifetime data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$,
-at any fixed time $t \in {\cal T}$ this results in the observation from the Binomial model described above,
+However, such direct specification is non-trivial, neglects any inherent uncertainty in the particular choice, and cannot be 
+easily combined with test data.
+To account for the uncertainty, one can express knowledge about $\ptk$ through a prior distribution.
+A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, particularly because in a Bayesian inferential
+setting this is the conjugate prior which leads to a Beta posterior.
+
+Let the lifetime test data collected on component $k$ be $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$.
+At each fixed time $t \in {\cal T}$, this corresponds to an observation from the Binomial model described above,
 $s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
@@
 The posterior predictive distribution for the number of components surviving at time $t$
-of the $m_k$ components in the system, based on the lifetime data and the prior information,
+in a new system, based on the lifetime data and the prior information,
 is then a so-called Beta-Binomial distribution,
@@
 where $B(\cdot, \cdot)$ is the Beta function.
-This posterior predictive distribution is basically a Binomial distribution
+This posterior predictive distribution is essentially a Binomial distribution
 where the functioning probability $\ptk$ takes values in $[0,1]$
@@
 
-To wrap up, to calculate the system reliability according to \eqref{eq:rsyswithsurvsign},
-for each component type $k$,
+Consequently, in order to calculate the system reliability according to \eqref{eq:rsyswithsurvsign},
+for each component type $k$
 we need lifetime data $\vec{t}^k$,

### 2016-01-11 ijar-npb-ms.tex
Completion of software appendix.

@@
 \section{Sets of System Reliability Functions}
+\label{sec:setsofrel}
 
@@
 using the \texttt{setCompTypes} function.  This function takes the
-system graph and a list of component type names and corresponding
-component numbers.  Thus, completing the example for Figure
+system graph and a list of component type names (as the tag) and corresponding
+component numbers (as the value).  Thus, completing the example for Figure
 \ref{fig:bridge-layout}:
@@
 
-*** to be completed
+Once the system has been correctly described using an undirected graph
+as above, the methods presented in Sections \ref{sec:nonparamapproach}
+-- \ref{sec:setsofrel} can be used via the function
+\texttt{nonParBayesSystemInferencePriorSets}.
+
+The function prototype is:
+
+\noindent\texttt{nonParBayesSystemInferencePriorSets(at.times, survival.signature,}
+
+\noindent\texttt{~~~~~~~~~~test.data, nLower=2, nUpper=2, yLower=0.5, yUpper=0.5)}
+
+Aside from the system design, which can be passed to the function via
+the \texttt{survival.signature} argument, the remaining elements which
+must be specified are the:
+\begin{enumerate}
+  \item grid of times at which to evaluate the posterior, ${\cal T} = \{t_1, \ldots, \tmax\}$, via the \texttt{at.times} argument.
+  \item component test data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$ for $k=1,\dots,K$, via the \texttt{test.data} argument.
+  \item prior sets via the range of prior parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$, via the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower} and \texttt{yUpper} arguments.
+\end{enumerate}
+
+The grid of times, \texttt{at.times}, is specified as simply a vector 
+of time points.
+
+The \texttt{test.data} argument is a list of component type names (as
+the tag) and corresponding lifetime data (as the value), for example 
+a toy sized dataset for each component would be expressed as:
+
+\noindent\texttt{test.data=list("T1"=c(0.19, 0.73, 1.87, 1.17),}
+
+\noindent\texttt{~~~~~~~~~~~~~~~"T2"=c(0.22, 0.27, 0.63, 1.80, 1.25, 1.95),}
+
+\noindent\texttt{~~~~~~~~~~~~~~~"T3"=c(1.33, 0.65, 1.59))}
+
+Finally, there are multiple options for specifying the prior parameter
+sets.  Each of the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower}
+and \texttt{yUpper} arguments can be specified as:
+\begin{itemize}
+  \item a single value for a homogeneous prior across time and components.  e.g.\ \texttt{nLower=2} $\implies \nktzl=2 \ \forall\,k, t$
+  \item a vector of values of length $|{\cal T}|$ (\texttt{length(at.times)}), for a time inhomogeneous prior which is identical across component types.
+  \item a data frame of size $1\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time homogeneous prior which varies across component types.
+  \item a data frame of size $|{\cal T}|\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time inhomogeneous prior which varies across component types.
+\end{itemize}
+
+With these arguments supplied,  \texttt{nonParBayesSystemInferencePriorSets} will then compute
+the posterior sets automatically in parallel across the cores of a
+multicore CPU and return a list with two objects, named \texttt{lower} 
+and \texttt{upper}, containing respectively the lower and upper bound 
+for the system reliability function $\Rsys(t)$.
 

### 2016-01-12 ijar-npb-ms.tex
Update system in appendix to match new Figure 4.

@@
 
-\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,1\,-\,4\,-\,5\,-\,t, 2:4\,-\,6\,-\,3:5)}
+\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,4\,-\,5\,-\,3\,-\,t, 1:4\,-\,6\,-\,2:5)}
 \begin{itemize}
-  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component and going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
-  \item \texttt{s\,-\,1\,-\,4\,-\,5\,-\,t} signifies the bottom route through the block diagram;
-  \item \texttt{2:4\,-\,6\,-\,3:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
+  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
+  \item \texttt{s\,-\,4\,-\,5\,-\,3\,-\,t} signifies the bottom route through the block diagram;
+  \item \texttt{1:4\,-\,6\,-\,2:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
 \end{itemize}
@@
 
-\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2:4\,-\,6\,-\,3:5\,-\,t, 2\,-\,3, 4\,-\,5)}
+\noindent\texttt{sys <- graph.formula(s\,-\,1:4\,-\,6\,-\,2:5\,-\,3\,-\,t, 1\,-\,2, 4\,-\,5)}
 
@@
 
-\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1), "T2"=c(6),}
-
-\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(2,3,4,5)))}
+\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1,2,4,5), "T2"=c(6),}
+
+\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(3)))}
 

### 2016-01-12 ijar-npb-ms.tex
minor typos and tweaks

@@
 
-Let us denote the random failure time of component number $i$ of type $k$ by $T^k_i$, $i = 1, \ldots m_k$.
+Let us denote the random failure time of component number $i$ of type $k$ by $T^k_i$, $i = 1, \ldots, m_k$.
 The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
-or in terms of the reliability function $R^k(t) = P(T^k > t) = 1 - F^k(t)$,
+or in terms of the reliability function $R^k(t) = P(T^k_i > t) = 1 - F^k(t)$,
 also known as the survival function.
@@
 identified from rewriting the density in a canonical form;
-see, e.g., \citet[pp.~202 and 272f]{2000:bernardosmith}, or \citet[\S 1.2.3.1]{2013:diss-gw}.
-This canonical form gives a joint structure to all conjugate priors in exponential families.
+see, e.g., \cite[pp.~202 and 272f]{2000:bernardosmith}, or \cite[\S 1.2.3.1]{2013:diss-gw}.
+This canonical form gives a common structure to all conjugate priors in exponential families.
 
@@
 %based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
-given $s$ of $n$ components functioning.
+given that $s$ of $n$ components function.
 We have that
@@
 shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
-Also, the variance interval for $p_t^k$ will decrease
+Also, the variance interval for $p_t^k$ will shorten and shift towards zero,
 as the Beta distributions in $\MktN$ will be more pointed
@@
 When $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
-due to the banana shape
+the banana shape indicates that
 we will get one of the bounds for $\yktn$ using $\nktzl$.

### 2016-01-13 ijar-npb-ms.tex
text block for intro referring to a recent paper

@@
 Especially prior near ignorance can be modelled much more meaningfully than through usual so-called noninformative priors.
+
+*** prior-data conflict: more cautious probability statements
+(the reliability function is a collection of probability statements)
+
+*** Prior-data conflict has recently also been considered by \citet{2015:bickel},
+who, starting from a large class of reasonable models
+(which could be seen as stemming from a near-noninformative set of priors),
+identifies a subset of adequate models,
+selected according to a model adequacy measure that rejects a prior if it leads to prior-data conflict.
+
+ proposes a different approach
 

### 2016-01-13 ijar-npb-ms.tex
Section 4 language tweaks -- feel free to roll back any/all of them!

--- 2016-01-12 ijar-npb-ms.tex
@@
 The parametrisation of the Beta distribution used above is common,
-and allows to interpret $\alpha^k_t$ and $\beta^k_t$ as
+and allows $\alpha^k_t$ and $\beta^k_t$ to be interpreted as
 hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
-However, for our generalisation to sets of priors,
+However, when we generalise to sets of priors in the sequel,
 it is useful to consider a different parametrisation.
 
-For discussing this reparametrisation, we will drop the super- and subscript $k$ and $t$ for a while.
-Instead of $\alpha$ and $\beta$, we consider the parameters $\nz$ and $\yz$, where
+For clarity of presentation we will temporarily drop the super- and subscript $k$ and $t$ indices for component type and time.
+Instead of $\alpha$ and $\beta$, we consider the parameters $\nz \in [0, \infty)$ and $\yz \in [0,1]$, where
 \begin{align}
@@
 \end{align}
-or vice versa, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
-The upper index ${}\uz$ is used to identify $\nz$ and $\yz$ as prior parameter values,
+or equivalently, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
+The upper index ${}\uz$ is used to identify these as prior parameter values,
 in contrast to their posterior values $\nn$ and $\yn$
-obtained after observing $n$ failure times, see below.
+obtained after observing $n$ failure times (see below).
 $\nz$ and $\yz$ are sometimes called \emph{canonical} parameters,
-identified from rewriting the density in a canonical form;
-see, e.g., \cite[pp.~202 and 272f]{2000:bernardosmith}, or \cite[\S 1.2.3.1]{2013:diss-gw}.
-This canonical form gives a common structure to all conjugate priors in exponential families.
+identified from rewriting the density in canonical form;
+see for example \cite[pp.~202 and 272f]{2000:bernardosmith}, or \cite[\S 1.2.3.1]{2013:diss-gw}.
+This canonical form gives a common structure to all conjugacy results in exponential families.
 
@@
 it follows that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
-and that the higher $\nz$, the more probability weight will be concentrated around $\yz$,
-as $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
-Furthermore, $\nz$ can be interpreted as a pseudocount or prior strength,
-this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
-and will be further illustrated below through revisiting the posterior
-%based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
-given that $s$ of $n$ components function.
-We have that
-$p \mid s$ is Beta distributed with the updated parameters
+and that larger $\nz$ values lead to greater concentration of probability measure around $\yz$,
+since $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
+Consequently, $\nz$ represents the prior strength and moreover can be directly interpreted as a pseudocount, as will become clear.
+%this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
+%and will be further illustrated below through revisiting the posterior
+%%based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
+Indeed, consider the posterior given that $s$ out of $n$ components function:
+by conjugacy
+$p \mid s$ is Beta distributed with updated parameters
 \begin{align}
@@
 \end{align}
-After seeing that $s$ out of $n$ components function (at time $t$),
+Thus, after observing that $s$ out of $n$ components function (at time $t$),
 the posterior mean $\yn$ for $p$ is a weighted average of
 the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
-with the weights $\nz$ and $n$, respectively.
-We see that $\nz$ plays the same role for the prior mean $\yz$
-as the sample size $n$ for the observed mean $s/n$,
-thus the notion of pseudocount.
-Indeed, the higher $\nz$, the higher the weight for $\yz$
-in the weighted average calculation of $\yn$,
-so $\nz$ gives the strength of the prior as compared to the sample size $n$.
+with weights $\nz$ and $n$, respectively.
+Therefore $\nz$ takes on the same role for the prior mean $\yz$
+as the sample size $n$ does for the observed mean $s/n$,
+leading to the notion of it being a pseudocount.
+%Indeed, the higher $\nz$, the higher the weight for $\yz$
+%in the weighted average calculation of $\yn$,
+%so $\nz$ gives the strength of the prior as compared to the sample size $n$.
 %The parameters $\nz$ and $\yz$ have a more intuitive interprtation,
 
-The Beta-Binomial probability mass function (pmf) in terms of the updated parameters $\nn$ and $\yn$,
-now again with indicators $t$ and $k$,
-is therefore
+Reintroducing time and component type indices, the posterior predictive Beta-Binomial probability mass function (pmf) can be written in terms of the updated parameters as
 \begin{align}
@@
 \end{align}
-and the corresponding cumulative mass function (cmf) is given by
+with the corresponding cumulative mass function (cmf) given by
 \begin{align}
@@
 
-The parametrization in terms of prior mean and prior strength
-enables us to see that in this conjugate setting,
-learning from data amounts to averaging between prior and data.
-While this allows for the tractability of the model,
-it also comes with a serious drawback:
-When observed data are very much different from what is assumed in the prior,
-this conflict is simply averaged out,
-and is not reflected in the posterior or the posterior predictive.
-
-As a simple example, assume that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
+The parameterisation in terms of prior mean and prior strength (or pseudocount)
+makes clear that in this conjugate setting,
+learning from data corresponds to averaging between prior and data.
+This form is attractive not only because it enhances the interpretability of the model and prior specification,
+but crucially it also makes clear what should be a serious concern in any Bayesian analysis:
+when observed data differ greatly from what is expressed in the prior,
+this conflict is simply averaged out
+and is not reflected in the posterior or posterior predictive distributions.
+
+As a simple example, imagine that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
 so we choose $\yktz = 0.75$,
 and that we value this choice of mean functioning probability with $\nktz = 8$,
-i.e., like having seen $8$ observations with a mean $0.75$.
-Assume further that there are $n_k = 16$ components of type $k$ in the test data.
-When we observe $s^k_t = 12$ components functioning at time $t$,
-so $s^k_t/n_k = 0.75$ as we expect,
-then the updated parameters are $\nktn = 24, \yktn=0.75$.
-Unexpectedly observing that no component functions at time $t$ instead
+i.e., equivalently to having seen $8$ observations with a mean $0.75$.
+If we observe $n_k = 16$ components of type $k$ in the test data and $s^k_t = 12$ function at time $t$,
+then $s^k_t/n_k = 0.75$ as we expect,
+so that the updated parameters are $\nktn = 24, \yktn=0.75$.
+However, in contrast, unexpectedly observing that no component functions at time $t$ instead
 leads to parameters $\nktn = 24, \yktn=0.25$.
-The prior and the posteriors based on these two observation scenarios
+The prior and the posteriors based on these two scenarios
 are depicted in Figure~\ref{fig:singleprior-pdc}
-through their Beta densities and cdfs (left)
-and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
-for the case of $m_k = 5$ (right).
-
-Due to symmetry, we see that both posteriors have the same variance or spread,
+%through their Beta densities and cdfs (left)
+%and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
+for the case $m_k = 5$ (right).
+
+Due to symmetry, we see that both posteriors have the same variance,
 although arising from two fundamentally different scenarios.
@@
 the increase in confidence on $\ptk \approx 0.75$
-is reflected in a more pointed posterior density,
+is reflected in a more concentrated posterior density,
 and the posterior predictive is changed only slightly.
-It is quite disturbing to see the same degree of confidence in Posterior 2,
-being based on data in sharp conflict with prior expectations.
+However, it may be cause for concern to see the same degree of confidence in Posterior 2,
+which is based on data that is in sharp conflict with prior expectations.
 Posterior 2 places most probability weight around $0.25$,
 averaging between prior expectation and data,
-with the same variance or spread as Posterior 1.
-Instead of acknowledging the conflict between observed functioning probability zero
-and expected functioning probability $0.75$ by increased variance,
-Posterior 2 gives a false sense of certainty,
-also reflected in the posterior predictive,
-where both Posterior 1 and 2 have the same variance as well.
+with the same variance as Posterior 1.
+Accordingly, rather than conveying the conflict between observed
+and expected functioning probabilities with increased variance,
+Posterior 2 instead gives a false sense of certainty.
 
@@
 \caption{Beta densities (top left) and cdfs (bottom left),
-with the corresponding Beta-binomial probability mass functions (top right) and cumulative mass functions (bottom right),
+with the corresponding Beta-binomial posterior predictive probability mass functions (top right) and cumulative mass functions (bottom right),
 for a prior with $\nktz = 8, \yktz = 0.75$,
@@
 
-To counter this unwanted behaviour,
+To enable diagnosis of when this undesirable behaviour occurs,
 we propose to use an imprecise probability approach
-based on sets of Beta priors, described next.
+based on sets of Beta priors, described in the following section.
 

### 2016-01-14 ijar-npb-ms.tex
tweaking some of Louis' language edits of sec 4

@@
 The prior and the posteriors based on these two scenarios
-are depicted in Figure~\ref{fig:singleprior-pdc}
+are depicted in the left panels of Figure~\ref{fig:singleprior-pdc},
 %through their Beta densities and cdfs (left)
 %and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
-for the case $m_k = 5$ (right).
+along with their corresponding predictive Beta-binomial pmf and cmf
+for the case $m_k = 5$ (right panels).
 
@@
 \caption{Beta densities (top left) and cdfs (bottom left),
-with the corresponding Beta-binomial posterior predictive probability mass functions (top right) and cumulative mass functions (bottom right),
+with the corresponding Beta-binomial predictive probability mass functions (top right) and cumulative mass functions (bottom right),
 for a prior with $\nktz = 8, \yktz = 0.75$,

### 2016-01-14 ijar-npb-ms.tex
Section 5 language tweaks -- feel free to roll back any/all of them!

--- 2016-01-13 ijar-npb-ms.tex
@@
 we can have both tractability and meaningful reaction to prior-data conflict
-by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
-(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
+by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$
+(a detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
 In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
@@
 The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
-This element-by-element updating may seem ad-hoc, but can be rigorously justified
+This element-by-element updating can be rigorously justified
 as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
-Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
-obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
-and so can be described efficiently through the set of updated parameters
+Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$,
+obtained by updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
+leading to the set of updated parameters
 \begin{align}
@@
 \end{align}
+
 Examples for parameter sets $\PktZ$ and $\PktN$ as in \eqref{eq:paramsets} are depicted in Figure~\ref{fig:paramsets}.
 Such rectangular prior parameter sets $\PktZ$ have been shown
-to balance desirable model properties and ease of elicitation quite well
+to balance desirable model properties and ease of elicitation 
 (see \citet[pp.~123f]{2013:diss-gw} or \citet{Troffaes2013a-short}).
@@
 For each component type $k$ and time point $t$,
-one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
-(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
-prior knowledge on the survival function of components of type $k$);
-notwithstanding this, the model has favourable inference properties.
+one need only specify the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
+(so in total $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions
+on the survival function of each component.)
+%notwithstanding this, the model has favourable inference properties.
 
@@
 
-Central to these inference properties is that
-while the prior parameter set $\PktZ$ is rectangular,
-the posterior parameter set $\PktN$ is not rectangular anymore;
-indeed, the shape of $\PktN$ depends on the presence of prior-data conflict,
-which is naturally operationalized as $s^k_t/n_k \not\in [\yktzl, \yktzu]$:
-prior-data conflict is present when, at time $t$, the observed fraction of functioning components
-is outside its expected range.
-
-In absence of prior-data conflict, 
+A desirable inference property arising from this setup is that
+the posterior parameter set $\PktN$ is not rectangular in the way that the prior parameter set is.
+Indeed, the shape of $\PktN$ depends on the presence or absence of prior-data conflict,
+which is naturally operationalised as $s^k_t/n_k \not\in [\yktzl, \yktzu]$:
+that is, prior-data conflict is defined to occur when, at time $t$, the observed fraction of functioning components
+is outside its \emph{a priori} expected range.
+
+First, in the absence of prior-data conflict, 
 $\PktN$ shrinks in the $\ykt$ dimension;
-how much it shrinks depends on $\nktz \in [\nktzl, \nktzu]$,
+how much it shrinks depending on $\nktz \in [\nktzl, \nktzu]$,
 leading to the so-called spotlight shape depicted in Figure~\ref{fig:paramsets} (left).
-As $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
+Since $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
 shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
-Also, the variance interval for $p_t^k$ will shorten and shift towards zero,
-as the Beta distributions in $\MktN$ will be more pointed
+Also, the variance interval for $p_t^k$ (not shown) will shorten and shift towards zero,
+as the Beta distributions in $\MktN$ will be more concentrated
 due to the increase of $\nktz$ to $\nktn$.
 
-In case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl, \yktzu]$),
-$\PktN$ has instead the so-called banana shape,
-arising from $\yktn$ intervals being shifted closer towards $s^k_t/n_k$
+Alternatively, when there is conflict between prior and observed data (i.e.\ $s^k_t/n_k \not\in [\yktzl, \yktzu]$),
+$\PktN$ instead adopts the so-called `banana shape',
+arising from the intervals for $\yktn$  being shifted closer to $s^k_t/n_k$
 for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
-Overall, this results in a wider $\yktn$ interval as compared to the no conflict case, 
-reflecting the extra uncertainty due to prior-data conflict,
-thus making more cautious probability statements about $p_t^k$.
+Overall, this results in a wider $\yktn$ interval compared to the no conflict case, 
+reflecting the extra uncertainty due to prior-data conflict.  
+In other words, the posterior sets make more cautious probability statements about $p_t^k$, as desired in this scenario.
 
@@
 \end{align}
-The lower bound for $\yktn$ is always attained for $\yktzl$, the upper bound for $\yktzu$.
-Note that when $s^k_t/n_k \in [\yktzl, \yktzu]$,
-both the lower and the upper bound for $\yktn$ are attained using $\nktzu$,
-this corresponds to the spotlight shape.
-When $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
+Note that the lower bound for $\yktn$ is always attained at $\yktzl$, the upper bound at $\yktzu$.
+Also note that when $s^k_t/n_k \in [\yktzl, \yktzu]$,
+both the lower and the upper bounds for $\yktn$ are attained at $\nktzu$,
+corresponding to the spotlight shape.
+However, when $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
 the banana shape indicates that
-we will get one of the bounds for $\yktn$ using $\nktzl$.
+one of the bounds for $\yktn$ is attained at $\nktzl$.
 
@@
 
-The different locations and sizes of $\PktN$ in the conflict versus the no conflict case are then, in turn,
+The different locations and sizes of $\PktN$ in the conflict versus no conflict case are then, in turn,
 also reflected in the corresponding sets of Beta cdfs and Beta-Binomial cmfs.
-As an example, the sets corresponding to the parameter sets in Figure~\ref{fig:paramsets}
+As an example, those corresponding to the parameter sets in Figure~\ref{fig:paramsets}
 are depicted in Figure~\ref{fig:betaset-binomset}.
@@
 of Beta and Beta-Binomial distributions.
-E.g., the range of predictive probabilities
+For example, the range of predictive probabilities
 that two out of a set of five components of type $k$ function at time $t$ 
-has changed from $[0.10, 0.28]$ to $[0.11,0.14]$.
+has changed from $[0.10, 0.28]$ \emph{a priori} to $[0.11,0.14]$ \emph{a posteriori}.
 This reflects the gain in precision due to test data in accordance with prior assumptions.
 
-In the prior-data conflict case (Posterior 2, bottom row),
+In contrast, for the prior-data conflict case (Posterior 2, bottom row),
 the wide $\yktn$ range in $\PktN$ leads to a set of Beta and Beta-Binomial distributions
@@
 that two out of a set of five components of type $k$ function at time $t$
-is now $[0.86, 1.00]$, i.e., less precise than in the no conflict case.
+is now $[0.86, 1.00]$ \emph{a posteriori}, i.e., less precise than in the no conflict case.
 Using sets of Beta priors, the resulting set of posterior predictive Beta-Binomial distributions
-adequately reflects the precision of prior information,
+reflects the precision of prior information,
 the amount of data, and prior-data conflict.
@@
 Furthermore, with sets of Beta priors it is also possible
-to express prior ignorance in an appropriate way,
+to express prior ignorance
 by letting $\yktzl \to 0$ and $\yktzu \to 1$
 for some or all $t \in {\cal T}$.
-(It is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
+(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
 as this can lead to improper posterior predictive distributions.
-E.g., for any $t < \min(\vec{t}^k)$,
-we would get $\yktnu = 1$, leading to one argument of the Beta function
+For example, at any $t < \min(\vec{t}^k)$,
+we would have $\yktnu = 1$, leading to one argument of the Beta function
 in the denominator of \eqref{eq:postpredCny} being zero.)
-Choosing these limits for $\yktz$ means that we are prepared to give only trivial bounds for the functioning probability,
-and do not wish to make any commitments about $p^k_t$ a priori.
-Compare this to the uniform prior over $[0,1]$, a usual choice of `noninformative' prior,
-being a Beta prior with $\alpha^k_t = \beta^k_t = 1$, i.e., $\nktz = 2$, $\yktz = 0.5$.
-Taking this for all $t \in {\cal T}$ means that we expect the component reliability function
-to be on average 1/2 for all $t$, a very peculiar assumption,
-and, in our view, quite incompatible with the notion of prior ignorance.
+These limits for $\yktz$ imply we are only prepared to give trivial bounds for the functioning probability
+and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
+This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
+a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
+Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
+is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.
 
@@
 In a near-noninformative setting, the choice of $\nktzl$ is not relevant,
-as due to \eqref{eq:ysetupdate}, both lower and upper bound for $\yktn$ are obtained with $\nktzu$; 
-indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
+because \eqref{eq:ysetupdate} implies both lower and upper bound for $\yktn$ are obtained with $\nktzu$.
+In particular, $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
 $\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
-Obviously, one cannot have prior-data conflict in case of prior near ignorance.
+Naturally, one cannot have prior-data conflict in cases of near prior ignorance.
 

### 2016-01-15 ijar-npb-ms.tex
some text blocks on pdc for intro section and other minor stuff

@@
 
-(author order to be discussed of course)
-
 \section{Introduction}
@@
 Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
-naturally a Bayesian model for the functioning probability at each time point arises.
-To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict (see Section~***),
+naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
+To account for uncertainty in the choice of prior
+and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
 we propose an imprecise or interval probability approach
@@
 This approach also allows to adequately model weak or partial prior information.
-Especially prior near ignorance can be modelled much more meaningfully than through usual so-called noninformative priors.
-
-*** prior-data conflict: more cautious probability statements
-(the reliability function is a collection of probability statements)
-
-*** Prior-data conflict has recently also been considered by \citet{2015:bickel},
-who, starting from a large class of reasonable models
-(which could be seen as stemming from a near-noninformative set of priors),
+In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.
+
+Our imprecise probability approach leads to sets of system reliability functions,
+where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
+reflects the precision of the reliability estimate:
+a short range will indicate that we can quantify the reliability of the system quite precisely,
+while a large range will indicate that our (probabilistic) knowledge is rather shaky --
+remember that the reliability function is in essence a collection of probability statements.
+
+A central advantage of our imprecise probability model is
+that it leads to more cautious probability statements
+in case of \emph{prior-data conflict} \cite[see, e.g.,][]{2006:evans}:
+From the viewpoint of the expert, the observed failure times seem very surprising,
+i.e., information from data is in conflict with prior assumptions.
+This is most relevant when there is not enough data to overrule the prior;
+as it is then unclear whether to put more trust to prior assumptions or to the observations,
+posterior inferences should clearly reflect this state of uncertainty.
+
+As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
+prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
+ultimately conveying a false sense of certainty
+by communicating that we can quantify the reliability of the system quite precisely when in fact we can not.
+In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
+This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
+which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.
+
+Prior-data conflict has recently also been considered by \citet{2015:bickel},
+who, starting from a large class of reasonable models,
 identifies a subset of adequate models,
-selected according to a model adequacy measure that rejects a prior if it leads to prior-data conflict.
-
- proposes a different approach
+selected according to a model adequacy measure that allows to reject a prior if it leads to prior-data conflict.
 
@@
 \section{Reparametrisation of the Beta Distribution}
+\label{sec:reparam}
 
@@
 (so in total $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions
-on the survival function of each component.)
+on the survival function of each component).
 %notwithstanding this, the model has favourable inference properties.

### 2016-01-20 ijar-npb-ms.tex
New results in Section 6 (and proofs in appendix) on first-order stochastic dominance to avoid numerical optimisation for y and n.

--- 2016-01-14 ijar-npb-ms.tex
@@
 % ------------ custom defs -------------
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
 
@@
 
+The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
+providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
+is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
+enabling diagnoses of prior-data conflict which is consequential at the system
+level, via sets of system reliability functions.
+
 To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
@@
 where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
-It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
-as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
-
-To see this,
-remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
-From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
-%the posterior parameter set bounds are the transformed prior parameter set bounds,
-%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
-such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
+%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
+%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
 %
-Now, a higher posterior expected functioning probability means
-higher probability for many components out of $m_k$ surviving,
-i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
-Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
-its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
-such that the cmfs for different values of $\yktn$ do not cross each other.
-This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
-such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
-For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
-which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
+%To see this,
+%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
+%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
+%%the posterior parameter set bounds are the transformed prior parameter set bounds,
+%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
+%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
+%%
+%Now, a higher posterior expected functioning probability means
+%higher probability for many components out of $m_k$ surviving,
+%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
+%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
+%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
+%such that the cmfs for different values of $\yktn$ do not cross each other.
+%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
+%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
+%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
+%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
+%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
 We therefore have
@@
  &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
- &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \nonumber \\
- &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
+                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
-                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,. \label{eq:LwrSysPost}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
+                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
+    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
+    \,, \label{eq:LwrSysPostA}
 \end{align}
+and similarly maximising for $\uRsys(\cdot)$.
+
+Note that $\Phi(\cdot)$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
+thus if there is first-order stochastic ordering on $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$
+for each $k$, then this ordering can be used to determine the elements of $\PtZi{k}$
+which minimise and maximise the overall system reliability function without
+resorting to computationally expensive exhaustive searches or numerical optimisation.
+
+We therefore start by proving the following result, where indices are suppressed for readability.
+We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.
+
+\begin{theorem}
+  \label{thm:y}
+  Let $\beta_y$ denote the Beta-Binomial distribution with probability mass function parameterised as:
+  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
+  with $n, m, s,$ and $N$ fixed and unknown.
+
+  Then $\beta_{\yu} \ge_{\mathrm{st}} \beta_{\yl} \ \forall \ \yu > \yl$ with $\yu, \yl \in (0,1)$.
+\end{theorem}
+The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:y}.
+
+Consequently, for each component, the posterior predictive Beta Binomial distributions 
+with larger prior functioning probability stochastically dominate those
+with smaller prior functioning probability, providing rigorous proof 
+which accords with intuition. Applying this result to the sets of system reliability 
+functions, together with the monotonicity in the survival signature, means that
+$\lRsys(\cdot)$ is attained when $\yktz = \yktzl$ and $\uRsys(\cdot)$
+is attained when $\yktz = \yktzu$ for all possible $\nktz$ values.
+
+The analogous result for $\nktz$ is more subtle, because stochastic 
+dominance is not guaranteed at a single value.  The following Theorem 
+provides the conditions under which an upper or lower limit has first-order stochastic dominance.
+
+\begin{theorem}
+  \label{thm:n}
+  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
+  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
+  with $y, m, s,$ and $N$ fixed and unknown.  
+  Then,
+  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  and 
+  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+\end{theorem}
+The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.
+
+These first-order stochastic domination results now gives the exact 
+solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
+%For $\lRsys(\cdot)$, the minimum is achieved at
+%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
+%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
+%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
+%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
+%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
+\begin{align}
+\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
+ &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
+    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
+    \nonumber\\
+ &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
+ &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
+   \nktzu & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k < 0 \\
+   \nktzl & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k > 0 \\
+ \end{aligned} \right. \nonumber
+\end{align}
+
+\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}
+
 In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
@@
 \renewcommand*{\thesection}{\Alph{section}}
+
+\section{Proofs}
+\label{ap:proofs}
+
+\begin{proof}[\textbf{Proof of Theorem \ref{thm:y}, p\pageref{thm:y}}]
+  \label{prf:y}
+  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\yu}$ and $\beta_{\yl}$,
+  \begin{align*}
+    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid \yu, n, m, s, N)}{p(l \mid \yl, n, m, s, N)}} \\
+    &= \frac{B(l + n \yu + s, m - l + n (1 - \yu) + N - s) B(n \yl + s, n (1 - \yl) + N - s)}
+            {B(n \yu + s, n (1 - \yu) + N - s) B(l + n \yl + s, m - l + n (1 - \yl) + N - s)} \\
+    &= \frac{\Gamma(l + n \yu + s) \Gamma(m - l + n (1 - \yu) + N - s) \Gamma(n \yl + s) \Gamma(n (1 - \yl) + N - s)}
+            {\Gamma(l + n \yl + s) \Gamma(m - l + n (1 - \yl) + N - s) \Gamma(n \yu + s) \Gamma(n (1 - \yu) + N - s)} \\
+    &= \left\{ \begin{aligned}
+         \frac{\prod_{x=0}^{m-1} (x + n (1 - \yu) + N - s)}
+              {\prod_{x=0}^{m-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } l=0 \\
+         \frac{\prod_{x=0}^{l-1} (x + n \yu + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yu) + N - s)}
+              {\prod_{x=0}^{l-1} (x + n \yl + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } 0<l<m \\
+         \frac{\prod_{x=0}^{m-1} (x + n \yu + s)}
+              {\prod_{x=0}^{m-1} (x + n \yl + s)} &\quad\mbox{ for } l=m
+       \end{aligned} \right.
+  \end{align*}
+  since $\Gamma(x+1)=x \Gamma(x)$.
+
+  Thus,
+  \begin{align*}
+    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
+      \frac{(l + n \yu) (m - l - 1 + n (1 - \yl) + N - s)}
+           {(l + n \yl) (m - l - 1 + n (1 - \yu) + N - s)} \\
+    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
+  \end{align*}
+
+  Hence, $\mathcal{L}(\cdot)$ is monotone increasing for $0 < \yl < \yu < 1$, so that $\beta_{\yu}$ is larger than or equal to $\beta_{\yl}$ in monotone likelihood ratio order ($\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl}$).
+But, $\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl} \implies \beta_{\yu} \ge_\mathrm{st} \beta_{\yl}$ (\cite[Theorem 1.C.1, p.43]{shaked2007}) giving the required result.
+\end{proof}
+
+\begin{proof}[\textbf{Proof of Theorem \ref{thm:n}, p\pageref{thm:n}}]
+  \label{prf:n}
+  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\nu}$ and $\beta_{\nl}$,
+  \begin{align*}
+    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)}} \\
+    &= \frac{B(l + \nu y + s, m - l + \nu (1 - y) + N - s) B(\nl y + s, \nl (1 - y) + N - s)}
+            {B(\nu y + s, \nu (1 - y) + N - s) B(l + \nl y + s, m - l + \nl (1 - y) + N - s)} \\
+    &= \frac{\Gamma(l + \nu y + s) \Gamma(m - l + \nu (1 - y) + N - s)}
+            {\Gamma(l + \nl y + s) \Gamma(m - l + \nl (1 - y) + N - s)} \\
+    &\quad \times \frac{\Gamma(\nl y + s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu+N) \Gamma(m+\nl+N)}
+                       {\Gamma(\nu y + s) \Gamma(\nu (1 - y) + N - s)\Gamma(\nl+N) \Gamma(m+\nu+N)} \\
+    &= \left\{ \begin{aligned}
+         \frac{\prod_{x=0}^{m-1} (x + \nu (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nl + N)}
+              {\prod_{x=0}^{m-1} (x + \nl (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=0 \\
+         \frac{\prod_{x=0}^{l-1} (x + \nu y + s) \prod_{x=0}^{m-l-1} (x + \nu (1 - y) + N - s)}
+              {\prod_{x=0}^{l-1} (x + \nl y + s) \prod_{x=0}^{m-l-1} (x + \nl (1 - y) + N - s)} \\
+         \quad \times \frac{\prod_{x=0}^{m-1} (x + \nl + N)}{\prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } 0<l<m \\
+         \frac{\prod_{x=0}^{m-1} (x + \nu y + s) \prod_{x=0}^{m-1} (x + \nl + N)}
+              {\prod_{x=0}^{m-1} (x + \nl y + s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=m
+       \end{aligned} \right.
+  \end{align*}
+  since $\Gamma(x+1)=x \Gamma(x)$.
+
+  Thus,
+  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
+      \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
+           {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
+  \]
+
+  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
+  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
+  for the other parameters, so that necessary conditions for
+  monotonicity (either increasing or decreasing) must be established.
+  We require,
+  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
+          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
+     >1
+  \]
+  After extensive routine algebra, this can be conveniently expressed as
+  \begin{align*}
+    (\nu - \nl)[y (N + m) - s - y] - l (\nu - \nl)>0.
+  \end{align*}
+  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
+  Thus, for monotonicity to hold for all $l$, we require
+  \begin{align*}
+    (\nu - \nl)[y (N + m) - s - y] - m (\nu - \nl) &>0 \\
+    \implies (\nu - \nl)[y (N + m - 1) - s - y] &>0
+  \end{align*}
+  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
+  likelihood ratio only when \[ y (N + m - 1) - s - y > 0. \]  Likewise 
+  the likelihood ratio is only monotonically decreasing when
+  \[ y (N + m - 1) - s - y < 0. \]
+  Thus,
+  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  and 
+  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+  by \cite[Theorem 1.C.1, p.43]{shaked2007}.
+\end{proof}
+
 \section{Software details}

### 2016-01-21 brakingsystem.R
plots: 2 colours only, different colour scheme, white background

@@ -80,7 +80,8 @@ abdf <- rbind(data.frame(abM, Part="M"), data.frame(abH, Part="H"), data.frame(a
 abdf$Item <- ordered(abdf$Item, levels=c("Prior", "Posterior"))
 abdf$Part <- ordered(abdf$Part, levels=c("M", "H", "C", "P", "System"))
 #the plot
-ab1 <- ggplot(abdf, aes(x=Time))
+ab1 <- ggplot(abdf, aes(x=Time)) + theme_bw()
+ab1 <- ab1 + scale_fill_manual(values = c("#b2df8a", "#1f78b4")) + scale_colour_manual(values = c("#b2df8a", "#1f78b4"))
 ab1 <- ab1 +  geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))
 ab1 <- ab1 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
 ab1 <- ab1 + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=abdat) + xlab("Time") + ylab("Survival Probability")

### 2016-01-21 bridgesystem.R

@@ -6,6 +6,7 @@
 library("ReliabilityTheory")
 library(ggplot2)
 library(reshape2)
+library(RColorBrewer)
 
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
 rightlegend <- theme(legend.title = element_blank())
@@ -66,9 +67,12 @@ b3df <- rbind(data.frame(b3T1, Part="T1"), data.frame(b3T2, Part="T2"), data.fra
 b3df$Item <- ordered(b3df$Item, levels=c("Prior", "Posterior"))
 b3df$Part <- ordered(b3df$Part, levels=c("T1", "T2", "T3", "System"))
 
-p3 <- ggplot(b3df, aes(x=Time)) + rightlegend
+# + scale_colour_manual(values = c("red","blue"))
+# + scale_fill_brewer(palette="Set3")
+p3 <- ggplot(b3df, aes(x=Time)) + rightlegend + theme_bw()
+p3 <- p3 + scale_fill_manual(values = c("#b2df8a", "#1f78b4")) + scale_colour_manual(values = c("#b2df8a", "#1f78b4"))
 p3 <- p3 + geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))
-p3 <- p3 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
+p3 <- p3 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.5)
 p3 <- p3  + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=b3dat) + xlab("Time") + ylab("Survival Probability")
 pdf("bridge-latefailures.pdf", width=8, height=5)
 pdf("bridge-earlyfailures.pdf", width=8, height=5)

### 2016-01-21 pdc-illu.R

@@ -153,9 +153,9 @@ pdf("singleprior-pdc.pdf", width=8, height=3)
 grid.arrange(betadens2, pdcillu, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
 
-betapdfcdf      <- betapdfcdf    + theme(plot.margin = unit(c(0,0.5,0,-0.75), "lines"))
+betapdfcdf      <- betapdfcdf    + theme(plot.margin = unit(c(0,0.5,0,-0.75), "lines")) + theme_bw()
 pdcillupmfcmf   <- pdcillupmfcmf + theme(plot.margin = unit(c(0,0,  0,-0.75), "lines"),
-                                    legend.margin = unit(-0.5, "cm"))
+                                    legend.margin = unit(-0.5, "cm")) + theme_bw()
 pdf("singleprior-pdc2.pdf", width=8, height=5)
 grid.arrange(betapdfcdf, pdcillupmfcmf, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
@@ -236,67 +236,21 @@ betapos2corners <- sapply(luck4cny(setpos2, posterior=TRUE), function(x){
   pbetany(betavec, x)
 })
 
-betasetdf <- rbind(data.frame(x=betavec, Lower=betapriolow, Upper=betaprioupp, betapriocorners, Item="Prior", Facet="Prior & Posterior 1"),
-                   data.frame(x=betavec, Lower=betapos1low, Upper=betapos1upp, betapos1corners, Item="Posterior 1", Facet="Prior & Posterior 1"),
-                   data.frame(x=betavec, Lower=betapriolow, Upper=betaprioupp, betapriocorners, Item="Prior", Facet="Prior & Posterior 2"),
-                   data.frame(x=betavec, Lower=betapos2low, Upper=betapos2upp, betapos2corners, Item="Posterior 2", Facet="Prior & Posterior 2"))
+betasetdf <- rbind(data.frame(x=betavec, Lower=betapriolow, Upper=betaprioupp, betapriocorners, Facet="Prior & Posterior 1", Item="Prior", Item2="Prior"),
+                   data.frame(x=betavec, Lower=betapos1low, Upper=betapos1upp, betapos1corners, Facet="Prior & Posterior 1", Item="Posterior 1", Item2="Posterior"),
[…]

### 2016-01-21 ijar-npb-ms.tex
Fix typos in proofs
Fix typo and small logical gap in Theorems & Proofs.

@@
   Then,
-  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
   and 
-  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+  If $\frac{s}{N + m - 1} < y < \frac{s + m}{N + m - 1}$ then first-order stochastic dominance is not guaranteed.
 \end{theorem}
@@
  &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
-   \nktzu & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k < 0 \\
-   \nktzl & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k > 0 \\
+   \nktzu & \quad\mbox{if}\quad \yktzl < \frac{s}{N + m - 1} \\
+   \nktzl & \quad\mbox{if}\quad \yktzl > \frac{s + m}{N + m - 1} \\
+   \mathrm{optimised} & \quad\mbox{if}\quad \frac{s}{N + m - 1} < \yktzl < \frac{s + m}{N + m - 1}
  \end{aligned} \right. \nonumber
@@
     \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
-      \frac{(l + n \yu) (m - l - 1 + n (1 - \yl) + N - s)}
-           {(l + n \yl) (m - l - 1 + n (1 - \yu) + N - s)} \\
+      \frac{(l + n \yu + s) (m - l - 1 + n (1 - \yl) + N - s)}
+           {(l + n \yl + s) (m - l - 1 + n (1 - \yu) + N - s)} \\
     &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
@@
   \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
-      \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
-           {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
+      \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
+           {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
   \]
@@
   \begin{align*}
-    (\nu - \nl)[y (N + m) - s - y] - l (\nu - \nl)>0.
+    (\nu - \nl)[y (N + m - 1) - s] - l (\nu - \nl)>0.
   \end{align*}
@@
   \begin{align*}
-    (\nu - \nl)[y (N + m) - s - y] - m (\nu - \nl) &>0 \\
-    \implies (\nu - \nl)[y (N + m - 1) - s - y] &>0
+    (\nu - \nl)[y (N + m - 1) - s] - m (\nu - \nl) &>0 \\
+    \implies (\nu - \nl)[y (N + m - 1) - s - m] &>0
   \end{align*}
   Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
-  likelihood ratio only when \[ y (N + m - 1) - s - y > 0. \]  Likewise 
-  the likelihood ratio is only monotonically decreasing when
-  \[ y (N + m - 1) - s - y < 0. \]
+  likelihood ratio only when \[ y (N + m - 1) - s - m > 0. \]
+  By a similar argument, the likelihood ratio is only monotonically decreasing when
+  \[ y (N + m - 1) - s < 0. \]
   Thus,
-  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
   and 
-  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-  by \cite[Theorem 1.C.1, p.43]{shaked2007}.
+  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+  by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
+  \[ \frac{s}{N+m-1} < y < \frac{s+m}{N+m-1} \]
+  we cannot definitively state the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
 \end{proof}

### 2016-01-21 ijar-npb-ms.tex
Another missed +s !!
comments Frank on secs 1,2 and 8

--- 2016-01-20 ijar-npb-ms.tex
@@
 % ------------ custom defs -------------
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
 
@@
 
-Based on expert assumptions for component failure distribution and component test data,
+Based on expert assumptions for component failure distributions and component test data,
 we make predictive inference for a system with components that are exchangeable
@@
 and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
-we propose an imprecise or interval probability approach
+we propose an imprecise probability approach
 based on sets of prior distributions defined through sets of canonical parameters.
@@
 
-Our imprecise probability approach leads to sets of system reliability functions,
-where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
-reflects the precision of the reliability estimate:
-a short range will indicate that we can quantify the reliability of the system quite precisely,
-while a large range will indicate that our (probabilistic) knowledge is rather shaky --
-remember that the reliability function is in essence a collection of probability statements.
+%Our imprecise probability approach leads to sets of system reliability functions,
+%where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
+%reflects the precision of the reliability estimate:
+%a short range will indicate that we can quantify the reliability of the system quite precisely,
+%while a large range will indicate that our (probabilistic) knowledge is rather shaky --
+%remember that the reliability function is in essence a collection of probability statements.
+Our imprecise probability approach leads, for each $t$ in some grid of time points ${\cal T}$,
+to a posterior predictive probability interval for the event that the system will function at time $t$.
+The width of these intervals reflects the precision of the probability statement:
+a short range will indicate that we can quantify the system functioning probability quite precisely,
+while a large range will indicate that our (probabilistic) knowledge is indeterminate.
 
@@
 ultimately conveying a false sense of certainty
-by communicating that we can quantify the reliability of the system quite precisely when in fact we can not.
+by communicating that we can quantify the reliability of the system quite precisely when in fact we cannot do so.
 In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
@@
 This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
-***This step is less trivial here as we must ensure to have probability distributions for these events,
-thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
-***covered because of parametric distribution, min and max over parameter sets (see section 6)***
-***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
-see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
-\td{Leave out the sentences framed with `***'?}
-Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
-to reflect uncertainty about system functioning for known states of its components.
-A further suggestion was to generalize this to lower and upper structure functions,
-within the theory of imprecise probability \citep{itip,CU11}.
-These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
-which in the latter case also becomes an imprecise probability.
-
-The survival signature is a powerful but rather basic concept.
-As such, further generalizations are conceptually easy,
-for example one can straightforwardly generalize the survival signature to multi-state systems
-such that it again summarizes the structure function
-in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
+Like \citet{CCMA14}, we will utilize the monotonicity of the survival signature for coherent systems
+to simplify computations.
 
@@
 
-The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
-providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
-is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
-enabling diagnoses of prior-data conflict which is consequential at the system
-level, via sets of system reliability functions.
-
 To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
@@
 where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
-%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
-%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
+It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
+as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
+
+To see this,
+remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
+From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
+%the posterior parameter set bounds are the transformed prior parameter set bounds,
+%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
+such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
 %
-%To see this,
-%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
-%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
-%%the posterior parameter set bounds are the transformed prior parameter set bounds,
-%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
-%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
-%%
-%Now, a higher posterior expected functioning probability means
-%higher probability for many components out of $m_k$ surviving,
-%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
-%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
-%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
-%such that the cmfs for different values of $\yktn$ do not cross each other.
-%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
-%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
-%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
-%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
+Now, a higher posterior expected functioning probability means
+higher probability for many components out of $m_k$ surviving,
+i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
+Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
+its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
+such that the cmfs for different values of $\yktn$ do not cross each other.
+This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
+such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
+For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
+thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
+which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
 We therefore have
@@
  &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
+ &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
+                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktzl, \nktz, s^k_t) \nonumber \\
+ &= \min_{\nz_{1,t},\ldots,\nz_{K,t}} 
     \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
-                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
-    \,, \label{eq:LwrSysPostA}
+    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\ynl_{k,t}, m_k - l_k + \nn_{k,t}(1-\ynl_{k,t}))}
+                                         {B(\nn_{k,t}\ynl_{k,t}, \nn_{k,t}(1-\ynl_{k,t}))} \,. \label{eq:LwrSysPost}
 \end{align}
-and similarly maximising for $\uRsys(\cdot)$.
-
-Note that $\Phi(\cdot)$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-thus if there is first-order stochastic ordering on $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$
-for each $k$, then this ordering can be used to determine the elements of $\PtZi{k}$
-which minimise and maximise the overall system reliability function without
-resorting to computationally expensive exhaustive searches or numerical optimisation.
-
-We therefore start by proving the following result, where indices are suppressed for readability.
-We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.
-
-\begin{theorem}
-  \label{thm:y}
-  Let $\beta_y$ denote the Beta-Binomial distribution with probability mass function parameterised as:
-  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
-  with $n, m, s,$ and $N$ fixed and unknown.
-
-  Then $\beta_{\yu} \ge_{\mathrm{st}} \beta_{\yl} \ \forall \ \yu > \yl$ with $\yu, \yl \in (0,1)$.
-\end{theorem}
-The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:y}.
-
-Consequently, for each component, the posterior predictive Beta Binomial distributions 
-with larger prior functioning probability stochastically dominate those
-with smaller prior functioning probability, providing rigorous proof 
-which accords with intuition. Applying this result to the sets of system reliability 
-functions, together with the monotonicity in the survival signature, means that
-$\lRsys(\cdot)$ is attained when $\yktz = \yktzl$ and $\uRsys(\cdot)$
-is attained when $\yktz = \yktzu$ for all possible $\nktz$ values.
-
-The analogous result for $\nktz$ is more subtle, because stochastic 
-dominance is not guaranteed at a single value.  The following Theorem 
-provides the conditions under which an upper or lower limit has first-order stochastic dominance.
-
-\begin{theorem}
-  \label{thm:n}
-  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
-  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
-  with $y, m, s,$ and $N$ fixed and unknown.  
-  Then,
-  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
-  and 
-  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-\end{theorem}
-The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.
-
-These first-order stochastic domination results now gives the exact 
-solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
-%For $\lRsys(\cdot)$, the minimum is achieved at
-%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
-%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
-%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
-%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
-%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
-\begin{align}
-\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
-    \nonumber\\
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
- &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
-   \nktzu & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k < 0 \\
-   \nktzl & \quad\mbox{if}\quad \yktzl(n_k+m_k-1)-s^k_t-m_k > 0 \\
- \end{aligned} \right. \nonumber
-\end{align}
-
-\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}
-
 In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
@@
 
+The survival signature and its use for uncertainty quantification for system
+reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
+For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
+to reflect uncertainty about system functioning for known states of its components, with a further
+generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
+survival signature to multi-state systems such that it again summarizes the structure function
+in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
+
 ***Extend the model to deal with right-censored observations which are common in the reliability setting.
-We believe that a minimal assumption (component can fail immediately after censoring or live forever)
-will be simple to implememt but will lead to high imprecision,
+The minimal assumption that a component can either fail immediately after censoring or live forever
+will be simple to implement but will lead to high imprecision,
 whereas assuming exchangeability with other surviving components at moment of censoring
 will be more complex to accomodate but will lead to less imprecision.
+This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
+and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
 
@@
 \renewcommand*{\thesection}{\Alph{section}}
-
-\section{Proofs}
-\label{ap:proofs}
-
-\begin{proof}[\textbf{Proof of Theorem \ref{thm:y}, p\pageref{thm:y}}]
-  \label{prf:y}
-  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\yu}$ and $\beta_{\yl}$,
-  \begin{align*}
-    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid \yu, n, m, s, N)}{p(l \mid \yl, n, m, s, N)}} \\
-    &= \frac{B(l + n \yu + s, m - l + n (1 - \yu) + N - s) B(n \yl + s, n (1 - \yl) + N - s)}
-            {B(n \yu + s, n (1 - \yu) + N - s) B(l + n \yl + s, m - l + n (1 - \yl) + N - s)} \\
-    &= \frac{\Gamma(l + n \yu + s) \Gamma(m - l + n (1 - \yu) + N - s) \Gamma(n \yl + s) \Gamma(n (1 - \yl) + N - s)}
-            {\Gamma(l + n \yl + s) \Gamma(m - l + n (1 - \yl) + N - s) \Gamma(n \yu + s) \Gamma(n (1 - \yu) + N - s)} \\
-    &= \left\{ \begin{aligned}
-         \frac{\prod_{x=0}^{m-1} (x + n (1 - \yu) + N - s)}
-              {\prod_{x=0}^{m-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } l=0 \\
-         \frac{\prod_{x=0}^{l-1} (x + n \yu + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yu) + N - s)}
-              {\prod_{x=0}^{l-1} (x + n \yl + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } 0<l<m \\
-         \frac{\prod_{x=0}^{m-1} (x + n \yu + s)}
-              {\prod_{x=0}^{m-1} (x + n \yl + s)} &\quad\mbox{ for } l=m
-       \end{aligned} \right.
-  \end{align*}
-  since $\Gamma(x+1)=x \Gamma(x)$.
-
-  Thus,
-  \begin{align*}
-    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
-      \frac{(l + n \yu) (m - l - 1 + n (1 - \yl) + N - s)}
-           {(l + n \yl) (m - l - 1 + n (1 - \yu) + N - s)} \\
-    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
-  \end{align*}
-
-  Hence, $\mathcal{L}(\cdot)$ is monotone increasing for $0 < \yl < \yu < 1$, so that $\beta_{\yu}$ is larger than or equal to $\beta_{\yl}$ in monotone likelihood ratio order ($\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl}$).
-But, $\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl} \implies \beta_{\yu} \ge_\mathrm{st} \beta_{\yl}$ (\cite[Theorem 1.C.1, p.43]{shaked2007}) giving the required result.
-\end{proof}
-
-\begin{proof}[\textbf{Proof of Theorem \ref{thm:n}, p\pageref{thm:n}}]
-  \label{prf:n}
-  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\nu}$ and $\beta_{\nl}$,
-  \begin{align*}
-    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)}} \\
-    &= \frac{B(l + \nu y + s, m - l + \nu (1 - y) + N - s) B(\nl y + s, \nl (1 - y) + N - s)}
-            {B(\nu y + s, \nu (1 - y) + N - s) B(l + \nl y + s, m - l + \nl (1 - y) + N - s)} \\
-    &= \frac{\Gamma(l + \nu y + s) \Gamma(m - l + \nu (1 - y) + N - s)}
-            {\Gamma(l + \nl y + s) \Gamma(m - l + \nl (1 - y) + N - s)} \\
-    &\quad \times \frac{\Gamma(\nl y + s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu+N) \Gamma(m+\nl+N)}
-                       {\Gamma(\nu y + s) \Gamma(\nu (1 - y) + N - s)\Gamma(\nl+N) \Gamma(m+\nu+N)} \\
-    &= \left\{ \begin{aligned}
-         \frac{\prod_{x=0}^{m-1} (x + \nu (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nl + N)}
-              {\prod_{x=0}^{m-1} (x + \nl (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=0 \\
-         \frac{\prod_{x=0}^{l-1} (x + \nu y + s) \prod_{x=0}^{m-l-1} (x + \nu (1 - y) + N - s)}
-              {\prod_{x=0}^{l-1} (x + \nl y + s) \prod_{x=0}^{m-l-1} (x + \nl (1 - y) + N - s)} \\
-         \quad \times \frac{\prod_{x=0}^{m-1} (x + \nl + N)}{\prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } 0<l<m \\
-         \frac{\prod_{x=0}^{m-1} (x + \nu y + s) \prod_{x=0}^{m-1} (x + \nl + N)}
-              {\prod_{x=0}^{m-1} (x + \nl y + s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=m
-       \end{aligned} \right.
-  \end{align*}
-  since $\Gamma(x+1)=x \Gamma(x)$.
-
-  Thus,
-  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
-      \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
-           {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
-  \]
-
-  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
-  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
-  for the other parameters, so that necessary conditions for
-  monotonicity (either increasing or decreasing) must be established.
-  We require,
-  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
-          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
-     >1
-  \]
-  After extensive routine algebra, this can be conveniently expressed as
-  \begin{align*}
-    (\nu - \nl)[y (N + m) - s - y] - l (\nu - \nl)>0.
-  \end{align*}
-  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
-  Thus, for monotonicity to hold for all $l$, we require
-  \begin{align*}
-    (\nu - \nl)[y (N + m) - s - y] - m (\nu - \nl) &>0 \\
-    \implies (\nu - \nl)[y (N + m - 1) - s - y] &>0
-  \end{align*}
-  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
-  likelihood ratio only when \[ y (N + m - 1) - s - y > 0. \]  Likewise 
-  the likelihood ratio is only monotonically decreasing when
-  \[ y (N + m - 1) - s - y < 0. \]
-  Thus,
-  \[ y(N+m-1)-s-m > 0 \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
-  and 
-  \[ y(N+m-1)-s-m < 0 \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-  by \cite[Theorem 1.C.1, p.43]{shaked2007}.
-\end{proof}
-
 \section{Software details}

### 2016-01-21 ijar-npb-ms.tex

--- 2016-01-21 ijar-npb-ms.tex
@@
   We require,
-  \[ \frac{(l + \nu y) (m - l - 1 + \nl (1 - y) + N - s)}
-          {(l + \nl y) (m - l - 1 + \nu (1 - y) + N - s)}
+  \[ \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
+          {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
      >1

### 2016-01-21 ijar-npb-ms.tex
fig 8 changed & brake now spelled correctly

@@
 
-***Another example: simplified automotive breaking system, Figure~\ref{fig:breakingsystem}.
+***Another example: simplified automotive brake system, Figure~\ref{fig:brakesystem}.
 Prior sets and data exemplary only, prior bounds more smooth curves?
-The master breaking cylinder (M) activates all four wheel braking cylinders (C1 -- C4),
+The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
 which in turn actuate a braking pad assembly each (P1 -- P4).
-The hand break mechanism (H) goes directly to two brake pad assemblies P3 and P4;
-the car breaks when at least one brake pad assembly is actuated.***
+The hand brake mechanism (H) goes directly to two brake pad assemblies P3 and P4;
+the car brakes when at least one brake pad assembly is actuated.***
 
@@
  vh path/.style={thick, to path={|- (\tikztotarget)}}]
-\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-2}};
+\node at (0,0) {\includegraphics[width=\textwidth]{brakingsystem-2}};
 \begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
@@
 \end{tikzpicture}
-\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
+\caption{Prior and posterior sets of reliability functions for a simplified automotive brake system
 with layout as depicted in the lower right panel.}
-\label{fig:breakingsystem}
+\label{fig:brakesystem}
 \end{figure}

### 2016-01-21 brakingsystem.R

@@ -83,11 +83,11 @@ abdf$Part <- ordered(abdf$Part, levels=c("M", "H", "C", "P", "System"))
 ab1 <- ggplot(abdf, aes(x=Time)) + theme_bw()
 ab1 <- ab1 + scale_fill_manual(values = c("#b2df8a", "#1f78b4")) + scale_colour_manual(values = c("#b2df8a", "#1f78b4"))
 ab1 <- ab1 +  geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))
-ab1 <- ab1 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.3)
+ab1 <- ab1 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.5)
 ab1 <- ab1 + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=abdat) + xlab("Time") + ylab("Survival Probability")
 ab1 <- ab1 + bottomlegend
 
-pdf("breakingsystem-2.pdf", width=8, height=5)
+pdf("brakingsystem-2.pdf", width=8, height=5)
 ab1
 dev.off()
 #

### 2016-01-22 ijar-npb-ms.tex
some work on brake system example

@@
 
-***Another example: simplified automotive brake system, Figure~\ref{fig:brakesystem}.
-Prior sets and data exemplary only, prior bounds more smooth curves?
+As example to illustrate the potential of our model,
+we consider a simplified automotive brake system.
 The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
 which in turn actuate a braking pad assembly each (P1 -- P4).
-The hand brake mechanism (H) goes directly to two brake pad assemblies P3 and P4;
-the car brakes when at least one brake pad assembly is actuated.***
+The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
+the car brakes when at least one brake pad assembly is actuated.
+The system layout is depicted in Figure~\ref{fig:brakesystem},
+together with prior and posterior sets of reliability functions for the four component types and the complete system.
+Observed lifetimes from test data are indicated by tick marks in each of the four component type panels,
+where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
+We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
+and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
+Prior functioning probability bounds for M are based on
+a Weibull cdf with shape $2.5$ and scales $6$ and $8$ for the lower and upper bound, respectively.
+The prior bounds for P can be seen as the least committal bounds
+derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.
+
+***We see that posterior lower and upper functioning probabilities drop at those times $t$
+for which there is a failure time in the test data,
+or a drop in the prior functioning probability bounds.
+The lower bound for prior system reliability drops to zero at $t=5$
+since the prior lower bound for P drops to zero at $t=5$;
+for the system to function, at least one brake pad assembly must function.***
+
+For H, near-noninformative prior functioning probability bounds have been selected;
+with the upper bound for P being approximately one for $t \le 5$ as well,
+the prior upper system reliability bound for $t \le 5$ is close to one, too,
+since the system can function on H and one of P1 -- P4 alone.
+Note that the posterior functioning probability interval for M
+is wide not only due to the limited number of observations,
+but also because $\ntzu{\text{M}} = 8$ and the prior-data conflict reaction.
+
+Posterior functioning probability bounds for the complete system
+are much more precise than the prior system bounds,
+reflecting the information gained from component test data.
+The posterior system bounds can be also seen to reflect location and precision of the component bounds;
+for example, the system bounds drop drastically between $t=2.5$ and $t=3.5$
+mainly due to the drop of the bounds for P at that time.
 

### 2016-01-22 brakingsystem.R

@@ -55,15 +55,25 @@ abdat <- melt(abtestdata); names(abdat) <- c("x", "Part")
 abdat$Part <- ordered(abdat$Part, levels=c("M", "H", "C", "P", "System"))
 absig <- computeSystemSurvivalSignature(ab)
 abt <- seq(0, 10, length.out=301)
+#MpriorU <- 1-pexp(abt, rate=0.15)
+MpriorU <- 1-pweibull(abt, shape=2.5, scale=8)
+MpriorU[MpriorU==1] <- 1-1e-6
+#MpriorL <- 1-pexp(abt, rate=0.5)
+MpriorL <- 1-pweibull(abt, shape=2.5, scale=6)
+MpriorL[MpriorL==1] <- 1-1e-6
 # priors
 abnL <- data.frame(M=rep(1,301), H=rep(1,301), C=rep(1,301), P=rep(1,301))
 abnU <- data.frame(M=rep(8,301), H=rep(2,301), C=rep(2,301), P=rep(2,301))
-abyL <- data.frame(M=c(rep(0.8, 150), rep(0.6, 60), rep(0.2, 30), rep(0.1, 61)),
-                   H=c(rep(0.5, 150), rep(0.25, 60), rep(0.01, 91)),
+abyL <- data.frame(M=MpriorL,
+                   #M=c(rep(0.8, 150), rep(0.6, 60), rep(0.2, 30), rep(0.1, 61)),
+                   H=rep(0.0001, 301),
+                   #H=c(rep(0.5, 150), rep(0.25, 60), rep(0.01, 91)),
                    C=c(rep(c(0.75, 0.73, 0.71, 0.70, 0.60, 0.45, 0.30, 0.23, 0.21, 0.20), each=30), 0.20),
                    P=c(rep(c(0.5, 0.01), each=150), 0.01))
-abyU <- data.frame(M=c(rep(0.99, 180), rep(0.9, 60), rep(0.6, 30), rep(0.4, 31)),
-                   H=c(rep(0.99, 90), rep(0.9, 90), rep(0.7, 30), rep(0.5, 30), rep(0.3,61)),
+abyU <- data.frame(M=MpriorU,
+                   #M=c(rep(0.99, 180), rep(0.9, 60), rep(0.6, 30), rep(0.4, 31)),
+                   H=rep(0.9999, 301),
[…]

### 2016-01-22 for-franks-paper.tex
brake system example in separate file for Frank

--- 2016-01-22 ijar-npb-ms.tex
@@
 
-%\newcommand{\comments}[1]{{\small\color{gray} #1}}
-\newtoggle{td}
-\newcommand{\td}[1]{%
-  \iftoggle{td}{%
-    \todo[inline]{#1}%
-  }{}%
-}
-
-% ------------ options -------------
-
-\allowdisplaybreaks
-
-\toggletrue{td} % show todo's
-%\togglefalse{td} % hide todo's
-
-%\biboptions{longnamesfirst,angle,semicolon}
-
-\journal{IJAR}
-
 \begin{document}
-
-% ------------ frontmatter -------------
-
-\begin{frontmatter}
-\title{Bayesian Nonparametric System Reliability\\ using Sets of Priors}
-
-\author[ein]{Gero Walter\fnref{fn1}}
-\ead{g.m.walter@tue.nl}
-\author[oxf]{Louis J.M. Aslett}
-\ead{louis.aslett@stats.ox.ac.uk}
-\author[dur]{Frank P.A. Coolen}
-\ead{frank.coolen@durham.ac.uk}
-
-\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}
-\address[oxf]{Department of Statistics, University of Oxford, Oxford, UK}
-\address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}
-
-\fntext[fn1]{Gero Walter was supported by the Dinalog project
-``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).}
-
-\begin{abstract}
-Imprecise Bayesian nonparametric approach to system reliability with multiple types of components,
-sets of priors through sets of canonical parameters,
-leading to sets of system reliability functions,
-reflection of prior-data conflict
-\end{abstract}
-
-\begin{keyword}
-System reliability \sep
-Survival signature \sep
-Imprecise probability \sep
-Bayesian Nonparametrics \sep
-Prior-data conflict
-\end{keyword}
-\end{frontmatter}
-
-% ------------ manuscript -------------
-
-\section{Introduction}
-
-(some sentences may be useful for the abstract instead)
-
-System with components of $k=1,\ldots,K$ different types.
-There are $m_k$ components of type $k$ in the system.
-Components of the same type are i.i.d.\ and independent of components of other types.
-Arbitrary system layout, i.e.\ any series / parallel combination, $k$ out of $n$ etc.
-
-The survival signature allows for straightforward computation of system reliability
-for systems with complex layouts and multiple component types.
-It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
-by partitioning the event $\Tsys > t$ according to the number of components of each type functioning at time $t$.
-
-Based on expert assumptions for component failure distributions and component test data,
-we make predictive inference for a system with components that are exchangeable
-with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
-Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
-naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
-To account for uncertainty in the choice of prior
-and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
-we propose an imprecise probability approach
-based on sets of prior distributions defined through sets of canonical parameters.
-This approach also allows to adequately model weak or partial prior information.
-In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.
-
-%Our imprecise probability approach leads to sets of system reliability functions,
-%where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
-%reflects the precision of the reliability estimate:
-%a short range will indicate that we can quantify the reliability of the system quite precisely,
-%while a large range will indicate that our (probabilistic) knowledge is rather shaky --
-%remember that the reliability function is in essence a collection of probability statements.
-Our imprecise probability approach leads, for each $t$ in some grid of time points ${\cal T}$,
-to a posterior predictive probability interval for the event that the system will function at time $t$.
-The width of these intervals reflects the precision of the probability statement:
-a short range will indicate that we can quantify the system functioning probability quite precisely,
-while a large range will indicate that our (probabilistic) knowledge is indeterminate.
-
-A central advantage of our imprecise probability model is
-that it leads to more cautious probability statements
-in case of \emph{prior-data conflict} \cite[see, e.g.,][]{2006:evans}:
-From the viewpoint of the expert, the observed failure times seem very surprising,
-i.e., information from data is in conflict with prior assumptions.
-This is most relevant when there is not enough data to overrule the prior;
-as it is then unclear whether to put more trust to prior assumptions or to the observations,
-posterior inferences should clearly reflect this state of uncertainty.
-
-As we will show in Section~\ref{sec:reparam}, when taking the standard choice of a conjugate Beta prior,
-prior-data conflict is ignored, as the spread of the posterior distribution does not increase in case of such a conflict,
-ultimately conveying a false sense of certainty
-by communicating that we can quantify the reliability of the system quite precisely when in fact we cannot do so.
-In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
-This behaviour is obtained by a specific choice for the set of priors (see Section~\ref{sec:setsofbetapriors})
-which leads to larger sets of posterior distributions when prior knowledge and data are in conflict.
-
-Prior-data conflict has recently also been considered by \citet{2015:bickel},
-who, starting from a large class of reasonable models,
-identifies a subset of adequate models,
-selected according to a model adequacy measure that allows to reject a prior if it leads to prior-data conflict.
-
-Our method produces a set of discrete system reliability functions,
-or, for each time point $t$, an interval for the system survival probability,
-that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.
-
-***main contribution of the paper:
-set of priors thing,
-guidelines on how to choose the parameters;
-this is easier in terms of $(\nz, \yz)$ than in terms of $(\alpha, \beta)$***
-
-This paper implements the nonparametric approach described in Section~4 of \citet{2015:bayessurvsign}
-and extends it to sets of priors.
-
-The paper is organised as follows.
-In Section~\ref{sec:survsign}, we describe ***
-
-\section{Survival Signature}
-\label{sec:survsign}
-
-In the mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
-of its components and the structure of the system. The mathematical concept which is central to this theory is the 
-\emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
-$\underline{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
-and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\underline{x}$. 
-The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\underline{x}$, takes 
-the value 1 if the system functions and 0 if the system does not function for state vector $\underline{x}$. 
-Most practical systems are coherent, which means that $\phi(\underline{x})$ 
-is non-decreasing in any of the components of $\underline{x}$, so system functioning cannot be improved by worse performance 
-of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
-quantification for system reliability. It is further logical to assume that $\phi(\underline{0})=0$ and $\phi(\underline{1})=1$, 
-so the system fails if all its components fail and it functions if all its components function.
-
-For larger systems, working with the full structure function may be complicated, and one may particularly
-only need a summary of the structure function in case the system has exchangeable components of one or more
-types. We use the term `exchangeable components' to indicate that the failure times of the components in the system
-are exchangeable \citep{DF74}. \citet{2012:survsign} introduced such a summary,
-called the \emph{survival signature}, 
-to facilitate reliability analyses for systems with multiple types of components. In case of just a single type of components, 
-the survival signature is closely related to the system signature \citep{Sa07}, which is well-established and the topic of many
-research papers during the last decade. However, generalization of the signature to systems with
-multiple types of components is extremely complicated (as it involves ordering order statistics of different
-distributions), so much so that it cannot be applied to most practical systems. In addition to the 
-possible use for such systems, where the benefit only occurs if there are multiple components of the 
-same types, the survival signature is arguably also easier to interpret than the signature.
-
-Consider a system with $K\ge 1$ types of components, with $m_k$ components of type $k \in \{1,\ldots,K\}$ and 
-$\sum_{k=1}^K m_k = m$. Assume that the random failure times of components of the same type are exchangeable \citep{DF74}.
-Due to the arbitrary ordering of the components in the state vector, components of the same type can be grouped together, 
-leading to a state vector that can be written as 
-$\underline{x} = (\underline{x}^1,\underline{x}^2,\ldots,\underline{x}^K)$, with 
-$\underline{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.
-
-The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
-for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
-$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}.
-Essentially, this creates a $K$-dimensional partition for the event $\Tsys > t$, such that $\Rsys(t) = P(\Tsys > t)$
-can be calculated using the law of total probability:
-\begin{align}
-\label{eq:rsyswithsurvsign}
-P(\Tsys > t)
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K) \nonumber\\
- &  \hspace*{24ex}                        \times P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \nonumber\\
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \,,
-%                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
-\end{align}
-where $C^k_t \in \{0, 1, \ldots, m_k\}$ denotes
-the random number of components of type $k$ functioning at time $t$.
-
-For calculating the survival signature based on the structure function, observe that
-there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
-denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
-all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
-exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
-$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
-\begin{align}
-\label{eq:surv-sig}
-\Phi(l_1,\ldots,l_K)
- &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
-\end{align}
-%
-%Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
-%Then, for system failure time $\Tsys$,
-%\begin{align*}
-%P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
-%\end{align*}
-It should be emphasized that when using the survival signature,
-there are no restrictions on dependence of the failure times of components of different types,
-as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
-for example one can include common-cause failures quite straightforwardly into this approach \cite{CCM15}. %\citep[see][]{CCM15}.
-However, there is a substantial simplification
-if one can assume that the failure times of components of different types are independent,
-and even more so if one can assume that the failure times of components of type $k$ 
-are conditionally independent and identically distributed with CDF $F_k(t)$.
-With these assumptions, we get
-\begin{align*}
-\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
-            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
-\end{align*}
-We will employ both assumptions in this paper,
-leading to $C^k_t$ having a Beta-Binomial distribution,
-giving us a closed form expression for $P(C^k_t = l_k)$ for all $t$, $k$, and $l_k$.
-
-The main advantage of the survival signature, in line with this property of the signature for systems with a single type of 
-components \citep{Sa07}, is that the information about the system structure is fully 
-separated from the information about functioning of the components, which simplifies related statistical inference as well as
-considerations of optimal system design. In particular for study of system reliability over time, with the structure of the system, 
-and hence the survival signature, not changing, this separation also enables relatively straightforward statistical inferences.
-
-There are several relatively straightforward generalizations of the use of the survival signature.
-The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
-as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
-where lower and upper probabilities for the events $C_k = l_k$
-are inferred from test data on components of the same types as those in the system.
-This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
-Like \citet{CCMA14}, we will utilize the monotonicity of the survival signature for coherent systems
-to simplify computations.
-
-\section{Nonparametric Bayesian Approach for Component Reliability}
-\label{sec:nonparamapproach}
-
-Let us denote the random failure time of component number $i$ of type $k$ by $T^k_i$, $i = 1, \ldots, m_k$.
-The failure time distribution can be written in terms of the cdf $F^k(t) = P(T^k_i \le t)$,
-or in terms of the reliability function $R^k(t) = P(T^k_i > t) = 1 - F^k(t)$,
-also known as the survival function.
-For a nonparametric description of $R^k(t)$,
-we consider a set of time points $t$, $t \in {\cal T} = \{t_1, \ldots, \tmax\}$.
-
-At each time point $t$, the operational state of a single component of type $k$
-is Bernoulli distributed (functioning: 1, failed: 0) with parameter $\ptk$, so that
-\begin{align*}
-P\big(\indic(T^k_i > t) = 1\big) &= \ptk\,, \\
-P\big(\indic(T^k_i > t) = 0\big) &= 1 - \ptk\,,
-\end{align*}
-That is, $\indic(T^k_i > t) \sim \ber(\ptk)$, $i = 1, \ldots, m_k$, $t \in {\cal T}$.
-
-The set of probabilities $\{ \ptk, t \in {\cal T}\}$
-defines a discrete failure time distribution for components of type $k$ through
-\begin{align*}
-R^k(t_j) &= P(T^k > t_j) = p^k_{t_j},\ t_j = t_1, \ldots, \tmax\,.
-\end{align*}
-We can also express this failure time distribution through the probability mass function (pmf) and discrete hazard function,
-\begin{align*}
-f^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\big) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
-h^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\mid T^k > t_j\big) = \frac{f^k(t_j)}{R^k(t_j)}\,. % or R^k(t_{j-1}) ???
-\end{align*}
-The time grid $\cal T$ can be chosen to be appropriately dense for the application at hand,
-with the natural extension between grid points by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
-$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
-or by taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.
-
-\td{***illustrate discrete distribution with a graph of R, f, h?***}
-
-The independence assumption for components of the same type immediately implies that 
-the number of functioning components of type $k$ in the system
-is binomially distributed, $C^k_t = \sum_{i=1}^{m_k} \indic(T^k_i > t) \sim \bin(\ptk, m_k)$.
-%(maybe not relevant for this manuscript, but would it make sense to take Kaplan-Meier estimates for the $p^k_t$'s,
-%or the NPI bounds for Kaplan-Meier?)
-
-The $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
-$[0,\infty)$, for example matching a bathtub curve for the corresponding hazard rate $h^k(t_j)$.
-Naturally, $p^k_{t_j} \ge p^k_{t_{j+1}}$ should hold (assuming no repair).
-However, such direct specification is non-trivial, neglects any inherent uncertainty in the particular choice, and cannot be 
-easily combined with test data.
-To account for the uncertainty, one can express knowledge about $\ptk$ through a prior distribution.
-A convenient and natural choice is $\ptk \sim \be(\alpha^k_t, \beta^k_t)$, particularly because in a Bayesian inferential
-setting this is the conjugate prior which leads to a Beta posterior.
-
-Let the lifetime test data collected on component $k$ be $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$.
-At each fixed time $t \in {\cal T}$, this corresponds to an observation from the Binomial model described above,
-$s^k_t = \sum_{i=1}^{n_k} \indic(t^k_i > t)$.
-The posterior is then $\ptk \mid s^k_t \sim \be(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
-The combination of a Binomial observation model with a Beta prior is often called Beta-Binomial model.
-
-The posterior predictive distribution for the number of components surviving at time $t$
-in a new system, based on the lifetime data and the prior information,
-is then a so-called Beta-Binomial distribution,
-$C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
-That is, we have
-\begin{align*}
-P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \alpha^k_t + s^k_t, m_k - l_k + \beta^k_t + n_k - s^k_t)}
-                                                    {B(\alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)} \,,
-\end{align*}
-where $B(\cdot, \cdot)$ is the Beta function.
-This posterior predictive distribution is essentially a Binomial distribution
-where the functioning probability $\ptk$ takes values in $[0,1]$
-with the probability given by the posterior on $\ptk$.
-
-Consequently, in order to calculate the system reliability according to \eqref{eq:rsyswithsurvsign},
-for each component type $k$
-we need lifetime data $\vec{t}^k$,
-and have to choose $2 \times |{\cal T}|$ parameters
-to specify the prior distribution for the discrete survival function of $T^k_i$.
-In total, values for $2 \times |{\cal T}| \times K$ parameters must be chosen.
-
-\section{Reparametrisation of the Beta Distribution}
-\label{sec:reparam}
-
-The parametrisation of the Beta distribution used above is common,
-and allows $\alpha^k_t$ and $\beta^k_t$ to be interpreted as
-hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
-However, when we generalise to sets of priors in the sequel,
-it is useful to consider a different parametrisation.
-
-For clarity of presentation we will temporarily drop the super- and subscript $k$ and $t$ indices for component type and time.
-Instead of $\alpha$ and $\beta$, we consider the parameters $\nz \in [0, \infty)$ and $\yz \in [0,1]$, where
-\begin{align}
-\nz &= \alpha + \beta &
-&\text{and} &
-\yz &= \frac{\alpha}{\alpha + \beta} \,,
-\label{eq:reparam}
-\end{align}
-or equivalently, $\alpha = \nz\yz$ and $\beta = \nz(1-\yz)$.
-The upper index ${}\uz$ is used to identify these as prior parameter values,
-in contrast to their posterior values $\nn$ and $\yn$
-obtained after observing $n$ failure times (see below).
-$\nz$ and $\yz$ are sometimes called \emph{canonical} parameters,
-identified from rewriting the density in canonical form;
-see for example \cite[pp.~202 and 272f]{2000:bernardosmith}, or \cite[\S 1.2.3.1]{2013:diss-gw}.
-This canonical form gives a common structure to all conjugacy results in exponential families.
-
-From the properties of the Beta distribution,
-it follows that $\yz = \E[p]$ is the prior expectation for the functioning probability $p$,
-and that larger $\nz$ values lead to greater concentration of probability measure around $\yz$,
-since $\V(p) = \frac{\yz (1-\yz)}{\nz + 1}$.
-Consequently, $\nz$ represents the prior strength and moreover can be directly interpreted as a pseudocount, as will become clear.
-%this is clear from the interpretation of $\alpha$ and $\beta$ and \eqref{eq:reparam},
-%and will be further illustrated below through revisiting the posterior
-%%based on observed lifetimes $\vec{t} = (t_1, \ldots, t_{n})$.
-Indeed, consider the posterior given that $s$ out of $n$ components function:
-by conjugacy
-$p \mid s$ is Beta distributed with updated parameters
-\begin{align}
-\nn &= \nz + n\,, &
-\yn &= \frac{\nz}{\nz + n} \cdot \yz + \frac{n}{\nz + n} \cdot \frac{s}{n}\,.
-\label{eq:nyupdate}
-\end{align}
-Thus, after observing that $s$ out of $n$ components function (at time $t$),
-the posterior mean $\yn$ for $p$ is a weighted average of
-the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
-with weights $\nz$ and $n$, respectively.
-Therefore $\nz$ takes on the same role for the prior mean $\yz$
-as the sample size $n$ does for the observed mean $s/n$,
-leading to the notion of it being a pseudocount.
-%Indeed, the higher $\nz$, the higher the weight for $\yz$
-%in the weighted average calculation of $\yn$,
-%so $\nz$ gives the strength of the prior as compared to the sample size $n$.
-%The parameters $\nz$ and $\yz$ have a more intuitive interprtation,
-
-Reintroducing time and component type indices, the posterior predictive Beta-Binomial probability mass function (pmf) can be written in terms of the updated parameters as
-\begin{align}
-P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
-                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,,
-\label{eq:postpredCny}
-\end{align}
-with the corresponding cumulative mass function (cmf) given by
-\begin{align}
-F_{C^k_t\mid s^k_t}(l_k) &= P(C^k_t \le l_k \mid s^k_t) = \sum_{j_k=0}^{l_k} P(C^k_t = j_k \mid s^k_t)\,.
-\label{eq:postpredCnycmf}
-\end{align}
-
-The parameterisation in terms of prior mean and prior strength (or pseudocount)
-makes clear that in this conjugate setting,
-learning from data corresponds to averaging between prior and data.
-This form is attractive not only because it enhances the interpretability of the model and prior specification,
-but crucially it also makes clear what should be a serious concern in any Bayesian analysis:
-when observed data differ greatly from what is expressed in the prior,
-this conflict is simply averaged out
-and is not reflected in the posterior or posterior predictive distributions.
-
-As a simple example, imagine that we expect $\ptk$ to be about $0.75$ for a certain $k$ and $t$,
-so we choose $\yktz = 0.75$,
-and that we value this choice of mean functioning probability with $\nktz = 8$,
-i.e., equivalently to having seen $8$ observations with a mean $0.75$.
-If we observe $n_k = 16$ components of type $k$ in the test data and $s^k_t = 12$ function at time $t$,
-then $s^k_t/n_k = 0.75$ as we expect,
-so that the updated parameters are $\nktn = 24, \yktn=0.75$.
-However, in contrast, unexpectedly observing that no component functions at time $t$ instead
-leads to parameters $\nktn = 24, \yktn=0.25$.
-The prior and the posteriors based on these two scenarios
-are depicted in the left panels of Figure~\ref{fig:singleprior-pdc},
-%through their Beta densities and cdfs (left)
-%and corresponding Beta-binomial probabilities $P(C^k_t = l_k\mid s^k_t)$ and cmfs
-along with their corresponding predictive Beta-binomial pmf and cmf
-for the case $m_k = 5$ (right panels).
-
-Due to symmetry, we see that both posteriors have the same variance,
-although arising from two fundamentally different scenarios.
-Posterior 1 is based on data exactly according to prior expectations;
-the increase in confidence on $\ptk \approx 0.75$
-is reflected in a more concentrated posterior density,
-and the posterior predictive is changed only slightly.
-However, it may be cause for concern to see the same degree of confidence in Posterior 2,
-which is based on data that is in sharp conflict with prior expectations.
-Posterior 2 places most probability weight around $0.25$,
-averaging between prior expectation and data,
-with the same variance as Posterior 1.
-Accordingly, rather than conveying the conflict between observed
-and expected functioning probabilities with increased variance,
-Posterior 2 instead gives a false sense of certainty.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{singleprior-pdc2}
-\caption{Beta densities (top left) and cdfs (bottom left),
-with the corresponding Beta-binomial predictive probability mass functions (top right) and cumulative mass functions (bottom right),
-for a prior with $\nktz = 8, \yktz = 0.75$,
-and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior~1) and $s^k_t=0$ (Posterior~2), respectively.
-Data for Posterior~1 confirm prior assumptions,
-while data for Posterior~2 are in conflict with the prior.
-However, this conflict is averaged out,
-and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf/cdf and the posterior predictive pmf/cmf,
-such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}
-\label{fig:singleprior-pdc}
-\end{figure}
-
-To enable diagnosis of when this undesirable behaviour occurs,
-we propose to use an imprecise probability approach
-based on sets of Beta priors, described in the following section.
-
-\section{Sets of Beta Priors}
-\label{sec:setsofbetapriors}
-
-As was shown by \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
-we can have both tractability and meaningful reaction to prior-data conflict
-by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$
-(a detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
-In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
-corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
-The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
-This element-by-element updating can be rigorously justified
-as ensuring coherence \citep[\S 2.5]{1991:walley}, and was termed ``Generalized Bayes' Rule'' by \citet[\S 6.4]{1991:walley}.
-Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$,
-obtained by updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
-leading to the set of updated parameters
-\begin{align}
-\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
-\label{eq:paramsets}
-\end{align}
-
-Examples for parameter sets $\PktZ$ and $\PktN$ as in \eqref{eq:paramsets} are depicted in Figure~\ref{fig:paramsets}.
-Such rectangular prior parameter sets $\PktZ$ have been shown
-to balance desirable model properties and ease of elicitation 
-(see \citet[pp.~123f]{2013:diss-gw} or \citet{Troffaes2013a-short}).
-%
-For each component type $k$ and time point $t$,
-one need only specify the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
-(so in total $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions
-on the survival function of each component).
-%notwithstanding this, the model has favourable inference properties.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{paramsets}
-\caption{Prior parameter set $\PktZ = [1,8] \times [0.7,0.8]$ and posterior parameter set $\PktN$
-for data $s^k_t/n_k = 12/16$ (Posterior 1, left) and $s^k_t/n_k = 0/16$ (Posterior 2, right).
-For no-conflict data ($s^k_t/n_k \in [\yktzl,\yktzu]$), $\PktN$ has the `spotlight' shape (left);
-in case of prior-data conflict ($s^k_t/n_k \not\in [\yktzl,\yktzu]$), $\PktN$ has the `banana' shape (right),
-leading to a large degree of imprecision in the $\yktn$ dimension of $\PktN$,
-thus reflecting increased uncertainty about the functioning probability $p^k_t$
-due to the conflict between prior assumptions and observed data.}
-\label{fig:paramsets}
-\end{figure}
-
-A desirable inference property arising from this setup is that
-the posterior parameter set $\PktN$ is not rectangular in the way that the prior parameter set is.
-Indeed, the shape of $\PktN$ depends on the presence or absence of prior-data conflict,
-which is naturally operationalised as $s^k_t/n_k \not\in [\yktzl, \yktzu]$:
-that is, prior-data conflict is defined to occur when, at time $t$, the observed fraction of functioning components
-is outside its \emph{a priori} expected range.
-
-First, in the absence of prior-data conflict, 
-$\PktN$ shrinks in the $\ykt$ dimension;
-how much it shrinks depending on $\nktz \in [\nktzl, \nktzu]$,
-leading to the so-called spotlight shape depicted in Figure~\ref{fig:paramsets} (left).
-Since $\yktn$ gives the posterior expectation for the functioning probability $p_t^k$,
-shorter $\yktn$ intervals mean more precise knowledge about $p_t^k$.
-Also, the variance interval for $p_t^k$ (not shown) will shorten and shift towards zero,
-as the Beta distributions in $\MktN$ will be more concentrated
-due to the increase of $\nktz$ to $\nktn$.
-
-Alternatively, when there is conflict between prior and observed data (i.e.\ $s^k_t/n_k \not\in [\yktzl, \yktzu]$),
-$\PktN$ instead adopts the so-called `banana shape',
-arising from the intervals for $\yktn$  being shifted closer to $s^k_t/n_k$
-for lower $\nktn$ values than for higher $\nktn$ values, see Figure~\ref{fig:paramsets} (right).
-Overall, this results in a wider $\yktn$ interval compared to the no conflict case, 
-reflecting the extra uncertainty due to prior-data conflict.  
-In other words, the posterior sets make more cautious probability statements about $p_t^k$, as desired in this scenario.
-
-Based on these shapes and \eqref{eq:nyupdate}, it is possible to deduce the following expressions
-for the lower and upper bounds of $\yktn$:
-\begin{align}
-\begin{aligned}
-\min_{\PktN} \yktn &=
- \begin{cases}
- %\dfrac{\nktzu \yktzl + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \ge \yktzl \\
- \big(\nktzu \yktzl + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \ge \yktzl \\
- %\dfrac{\nktzl \yktzl + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k <   \yktzl
- \big(\nktzl \yktzl + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k <   \yktzl
- \end{cases}\,,\\
-\max_{\PktN} \yktn &=
- \begin{cases}
- %\dfrac{\nktzu \yktzu + s^k_t}{\nktzu + n_k} & \text{if } s^k_t/n_k \le \yktzu \\
- \big(\nktzu \yktzu + s^k_t\big) / \big(\nktzu + n_k\big) & \text{if } s^k_t/n_k \le \yktzu \\
- %\dfrac{\nktzl \yktzu + s^k_t}{\nktzl + n_k} & \text{if } s^k_t/n_k >   \yktzu
- \big(\nktzl \yktzu + s^k_t\big) / \big(\nktzl + n_k\big) & \text{if } s^k_t/n_k >   \yktzu
- \end{cases}\,.
-\end{aligned}
-\label{eq:ysetupdate}
-\end{align}
-Note that the lower bound for $\yktn$ is always attained at $\yktzl$, the upper bound at $\yktzu$.
-Also note that when $s^k_t/n_k \in [\yktzl, \yktzu]$,
-both the lower and the upper bounds for $\yktn$ are attained at $\nktzu$,
-corresponding to the spotlight shape.
-However, when $s^k_t/n_k \not\in [\yktzl, \yktzu]$,
-the banana shape indicates that
-one of the bounds for $\yktn$ is attained at $\nktzl$.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{betaset-binomset1}
-\caption{Sets of Beta pdfs (left) and Beta-Binomial cmfs (right, for $m_k=5$)
-corresponding to the prior and posterior parameter sets in Figure~\ref{fig:paramsets}.
-The sets are depicted as shaded areas,
-with the distributions corresponding to the four corners
-of the prior parameter set $\PktZ$ (or their posterior counterparts) as solid lines.
-The top row depicts the set of prior cdfs/cmfs and the set of posterior cdfs/cmfs for the case where data confirm prior assumptions
-(see left panel of Figure~\ref{fig:paramsets});
-the bottom row depicts the (identical) set of prior cdfs/cmfs and the set of posterior cdfs/cmfs in case of prior-data conflict
-(see right panel of Figure~\ref{fig:paramsets}).
-%The set of posteriors and the set of posterior predictive distributions
-The set of posterior cdfs and cmfs
-is much larger in case of prior-data conflict:
-uncertainty due to this conflict is reflected through increased imprecision.}
-\label{fig:betaset-binomset}
-\end{figure}
-
-The different locations and sizes of $\PktN$ in the conflict versus no conflict case are then, in turn,
-also reflected in the corresponding sets of Beta cdfs and Beta-Binomial cmfs.
-As an example, those corresponding to the parameter sets in Figure~\ref{fig:paramsets}
-are depicted in Figure~\ref{fig:betaset-binomset}.
-
-In the no conflict case (Posterior 1, top row),
-the reduction of the $\yktn$ range in $\PktN$ leads to a much smaller set
-of Beta and Beta-Binomial distributions.
-For example, the range of predictive probabilities
-that two out of a set of five components of type $k$ function at time $t$ 
-has changed from $[0.10, 0.28]$ \emph{a priori} to $[0.11,0.14]$ \emph{a posteriori}.
-This reflects the gain in precision due to test data in accordance with prior assumptions.
-
-In contrast, for the prior-data conflict case (Posterior 2, bottom row),
-the wide $\yktn$ range in $\PktN$ leads to a set of Beta and Beta-Binomial distributions
-that is much larger than in the no conflict case.
-Here, the range of posterior predictive probabilities
-that two out of a set of five components of type $k$ function at time $t$
-is now $[0.86, 1.00]$ \emph{a posteriori}, i.e., less precise than in the no conflict case.
-Using sets of Beta priors, the resulting set of posterior predictive Beta-Binomial distributions
-reflects the precision of prior information,
-the amount of data, and prior-data conflict.
-
-Furthermore, with sets of Beta priors it is also possible
-to express prior ignorance
-by letting $\yktzl \to 0$ and $\yktzu \to 1$
-for some or all $t \in {\cal T}$.
-(Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
-as this can lead to improper posterior predictive distributions.
-For example, at any $t < \min(\vec{t}^k)$,
-we would have $\yktnu = 1$, leading to one argument of the Beta function
-in the denominator of \eqref{eq:postpredCny} being zero.)
-These limits for $\yktz$ imply we are only prepared to give trivial bounds for the functioning probability
-and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
-This provides a more natural choice of `noninformative' prior over $[0,1]$ than the usual choice of
-a Beta prior with $\alpha^k_t = \beta^k_t = 1$ (or $\nktz = 2$, $\yktz = 0.5$).
-Such a prior for all $t \in {\cal T}$ actually reflects a belief that the component reliability function
-is on average 1/2 for all $t$, which is not an expression of ignorance, but rather a very specific (and arguably peculiar) prior belief.
-
-%With the bounded domain for $\yktz$ 
-%\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
-%benavoli zaffalon papers***}
-%
-%As a note regarding the bounds for $\nktz$,
-%for an informative prior the choice of $\nktzl$ is relevant for posterior inferences in case of prior-data conflict,
-%as then one of the bounds for $\ykt$ is attained for $\nktzl$.
-%In a near-noninformative setting, the choice of $\nktzl$ is instead not relevant,
-In a near-noninformative setting, the choice of $\nktzl$ is not relevant,
-because \eqref{eq:ysetupdate} implies both lower and upper bound for $\yktn$ are obtained with $\nktzu$.
-In particular, $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
-$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
-Naturally, one cannot have prior-data conflict in cases of near prior ignorance.
-
-\section{Sets of System Reliability Functions}
-\label{sec:setsofrel}
-
-The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
-providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
-is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
-enabling diagnoses of prior-data conflict which is consequential at the system
-level, via sets of system reliability functions.
-
-To obtain the lower and upper bound for the system reliability function $\Rsys(t)$,
-we now need to minimise and maximise Equation~\eqref{eq:rsyswithsurvsign} over $\PtZi{1}, \ldots, \PtZi{K}$ for each $t$,
-where the posterior predictive probabilities for $C^k_t$ are given by the Beta-Binomial pmf \eqref{eq:postpredCny}.
-%It turns out that we need to optimise over $\ntz{1}, \ldots, \ntz{K}$ only, %$\nktz$ ($k=1,\ldots,K$) only,
-%as lower and upper bounds for $\Rsys(t)$ are obtained for $\yktzl$ and $\yktzu$, respectively.
-%
-%To see this,
-%remember that $\yktz$ gives the prior expected functioning probability for a component of type $k$ at time $t$.
-%From Equation~\eqref{eq:nyupdate} (right) we see that $\yktn$ is increasing in $\yktz$,
-%%the posterior parameter set bounds are the transformed prior parameter set bounds,
-%%i.e., $\yktzu$ corresponds to the upper bound of $\PktN$, for all $\nktz \in \PktZ$,
-%such that for each fixed $\nktz$, $\yktzu$ will maximise the posterior expected functioning probability $\yktn$.
-%%
-%Now, a higher posterior expected functioning probability means
-%higher probability for many components out of $m_k$ surviving,
-%i.e., probabilities for the larger $l_k$'s are higher, and in turn for the lower $l_k$'s are lower.
-%Indeed, the Beta-Binomial distribution is stochastically ordered for varying $\yktn$, i.e.,
-%its cmf \eqref{eq:postpredCnycmf} is decreasing in $\yktn$ for all $l_k$,
-%such that the cmfs for different values of $\yktn$ do not cross each other.
-%This means that for each fixed $\nktz$, the Beta-Binomial cmf \eqref{eq:postpredCnycmf} is minimized for $\yktzu$ in all $l_k$,
-%such that the probability weights given to high values of $l_k$ are maximised. %for $\yktzu$.
-%For coherent systems, $\Phi$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-%thus $\Rsys(t)$ is maximised by putting most probability weight on the highest $l_k$ values for each $k$,
-%which is in turn obtained for $\yktzu$, $k=1,\ldots,K$.
-We therefore have
-%
-%for a certain $k$, a high probability on high $l_k$'s is never worse than a high probability on lower $l_k$'s,
-%keeping all other component type expressions fixed.
-%***Monotonicity in $\yz_{k,t}$, so we get, for each $t \in {\cal T}$,
-\begin{align}
-\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} \Rsys(t \mid \PtZi{1}, \ldots, \PtZi{K}, \vec{t}^1, \ldots, \vec{t}^K) \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
-                                                 \prod_{k=1}^K P(C^k_t = l_k \mid \yktz, \nktz, s^k_t) \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{12ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
-                                         {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
-    \,, \label{eq:LwrSysPostA}
-\end{align}
-and similarly maximising for $\uRsys(\cdot)$.
-
-Note that $\Phi(\cdot)$ is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
-thus if there is first-order stochastic ordering on $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$
-for each $k$, then this ordering can be used to determine the elements of $\PtZi{k}$
-which minimise and maximise the overall system reliability function without
-resorting to computationally expensive exhaustive searches or numerical optimisation.
-
-We therefore start by proving the following result, where indices are suppressed for readability.
-We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.
-
-\begin{theorem}
-  \label{thm:y}
-  Let $\beta_y$ denote the Beta-Binomial distribution with probability mass function parameterised as:
-  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
-  with $n, m, s,$ and $N$ fixed and unknown.
-
-  Then $\beta_{\yu} \ge_{\mathrm{st}} \beta_{\yl} \ \forall \ \yu > \yl$ with $\yu, \yl \in (0,1)$.
-\end{theorem}
-The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:y}.
-
-Consequently, for each component, the posterior predictive Beta Binomial distributions 
-with larger prior functioning probability stochastically dominate those
-with smaller prior functioning probability, providing rigorous proof 
-which accords with intuition. Applying this result to the sets of system reliability 
-functions, together with the monotonicity in the survival signature, means that
-$\lRsys(\cdot)$ is attained when $\yktz = \yktzl$ and $\uRsys(\cdot)$
-is attained when $\yktz = \yktzu$ for all possible $\nktz$ values.
-
-The analogous result for $\nktz$ is more subtle, because stochastic 
-dominance is not guaranteed at a single value.  The following Theorem 
-provides the conditions under which an upper or lower limit has first-order stochastic dominance.
-
-\begin{theorem}
-  \label{thm:n}
-  Let $\beta_n$ denote the Beta-Binomial distribution with probability mass function parameterised as:
-  \[ p(l \mid y, n, m, s, N) \propto \frac{B(l + ny + s, m - l + n(1-y) + N - s)}{B(ny + s, n(1-y) + N - s)}, \]
-  with $y, m, s,$ and $N$ fixed and unknown.  
-  Then,
-  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
-  and 
-  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-  If $\frac{s}{N + m - 1} < y < \frac{s + m}{N + m - 1}$ then first-order stochastic dominance is not guaranteed.
-\end{theorem}
-The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n}.
-
-These first-order stochastic domination results now gives the exact 
-solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
-%For $\lRsys(\cdot)$, the minimum is achieved at
-%$\nktzu$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k < 0$ and is achieved at 
-%$\nktzl$ if $\yktzl(n_k+m_k-1)-s^k_t-m_k > 0$.
-%Conversely, for $\uRsys(\cdot)$, the maximum is achieved at 
-%$\nktzu$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k > 0$ and is achieved at 
-%$\nktzl$ if $\yktzu(n_k+m_k-1)-s^k_t-m_k < 0$.
-\begin{align}
-\lefteqn{\lRsys(t \mid \vec{t}^1, \ldots, \vec{t}^K)} \nonumber \\
- &= \min_{\PtZi{1}, \ldots, \PtZi{K}} 
-    \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktz\yktz + s^k_t, m_k - l_k + \nktz(1-\yktz) + n_k - s^k_t)}{B(\nktz\yktz + s^k_t, \nktz(1-\yktz) + n_k - s^k_t)}
-    \nonumber\\
- &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K) \times \nonumber \\ & \hspace*{8ex}
-    \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
- &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
-   \nktzu & \quad\mbox{if}\quad \yktzl < \frac{s}{N + m - 1} \\
-   \nktzl & \quad\mbox{if}\quad \yktzl > \frac{s + m}{N + m - 1} \\
-   \mathrm{optimised} & \quad\mbox{if}\quad \frac{s}{N + m - 1} < \yktzl < \frac{s + m}{N + m - 1}
- \end{aligned} \right. \nonumber
-\end{align}
-
-\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}
-
-In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
-which define the set of prior discrete reliability functions for components of type $k$.
-We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
-%***How to choose the sets of priors for the survival function of type $k$ components,
-%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***
-
-As mentioned in Section~\ref{sec:nonparamapproach}, for the actual functioning probabilities $\ptk$
-it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
-%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
-%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
-%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
-%but does this need to hold for the prior guess range bound $\yktzu$?)***
-This naturally translates to conditions on the prior guess for $\ptk$,
-such that we propose that 
-$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
-Due to $s^k_t/n_k$ decrasing in $t$ and the weighted average property of the update step for $\ykt$,
-this ensures that 
-$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
-In a situation where we are quite sure about the functioning probability for low $t$,
-but are unsure about what happens for larger $t$ and so want to be maximally cautious for those $t$,
-then we can let $\yktzl$ drop to (almost) 0, but $\yktzu$ should not increase.
-%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
-%If we know, e.g., pretty much what's going on for low $t$
-%but want to be much more cautious for high $t$,
-%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
-
-We think it is not advisable to express certainty about expected functioning probabilities
-with $\nktz$ bounds that vary strongly over $t$.
-%***Better to express certainty of prior guess via $\nktz$ bounds?\\
-With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
-%it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
-E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
-and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
-and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
-\begin{itemize}
-\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
-\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
-\end{itemize}
-Again, this follows from the weighted average property of $\yktn$;
-for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
-% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
-It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
-Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to let them change with $t$ gradually only.
-
-Generally, the interpretation as pseudocount or prior strength should guide the choice of bounds for $\nktz$; 
-low values for $\nktz$ as compared to the test sample size $n_k$
-give low weight to the prior expected functioning probability intervals $[\yktzl, \yktzu]$,
-and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
-Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
-in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
-In contrast, high values for $\nktz$ will lead to slower learning and wider $\yktn$ intervals,
-which means more cautious posterior inferences.
-The difference betweeen $\nktzu$ and $\nktzl$ determines the strength of the prior-data conflict sensitivity;
-as is clear from Figure~\ref{fig:paramsets} and \eqref{eq:ysetupdate}, the wider the $\nktz$ interval,
-the wider $[\yktnl, \yktnu]$ in case of conflict.
-So it seems useful to choose $\nktzl = 1$ or $\nktzl = 2$,
-while choosing $\nktzu$ with help of the half-width rule as described above.
-
-%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
-%to get proper posteriors***
-As mentioned in Section~\ref{sec:setsofbetapriors},
-it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
-For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
-this can lead to improper posterior predictive distributions
-due to zero arguments for the Beta functions in the denominator of \eqref{eq:LwrSysPost}.
-%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
-But it is possible to choose values close to $0$ and $1$, respectively,
-and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
-posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
-%***what to do in extreme tail of component distributions?
-%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
-Likewise, our nonparametric method does not bring unintuitive tail behaviour
-as some parametric methods do;
-there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.
-
-%***elicitation: we should also consider the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
-%as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
-While it is possible to set the bounds $\yktzl$ and $\yktzu$ for each $t \in {\cal T}$ individually,
-in practice this will be often too time-consuming when ${\cal T}$ forms a dense grid.
-%(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
-Switching to a coarser time grid will waste information from data,
-as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
-We rather propose to elicit bounds for a subset of ${\cal T}$ only,
-and to fill up the time grid with the least committal bounds, i.e.,
-taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
-and likewise $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.
-A possible elicitation procedure in this vein could be
-to start with eliciting $\yktz$ bounds for a few `central' time points $t$,
-filling up the grid as described above accordingly,
-and then to further refine the obtained bounds as deemed necessary by the expert.
-%`middle' or `typical' $t$,
-%then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
-
-\section{Computations \& Examples}
-
-%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
-
-\subsection{Software}
-
-The methods of this paper have been implemented in the \textbf{R}
-\citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
-providing an easy to use interface for reliability practitioners.  The
-primary function, which computes the upper and lower posterior
-predictive system survival probabilities as in \eqref{eq:LwrSysPost}, is
-named \texttt{nonParBayesSystemInferencePriorSets()}.  The user
-specifies the times at which to evaluate the bounds, the survival
-signature ($\Phi(\cdot)$), the component test data ($\vec{t}^1, \ldots,
-\vec{t}^K$), and the prior parameter set for each component type and
-time ($\PtZi{k}$, via $\nzu_{k,t}, \nzl_{k,t}, \yzu_{k,t}$, and
-$\yzl_{k,t}$).  All computations of $\lRsys$
-and $\uRsys$ at different time points are performed in parallel
-automatically where the CPU has multiple cores.
-
-Note that computation of the system signature itself can be simplified by
-expressing the structure of the system as an undirected graph using the
-\texttt{computeSystemSurvivalSignature()} function in the same package,
-leaving only data and prior to be handled.  These publicly available
-functions have been used in computing all the following examples for
-reproducibility.  \ref{ap:software} details how to use this software.
-
-\subsection{Examples}
-
-\begin{figure}
-\centering
-\begin{tikzpicture}
-[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
- cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
- hv path/.style={thick, to path={-| (\tikztotarget)}},
- vh path/.style={thick, to path={|- (\tikztotarget)}}]
-%\begin{scope}[scale=0.75]
-\node[type1] (T3)   at ( 5.6, 0) {T3};
-\node[type2] (T2)   at ( 2.8, 0) {T2};
-\node[type3] (T1-2) at ( 1.4, 1) {T1};
-\node[type3] (T1-3) at ( 1.4,-1) {T1};
-\node[type3] (T1-5) at ( 4.2, 1) {T1};
-\node[type3] (T1-6) at ( 4.2,-1) {T1};
-\coordinate (start) at (0  ,0);
-\coordinate (end)   at (6.3,0);
-\coordinate (bista) at (0.7,0);
-\coordinate (biend) at (4.9,0);
-\path (bista)     edge[hv path] (start)
-                  edge[vh path] (T1-2.west)
-                  edge[vh path] (T1-3.west)
-      (T1-2.east) edge[hv path] (T2.north)
-      (T1-3.east) edge[hv path] (T2.south)
-      (T2.north)  edge[vh path] (T1-5.west)
-      (T2.south)  edge[vh path] (T1-6.west)
-      (biend)     edge[vh path] (T1-5.east)
-                  edge[vh path] (T1-6.east)
-                  edge[hv path] (T3.west)
-      (T3.east)   edge[hv path] (end);
-%\end{scope}
-\end{tikzpicture}
-\caption{Reliability block diagram for a `bridge' system with three component types.}
-\label{fig:bridge-layout}
-\end{figure}
-
-As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
-as depicted in Figure~\ref{fig:bridge-layout}.
-For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
-For components of type T3, we consider an informative set of prior reliability functions
-as given in Table~\ref{tab:bridge-T3prior}.
-This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
-and filling up the rest.
-These prior assumptions, together with sets of posterior reliability functions
-resulting from three different scenarios for test data for component type T3,
-are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
-test data for components of type T1 and T2 are invariably taken as
-$\vec{t}^1 = (2.2, 2.4, 2.6, 2.8)$ and $\vec{t}^2 = (3.2, 3.4, 3.6, 3.8)$, respectively.
-
-\begin{table}
-\centering
-\begin{tabular}{crrrrr}
-\toprule
-$t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
-\midrule
-$\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
-$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250 \\
-\bottomrule
-\end{tabular}
-\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system.}
-\label{tab:bridge-T3prior}
-\end{table}
-
-In Figure~\ref{fig:bridge-fitting}, 
-test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
-and so in line with expectations.
-The posterior set of reliability functions for each component type and the whole system
-is considerably smaller as compared to the prior set
-(due to the low prior strength intervals
-$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
-and so giving more precise reliability statements.
-We see that posterior lower and upper functioning probabilities drop at those times $t$
-when there is a failure time in the test data,
-or a drop in the prior functioning probability bounds.
-Note that the lower bound for prior system reliability function is zero
-due to the prior lower bound of zero for T1;
-for the system to function, at least two components of type T1 must function.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{bridge-fittingfailures}
-\caption{Prior and posterior sets of reliability functions for the `bridge' system and its three component types,
-with failure times as expected for component type T3.
-Test data failure times are denoted with tick marks near the time axis.}
-\label{fig:bridge-fitting}
-\end{figure}
-
-In Figure~\ref{fig:bridge-early},
-test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
-and so earlier than expected.
-Compared to Figure~\ref{fig:bridge-fitting},
-posterior functioning intervals for T3 are wider between $t=1$ and $t=3.5$,
-reflecting additional imprecision due to prior-data conflict.
-For $t > 1$, it is clearly visible how $\ytnu{3}$ is halfway between $\ytzu{3}$ and $s_t^3/n_3 = 0$
-(weights $\ntzu{3} = 4$ and $n_3 = 4$),
-while $\ytnl{3}$ is one-fifth of $\ytzl{3}$
-(weights $\ntzl{3} = 1$ and $n_3 = 4$).
-Note that the posterior system functioning probability is constant for $t \in [1,2]$
-because the prior functioning probability is constant for $t \in [1,2]$
-and there are no failure times $\in [1,2]$ in the test data.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{bridge-earlyfailures}
-\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
-with failure times earlier as expected for component type T3.}
-\label{fig:bridge-early}
-\end{figure}
-
-In Figure~\ref{fig:bridge-late}, 
-test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
-and so observed failures are later than expected.
-Here we see that for $t \in [2,4]$,
-posterior functioning bounds for T3 are even wider than prior functioning bounds.
-The width turns back to being half the prior width
-only after the four failures.
-The imprecision carries over to the system bounds,
-where we see wider bounds as compared to the other two scenarios
-especially between $t=2$ and $t=4$.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{bridge-latefailures}
-\caption{Prior and posterior sets of reliability functions for the `bridge' type system and its three component types,
-with failure times later as expected for component type T3.}
-\label{fig:bridge-late}
-\end{figure}
 
@@
 
-%***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
-%informative prior set for some component types, different degree of imprecision,
-%noninformative prior set for other components (make clear that precise `noninformative' prior actually contains info), 
-%combine with prior-data conflict and non-conflict test data,
-%to show effect of precision of prior knowledge / amount of data / (degree of) prior-data conflict on $\Rsys(t)$.***
-
-%***Vacuous prior sets $[\yktzl, \yktzu] = (0,1)$ for some component types,
-%informative prior sets for others. $[\nktzl, \nktzu]$ interval for all component types.***
-
-***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
-(could nicely illustrate challenges in decision making with intervals:
-do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
-or do I rather add redundancy such that effect is smaller but more certain?***
-
-***Other interesting extra illustration:
-show effect of replacement of components in system at certain time points
-(could be corrective (component failed) or preventive replacement),
-replaced components constitute a new type with shifted component reliability function***
-
-\section{Conclusions and Outlook}
-
-Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
-However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
-and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.
-
-The survival signature and its use for uncertainty quantification for system
-reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
-For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
-to reflect uncertainty about system functioning for known states of its components, with a further
-generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
-survival signature to multi-state systems such that it again summarizes the structure function
-in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
-
-***Extend the model to deal with right-censored observations which are common in the reliability setting.
-The minimal assumption that a component can either fail immediately after censoring or live forever
-will be simple to implement but will lead to high imprecision,
-whereas assuming exchangeability with other surviving components at moment of censoring
-will be more complex to accomodate but will lead to less imprecision.
-This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
-and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
-
-***right-censoring will also allow to use data from running system,
-to calculate its remaining useful life (RUL).
-
-% ------------ bibliography -------------
-
-\section*{References}
-
-\bibliographystyle{elsarticle-harv}
-\bibliography{ijar-npb-refs}
-
-\section*{Appendix}
-\appendix
-\renewcommand*{\thesection}{\Alph{section}}
-
-\section{Proofs}
-\label{ap:proofs}
-
-\begin{proof}[\textbf{Proof of Theorem \ref{thm:y}, p\pageref{thm:y}}]
-  \label{prf:y}
-  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\yu}$ and $\beta_{\yl}$,
-  \begin{align*}
-    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid \yu, n, m, s, N)}{p(l \mid \yl, n, m, s, N)}} \\
-    &= \frac{B(l + n \yu + s, m - l + n (1 - \yu) + N - s) B(n \yl + s, n (1 - \yl) + N - s)}
-            {B(n \yu + s, n (1 - \yu) + N - s) B(l + n \yl + s, m - l + n (1 - \yl) + N - s)} \\
-    &= \frac{\Gamma(l + n \yu + s) \Gamma(m - l + n (1 - \yu) + N - s) \Gamma(n \yl + s) \Gamma(n (1 - \yl) + N - s)}
-            {\Gamma(l + n \yl + s) \Gamma(m - l + n (1 - \yl) + N - s) \Gamma(n \yu + s) \Gamma(n (1 - \yu) + N - s)} \\
-    &= \left\{ \begin{aligned}
-         \frac{\prod_{x=0}^{m-1} (x + n (1 - \yu) + N - s)}
-              {\prod_{x=0}^{m-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } l=0 \\
-         \frac{\prod_{x=0}^{l-1} (x + n \yu + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yu) + N - s)}
-              {\prod_{x=0}^{l-1} (x + n \yl + s) \prod_{x=0}^{m-l-1} (x + n (1 - \yl) + N - s)} &\quad\mbox{ for } 0<l<m \\
-         \frac{\prod_{x=0}^{m-1} (x + n \yu + s)}
-              {\prod_{x=0}^{m-1} (x + n \yl + s)} &\quad\mbox{ for } l=m
-       \end{aligned} \right.
-  \end{align*}
-  since $\Gamma(x+1)=x \Gamma(x)$.
-
-  Thus,
-  \begin{align*}
-    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} &=
-      \frac{(l + n \yu + s) (m - l - 1 + n (1 - \yl) + N - s)}
-           {(l + n \yl + s) (m - l - 1 + n (1 - \yu) + N - s)} \\
-    &> 1 \quad\mbox{when}\quad 0 \le \yl < \yu \le 1
-  \end{align*}
-
-  Hence, $\mathcal{L}(\cdot)$ is monotone increasing for $0 < \yl < \yu < 1$, so that $\beta_{\yu}$ is larger than or equal to $\beta_{\yl}$ in monotone likelihood ratio order ($\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl}$).
-But, $\beta_{\yu} \ge_\mathrm{lr} \beta_{\yl} \implies \beta_{\yu} \ge_\mathrm{st} \beta_{\yl}$ (\cite[Theorem 1.C.1, p.43]{shaked2007}) giving the required result.
-\end{proof}
-
-\begin{proof}[\textbf{Proof of Theorem \ref{thm:n}, p\pageref{thm:n}}]
-  \label{prf:n}
-  Consider the likelihood ratio for the two Beta Binomial distributions $\beta_{\nu}$ and $\beta_{\nl}$,
-  \begin{align*}
-    \lefteqn{\mathcal{L}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)}} \\
-    &= \frac{B(l + \nu y + s, m - l + \nu (1 - y) + N - s) B(\nl y + s, \nl (1 - y) + N - s)}
-            {B(\nu y + s, \nu (1 - y) + N - s) B(l + \nl y + s, m - l + \nl (1 - y) + N - s)} \\
-    &= \frac{\Gamma(l + \nu y + s) \Gamma(m - l + \nu (1 - y) + N - s)}
-            {\Gamma(l + \nl y + s) \Gamma(m - l + \nl (1 - y) + N - s)} \\
-    &\quad \times \frac{\Gamma(\nl y + s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu+N) \Gamma(m+\nl+N)}
-                       {\Gamma(\nu y + s) \Gamma(\nu (1 - y) + N - s)\Gamma(\nl+N) \Gamma(m+\nu+N)} \\
-    &= \left\{ \begin{aligned}
-         \frac{\prod_{x=0}^{m-1} (x + \nu (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nl + N)}
-              {\prod_{x=0}^{m-1} (x + \nl (1 - y) + N - s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=0 \\
-         \frac{\prod_{x=0}^{l-1} (x + \nu y + s) \prod_{x=0}^{m-l-1} (x + \nu (1 - y) + N - s)}
-              {\prod_{x=0}^{l-1} (x + \nl y + s) \prod_{x=0}^{m-l-1} (x + \nl (1 - y) + N - s)} \\
-         \quad \times \frac{\prod_{x=0}^{m-1} (x + \nl + N)}{\prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } 0<l<m \\
-         \frac{\prod_{x=0}^{m-1} (x + \nu y + s) \prod_{x=0}^{m-1} (x + \nl + N)}
-              {\prod_{x=0}^{m-1} (x + \nl y + s) \prod_{x=0}^{m-1} (x + \nu + N)} &\quad\mbox{ for } l=m
-       \end{aligned} \right.
-  \end{align*}
-  since $\Gamma(x+1)=x \Gamma(x)$.
-
-  Thus,
-  \[ \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} =
-      \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
-           {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
-  \]
-
-  However, unlike the case for the $y$ parameter in Theorem \ref{thm:y}, neither $\beta_{\nl}$ 
-  nor $\beta_{\nu}$ can be guaranteed to dominate for all possible values 
-  for the other parameters, so that necessary conditions for
-  monotonicity (either increasing or decreasing) must be established.
-  We require,
-  \[ \frac{(l + \nu y + s) (m - l - 1 + \nl (1 - y) + N - s)}
-          {(l + \nl y + s) (m - l - 1 + \nu (1 - y) + N - s)}
-     >1
-  \]
-  After extensive routine algebra, this can be conveniently expressed as
-  \begin{align*}
-    (\nu - \nl)[y (N + m - 1) - s] - l (\nu - \nl)>0.
-  \end{align*}
-  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
-  Thus, for monotonicity to hold for all $l$, we require
-  \begin{align*}
-    (\nu - \nl)[y (N + m - 1) - s] - m (\nu - \nl) &>0 \\
-    \implies (\nu - \nl)[y (N + m - 1) - s - m] &>0
-  \end{align*}
-  Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
-  likelihood ratio only when \[ y (N + m - 1) - s - m > 0. \]
-  By a similar argument, the likelihood ratio is only monotonically decreasing when
-  \[ y (N + m - 1) - s < 0. \]
-  Thus,
-  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
-  and 
-  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-  by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
-  \[ \frac{s}{N+m-1} < y < \frac{s+m}{N+m-1} \]
-  we cannot definitively state the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
-\end{proof}
-
-\section{Software details}
-\label{ap:software}
-
-Functions which make it easy to use the methods of this paper have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
-There are two functions of particular note: \texttt{computeSystemSurvivalSignature} and \texttt{nonParBayesSystemInferencePriorSets}
-
-\subsection{Computing the survival signature}
-
-The function \texttt{computeSystemSurvivalSignature} allows easy 
-computation of the survival signature if the system is expressed as an
-undirected graph with `start' and `terminal' nodes (which are not
-considered components for survival signature computation).  The system
-is considered to work if there is a path from the start to the terminal
-node passing only through functioning components.
-
-Graph representations of systems are most simply defined by using the 
-\texttt{graph.formula} function.  The `start' node should be denoted
-\texttt{s} and the `terminal' node should be denoted \texttt{t} and
-intermediate nodes (representing actual components) should be numbered and
-connected by edges denoted by \texttt{-}, where the numbering denotes physically
-distinct components.  Component numbers can be repeated to include
-multiple links.  For example, to build a simple three component series
-system:
-
-\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t)}
-
-and to build a three component parallel system:
-
-\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,t, s\,-\,2\,-\,t, s\,-\,3\,-\,t)}
-
-There is an additional shorthand which indicates a link exists to a list of multiple components separated by the \texttt{:} operator, so that the parallel system can be also be expressed more compactly by:
-
-\noindent\texttt{sys <- graph.formula(s\,-\,1:2:3\,-\,t)}
-
-Therefore, the simple bridge system of Figure \ref{fig:bridge-layout} can be constructed with:
-
-\noindent\texttt{sys <- graph.formula(s\,-\,1\,-\,2\,-\,3\,-\,t, s\,-\,4\,-\,5\,-\,3\,-\,t, 1:4\,-\,6\,-\,2:5)}
-\begin{itemize}
-  \item \texttt{s\,-\,1\,-\,2\,-\,3\,-\,t} signifies the route from left to right entering the first component going across the top of the system block diagram in Figure \ref{fig:bridge-layout};
-  \item \texttt{s\,-\,4\,-\,5\,-\,3\,-\,t} signifies the bottom route through the block diagram;
-  \item \texttt{1:4\,-\,6\,-\,2:5} connects the top two components of type 3 to the bottom two components of type 3, signifying the bridge.
-\end{itemize}
-Naturally such as expression is not necessarily unique, so that completely equivalently one may write:
-
-\noindent\texttt{sys <- graph.formula(s\,-\,1:4\,-\,6\,-\,2:5\,-\,3\,-\,t, 1\,-\,2, 4\,-\,5)}
-
-\
-
-With the structure defined and the individual components numbered, it 
-just remains to specify the types of each component.  This can be done
-using the \texttt{setCompTypes} function.  This function takes the
-system graph and a list of component type names (as the tag) and corresponding
-component numbers (as the value).  Thus, completing the example for Figure
-\ref{fig:bridge-layout}:
-
-\noindent\texttt{sys <- setCompTypes(sys, list("T1"=c(1,2,4,5), "T2"=c(6),}
-
-\noindent\texttt{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~"T3"=c(3)))}
-
-\
-
-Computing the survival signature then involves a simple function call:
-\noindent\texttt{survsig <- computeSystemSurvivalSignature(sys)}
-
-\subsection{Computing sets of system survival probabilities}
-
-Once the system has been correctly described using an undirected graph
-as above, the methods presented in Sections \ref{sec:nonparamapproach}
--- \ref{sec:setsofrel} can be used via the function
-\texttt{nonParBayesSystemInferencePriorSets}.
-
-The function prototype is:
-
-\noindent\texttt{nonParBayesSystemInferencePriorSets(at.times, survival.signature,}
-
-\noindent\texttt{~~~~~~~~~~test.data, nLower=2, nUpper=2, yLower=0.5, yUpper=0.5)}
-
-Aside from the system design, which can be passed to the function via
-the \texttt{survival.signature} argument, the remaining elements which
-must be specified are the:
-\begin{enumerate}
-  \item grid of times at which to evaluate the posterior, ${\cal T} = \{t_1, \ldots, \tmax\}$, via the \texttt{at.times} argument.
-  \item component test data $\vec{t}^k = (t^k_1, \ldots, t^k_{n_k})$ for $k=1,\dots,K$, via the \texttt{test.data} argument.
-  \item prior sets via the range of prior parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$, via the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower} and \texttt{yUpper} arguments.
-\end{enumerate}
-
-The grid of times, \texttt{at.times}, is specified as simply a vector 
-of time points.
-
-The \texttt{test.data} argument is a list of component type names (as
-the tag) and corresponding lifetime data (as the value), for example 
-a toy sized dataset for each component would be expressed as:
-
-\noindent\texttt{test.data=list("T1"=c(0.19, 0.73, 1.87, 1.17),}
-
-\noindent\texttt{~~~~~~~~~~~~~~~"T2"=c(0.22, 0.27, 0.63, 1.80, 1.25, 1.95),}
-
-\noindent\texttt{~~~~~~~~~~~~~~~"T3"=c(1.33, 0.65, 1.59))}
-
-Finally, there are multiple options for specifying the prior parameter
-sets.  Each of the \texttt{nLower}, \texttt{nUpper}, \texttt{yLower}
-and \texttt{yUpper} arguments can be specified as:
-\begin{itemize}
-  \item a single value for a homogeneous prior across time and components.  e.g.\ \texttt{nLower=2} $\implies \nktzl=2 \ \forall\,k, t$
-  \item a vector of values of length $|{\cal T}|$ (\texttt{length(at.times)}), for a time inhomogeneous prior which is identical across component types.
-  \item a data frame of size $1\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time homogeneous prior which varies across component types.
-  \item a data frame of size $|{\cal T}|\times K$, where each column is named the same as in the \texttt{survival.signature} and \texttt{test.data} arguments, for a time inhomogeneous prior which varies across component types.
-\end{itemize}
-
-With these arguments supplied,  \texttt{nonParBayesSystemInferencePriorSets} will then compute
-the posterior sets automatically in parallel across the cores of a
-multicore CPU and return a list with two objects, named \texttt{lower} 
-and \texttt{upper}, containing respectively the lower and upper bound 
-for the system reliability function $\Rsys(t)$.
-
 \end{document}

### 2016-01-24 ijar-npb-ms.tex
Table with surv. sign. for bridge system

@@
 as depicted in Figure~\ref{fig:bridge-layout}.
+The survival signature for this system is given in Table~\ref{tab:bridge-survsign}.
+All rows with T3 $=0$ have been omitted; without T3, the system cannot function, thus $\Phi = 0$.
+\begin{table}
+\centering
+\begin{tabular}{ccclccccl}
+  \toprule
+T1 & T2 & T3 & $\Phi$ & \quad & T1 & T2 & T3 & $\Phi$\\ 
+  \midrule
+0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
+1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
+2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
+3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
+4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Survival signature for the bridge system from Figure~\ref{fig:bridge-layout},
+omitting all rows with T3 $=0$, since $\Phi=0$ for these.}
+\label{tab:bridge-survsign}
+\end{table}
 For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
@@
 \end{tabular}
-\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system.}
+\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system example.}
 \label{tab:bridge-T3prior}

### 2016-01-24 bridgesystem.R

@@ -7,6 +7,7 @@ library("ReliabilityTheory")
 library(ggplot2)
 library(reshape2)
 library(RColorBrewer)
+library(xtable)
 
 bottomlegend <- theme(legend.position = 'bottom', legend.direction = 'horizontal', legend.title = element_blank())
 rightlegend <- theme(legend.title = element_blank())
@@ -79,5 +80,11 @@ pdf("bridge-earlyfailures.pdf", width=8, height=5)
 pdf("bridge-fittingfailures.pdf", width=8, height=5)
 p3
 dev.off()
+
+b3sigtable <- b3sig[b3sig$T3 == 1,]
+b3sigtable$T1 <- as.factor(b3sigtable$T1)
+b3sigtable$T2 <- as.factor(b3sigtable$T2)
+b3sigtable$T3 <- as.factor(b3sigtable$T3)
+xtable(b3sigtable)
 
 #

### 2016-01-24 ijar-npb-ms.tex
Table with surv. sign. for brake system

@@
 the car brakes when at least one brake pad assembly is actuated.
+All values for $\Phi \not\in \{0,1\}$ are given in Table~\ref{tab:brake-survsign}.
+\begin{table}
+\centering
+\begin{tabular}{cccclcccccl}
+  \toprule
+M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
+  \midrule
+1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
+1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
+1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
+0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
+0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
+0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
+0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
+0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
+0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
+0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
+   \bottomrule
+\end{tabular}
+\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesystem}.
+}
+\label{tab:brake-survsign}
+\end{table}
 The system layout is depicted in Figure~\ref{fig:brakesystem},

### 2016-01-24 brakingsystem.R

@@ -100,4 +100,20 @@ ab1 <- ab1 + bottomlegend
 pdf("brakingsystem-2.pdf", width=8, height=5)
 ab1
 dev.off()
+
+absigtable <- subset(absig, M == 1 | H == 1)
+absigtable <- subset(absigtable, P > 0)
+absigtable <- subset(absig, Probability != 0 & Probability != 1)
+absigtable$C <- as.factor(absigtable$C)
+absigtable$H <- as.factor(absigtable$H)
+absigtable$M <- as.factor(absigtable$M)
+absigtable$P <- as.factor(absigtable$P)
+absigtable2 <- data.frame(M=absigtable$M,
+                          H=absigtable$H,
+                          C=absigtable$C,
+                          P=absigtable$P, Probability=absigtable$Probability)
+
+absigxtable <- xtable(absigtable2)
+print(absigxtable, include.rownames=F)
+
 #

### 2016-01-24 ijar-npb-ms.tex
Corrections and improvements to theory.

--- 2016-01-22 ijar-npb-ms.tex
@@
 % ------------ custom defs -------------
+
+\usepackage{mathtools}
 
@@
 
-Based on expert assumptions for component failure distributions and component test data,
+Based on expert assumptions for component failure distribution and component test data,
 we make predictive inference for a system with components that are exchangeable
@@
 and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
-we propose an imprecise probability approach
+we propose an imprecise or interval probability approach
 based on sets of prior distributions defined through sets of canonical parameters.
@@
 
-%Our imprecise probability approach leads to sets of system reliability functions,
-%where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
-%reflects the precision of the reliability estimate:
-%a short range will indicate that we can quantify the reliability of the system quite precisely,
-%while a large range will indicate that our (probabilistic) knowledge is rather shaky --
-%remember that the reliability function is in essence a collection of probability statements.
-Our imprecise probability approach leads, for each $t$ in some grid of time points ${\cal T}$,
-to a posterior predictive probability interval for the event that the system will function at time $t$.
-The width of these intervals reflects the precision of the probability statement:
-a short range will indicate that we can quantify the system functioning probability quite precisely,
-while a large range will indicate that our (probabilistic) knowledge is indeterminate.
+Our imprecise probability approach leads to sets of system reliability functions,
+where the magnitude of the set, i.e., the width of the posterior predictive functioning probability interval
+reflects the precision of the reliability estimate:
+a short range will indicate that we can quantify the reliability of the system quite precisely,
+while a large range will indicate that our (probabilistic) knowledge is rather shaky --
+remember that the reliability function is in essence a collection of probability statements.
 
@@
 ultimately conveying a false sense of certainty
-by communicating that we can quantify the reliability of the system quite precisely when in fact we cannot do so.
+by communicating that we can quantify the reliability of the system quite precisely when in fact we can not.
 In contrast, our method will indicate prior-data conflict by wider bounds for $\Rsys(t)$.
@@
 This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
-Like \citet{CCMA14}, we will utilize the monotonicity of the survival signature for coherent systems
-to simplify computations.
+***This step is less trivial here as we must ensure to have probability distributions for these events,
+thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
+***covered because of parametric distribution, min and max over parameter sets (see section 6)***
+***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
+see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
+\td{Leave out the sentences framed with `***'?}
+Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
+to reflect uncertainty about system functioning for known states of its components.
+A further suggestion was to generalize this to lower and upper structure functions,
+within the theory of imprecise probability \citep{itip,CU11}.
+These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
+which in the latter case also becomes an imprecise probability.
+
+The survival signature is a powerful but rather basic concept.
+As such, further generalizations are conceptually easy,
+for example one can straightforwardly generalize the survival signature to multi-state systems
+such that it again summarizes the structure function
+in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
 
@@
 dominance is not guaranteed at a single value.  The following Theorem 
-provides the conditions under which an upper or lower limit has first-order stochastic dominance.
+provides simple sufficient conditions under which an upper or lower 
+limit has first-order stochastic dominance and has virtually no 
+computational overhead to test.
 
@@
   Then,
-  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  \[ y > \frac{s + m - 1}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
   and 
   \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
-  If $\frac{s}{N + m - 1} < y < \frac{s + m}{N + m - 1}$ then first-order stochastic dominance is not guaranteed.
 \end{theorem}
@@
 
-These first-order stochastic domination results now gives the exact 
-solution for $\lRsys(\cdot)$ and $\uRsys(\cdot)$.  Thus,
+If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
+Theorem 2 cannot determine stochastic dominance.  The following slightly
+more computationally costly Lemma may be able to determine first-order
+stochastic dominance in such situations.
+\begin{lemma}
+  \label{lem:n}
+  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
+  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
+  Then,
+  \[ \left. \begin{aligned}
+       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
+       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
+    \end{aligned} \right\}
+    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  and
+  \[ \left. \begin{aligned}
+       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
+       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
+    \end{aligned} \right\}
+    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+\end{lemma}
+The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
+In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
+the entire posterior system reliability function must be optimised to 
+find the minima/maxima.
+In practise, in the examples to be presented in the sequel, Theorem 
+\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
+stochastic dominance for the vast majority of time points, $t$,
+substantially lowering the computational costs of performing the
+minimisation/maximisation involved in finding the sets of system 
+reliability functions compared to either numerical optimisation or
+an exhaustive grid search (which would get exponentially slower in 
+the number of different components).
+
+Thus,
 %For $\lRsys(\cdot)$, the minimum is achieved at
@@
     \prod_{k=1}^K {m_k \choose l_k} \frac{B(l_k + \nktzo\yktzl + s^k_t, m_k - l_k + \nktzo(1-\yktzl) + n_k - s^k_t)}{B(\nktzo\yktzl + s^k_t, \nktzo(1-\yktzl) + n_k - s^k_t)} \label{eq:LwrSysPost}\\
- &\qquad \qquad \mbox{where } \nktzo = \left\{ \begin{aligned}
-   \nktzu & \quad\mbox{if}\quad \yktzl < \frac{s}{N + m - 1} \\
-   \nktzl & \quad\mbox{if}\quad \yktzl > \frac{s + m}{N + m - 1} \\
-   \mathrm{optimised} & \quad\mbox{if}\quad \frac{s}{N + m - 1} < \yktzl < \frac{s + m}{N + m - 1}
+ &\mathrm{where} \nonumber \\
+ &\nktzo = \left\{ \begin{aligned}
+   \nktzu & \quad\mbox{if}\ \yktzl < \frac{s^k_t}{n_k + m_k - 1} \vee \Big( \mathcal{L}_{\nktzu,\nktzl}(0) \ge 1 \wedge \mathcal{L}_{\nktzu,\nktzl}(m) \le 1 \Big) \\
+   \nktzl & \quad\mbox{if}\ \yktzl > \frac{s^k_t + m_k - 1}{n_k + m_k - 1} \vee \Big( \mathcal{L}_{\nktzu,\nktzl}(0) \le 1 \wedge \mathcal{L}_{\nktzu,\nktzl}(m) \ge 1 \Big) \\
+   & \quad\mbox{optimised otherwise}
  \end{aligned} \right. \nonumber
@@
 
-As example to illustrate the potential of our model,
-we consider a simplified automotive brake system.
-The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
+***Another example: simplified automotive breaking system, Figure~\ref{fig:breakingsystem}.
+Prior sets and data exemplary only, prior bounds more smooth curves?
+The master breaking cylinder (M) activates all four wheel braking cylinders (C1 -- C4),
 which in turn actuate a braking pad assembly each (P1 -- P4).
-The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
-the car brakes when at least one brake pad assembly is actuated.
-The system layout is depicted in Figure~\ref{fig:brakesystem},
-together with prior and posterior sets of reliability functions for the four component types and the complete system.
-Observed lifetimes from test data are indicated by tick marks in each of the four component type panels,
-where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
-We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
-and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
-Prior functioning probability bounds for M are based on
-a Weibull cdf with shape $2.5$ and scales $6$ and $8$ for the lower and upper bound, respectively.
-The prior bounds for P can be seen as the least committal bounds
-derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.
-
-***We see that posterior lower and upper functioning probabilities drop at those times $t$
-for which there is a failure time in the test data,
-or a drop in the prior functioning probability bounds.
-The lower bound for prior system reliability drops to zero at $t=5$
-since the prior lower bound for P drops to zero at $t=5$;
-for the system to function, at least one brake pad assembly must function.***
-
-For H, near-noninformative prior functioning probability bounds have been selected;
-with the upper bound for P being approximately one for $t \le 5$ as well,
-the prior upper system reliability bound for $t \le 5$ is close to one, too,
-since the system can function on H and one of P1 -- P4 alone.
-Note that the posterior functioning probability interval for M
-is wide not only due to the limited number of observations,
-but also because $\ntzu{\text{M}} = 8$ and the prior-data conflict reaction.
-
-Posterior functioning probability bounds for the complete system
-are much more precise than the prior system bounds,
-reflecting the information gained from component test data.
-The posterior system bounds can be also seen to reflect location and precision of the component bounds;
-for example, the system bounds drop drastically between $t=2.5$ and $t=3.5$
-mainly due to the drop of the bounds for P at that time.
+The hand break mechanism (H) goes directly to two brake pad assemblies P3 and P4;
+the car breaks when at least one brake pad assembly is actuated.***
 
@@
  vh path/.style={thick, to path={|- (\tikztotarget)}}]
-\node at (0,0) {\includegraphics[width=\textwidth]{brakingsystem-2}};
+\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-2}};
 \begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
@@
 \end{tikzpicture}
-\caption{Prior and posterior sets of reliability functions for a simplified automotive brake system
+\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
 with layout as depicted in the lower right panel.}
-\label{fig:brakesystem}
+\label{fig:breakingsystem}
 \end{figure}
@@
 
-The survival signature and its use for uncertainty quantification for system
-reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
-For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
-to reflect uncertainty about system functioning for known states of its components, with a further
-generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
-survival signature to multi-state systems such that it again summarizes the structure function
-in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
-
 ***Extend the model to deal with right-censored observations which are common in the reliability setting.
-The minimal assumption that a component can either fail immediately after censoring or live forever
-will be simple to implement but will lead to high imprecision,
+We believe that a minimal assumption (component can fail immediately after censoring or live forever)
+will be simple to implememt but will lead to high imprecision,
 whereas assuming exchangeability with other surviving components at moment of censoring
 will be more complex to accomodate but will lead to less imprecision.
-This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
-and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
 
@@
 \end{proof}
+
+%\begin{lemma}
+%  \label{lm:ineq}
+%  Let $a, b > 0$.  Then, \[ b > a \quad \iff \quad \frac{a}{b} < \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \quad \forall \  \xi, \varepsilon > 0 \]
+%\end{lemma}
+%\begin{proof}
+%  Since everything is strictly positive, the proof follows trivially:
+%  \begin{align*}
+%    \frac{a}{b} &< \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \\
+%    \iff \quad a b \xi + a \varepsilon &< a b \xi + b \varepsilon \\
+%    \iff \quad a &< b
+%  \end{align*}
+%\end{proof}
 
@@
   \end{align*}
-  This limit is hardest to satisfy for $l=m$ since $\nu-\nl>0$.
+  This limit is hardest to satisfy for $l=m-1$ since $\nu-\nl>0$ (note $l\ne m$ since we are evaluating $\mathcal{L}(l+1)/\mathcal{L}(l)$, so $m-1$ is the maximal value $l$ can take).
   Thus, for monotonicity to hold for all $l$, we require
   \begin{align*}
-    (\nu - \nl)[y (N + m - 1) - s] - m (\nu - \nl) &>0 \\
-    \implies (\nu - \nl)[y (N + m - 1) - s - m] &>0
+    (\nu - \nl)[y (N + m - 1) - s] - (m - 1) (\nu - \nl) &>0 \\
+    \implies (\nu - \nl)[y (N + m - 1) - s - m + 1] &>0
   \end{align*}
   Since $\nu-\nl>0$ by definition, we have a monotonically increasing 
-  likelihood ratio only when \[ y (N + m - 1) - s - m > 0. \]
+  likelihood ratio only when \[ y (N + m - 1) - s - m + 1 > 0. \]
   By a similar argument, the likelihood ratio is only monotonically decreasing when
@@
   Thus,
-  \[ y > \frac{s + m}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+  \begin{equation}
+    y > \frac{s + m - 1}{N + m - 1} \implies \beta_{\nu} \ge_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl}
+    \label{eq:nuDOMnl}
+  \end{equation}
   and 
-  \[ y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
+  \begin{equation}
+    y < \frac{s}{N + m - 1} \implies \beta_{\nu} \le_{\mathrm{lr}} \beta_{\nl} \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} 
+    \label{eq:nlDOMnu}
+  \end{equation}
   by \cite[Theorem 1.C.1, p.43]{shaked2007}.  In the intermediate case,
-  \[ \frac{s}{N+m-1} < y < \frac{s+m}{N+m-1} \]
-  we cannot definitively state the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
+  \[ \frac{s}{N+m-1} < y < \frac{s+m-1}{N+m-1} \]
+  standard likelihood ratio ordering theory cannot definitively state
+  the stochastic ordering on $\beta_{\nu}$ and $\beta_{\nl}$.
 \end{proof}
+
+\begin{proof}[\textbf{Proof of Lemma \ref{lem:n}, p\pageref{lem:n}}]
+  \label{prf:n2}
+  \eqref{eq:nuDOMnl} and \eqref{eq:nlDOMnu}
+  are sufficient but not necessary conditions.  Using theory in 
+  \cite{klenke2010} we can sharpen these conditions to provide
+  first-order stochastic dominance conditions for a larger range of
+  parameter values.
+
+  Proposition 2.1, p.399 of \cite{klenke2010} proves that half-monotone
+  likelihood ratio ordering --- i.e.\ monotonicity of $\mathcal{L}(l+1) / \mathcal{L}(l)$ ---
+  together with left and right tail conditions on $\mathcal{L}(\cdot)$
+  imply first order stochastic dominance.
+
+  \medskip
+  \noindent{\emph{Half-monotonicity of $\mathcal{L}(\cdot)$}}
+
+  Although there exist parameters for which $\mathcal{L}(\cdot)$ is
+  not monotone, it is half-monotone.  That is, $\mathcal{L}(l+1) / \mathcal{L}(l)$ is itself monotone.  For simplicity, write
+  \begin{align*}
+    \frac{\mathcal{L}(l+1)}{\mathcal{L}(l)} = \frac{(l + \pu)(\el - l)}{(l + \pl)(\eu - l)}
+    \quad \mbox{where} \left\{\begin{aligned}
+      \pu &= \nu y + s \\
+      \pl &= \nl y + s \\
+      \eu &= m - 1 + \nu (1 - y) + N - s \\
+      \el &= m - 1 + \nl (1 - y) + N - s
+    \end{aligned} \right.
+  \end{align*}
+  Then,
+  \begin{align*}
+    \frac{\mathcal{L}(l+2)/\mathcal{L}(l+1)}{\mathcal{L}(l+1)/\mathcal{L}(l)} =
+    \frac{(\pl + l)(\pu + l + 1)(\el - l - 1)(\eu - l)}
+           {(\pl + l + 1)(\pu + l)(\el -
+l)(\eu - l - 1)}
+    &> 1 \\
+    \iff \qquad \frac{\pl + l}{\pu + l} \cdot \frac{\el - l - 1}{\eu - l - 1} 
+    &> \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
+l}{\eu - l}
+  \end{align*}
+  But, $\pu > \pl > 0$, $\eu > \el > 0$, $l > 0$, %and Lemma \ref{lm:ineq} (p.\pageref{lm:ineq}) with $\xi=\varepsilon=1$ imply
+  so it is trivial to prove
+  \[
+    \frac{\pl + l}{\pu + l} > \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} > \frac{\el -
+l}{\eu - l} \qquad \forall\ l \in \{0,\dots,m\}
+  \]
+  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone increasing.
+
+  \medskip
+  \noindent{\emph{Tail conditions on $\mathcal{L}(\cdot)$}}
+
+  It is not difficult to derive the same loose bounds as in Theorem \ref{thm:n}
+  using the tail conditions.  However, it is also easy to see that 
+  these are sufficient but not necessary.  Sharpening these bounds
+  in terms of the other parameter values involves seemingly intractable
+  algebra, so we leave the tail condition as the alternative slightly 
+  more costly numerical check when the conditions of Theorem
+  \ref{thm:n} are not satisfied.  Evaluation of $\mathcal{L}(\cdot)$ 
+  at two values is still orders of magnitude less costly than 
+  reevaluation of $\lRsys(\cdot)$ or $\uRsys(\cdot)$.
+\end{proof}
+%  \medskip
+%  \noindent{\emph{ii) Left tail condition $\mathcal{L}(0) \le 1$}}
+%
+%  The second condition is that
+%  \begin{align*}
+%    \mathcal{L}(0) 
+%    &= \frac{\Gamma(m + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s)}
+%            {\Gamma(m + \nl (1 - y) + N - s) \Gamma(\nu (1 - y) + N - s)} \\
+%    &\qquad \times \frac{\Gamma(\nu+N) \Gamma(m+\nl+N)}
+%                       {\Gamma(\nl+N) \Gamma(m+\nu+N)} \le 1
+%  \end{align*}
+%  
+%  Let, $m=1$, it's minimal possible value.  Then,
+%  \begin{align*}
+%    &\frac{\Gamma(1 + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu + N) \Gamma(1 + \nl + N)}
+%            {\Gamma(1 + \nl (1 - y) + N - s) \Gamma(\nu (1 - y) + N - s) \Gamma(\nl + N) \Gamma(1 + \nu + N)} \\
+%    &= \frac{(\nu (1 - y) + N - s) (\nl + N)}{(\nl (1 - y) + N - s) (\nu + N)}
+%  \end{align*}
+%  But,
+%  \[ \frac{(\nu (1 - y) + N - s) (\nl + N)}{(\nl (1 - y) + N - s) (\nu + N)} \le 1 \quad\iff\quad y \le \frac{s}{N} \]
+%  
+%  Assume $y \le s / N$ and $\mathcal{L}(0 \mid m = k) \le 1$.  Then, for $m=k+1$
+%  \begin{align*}
+%    &\frac{\Gamma(k+1 + \nu (1 - y) + N - s) \Gamma(\nl (1 - y) + N - s) \Gamma(\nu + N) \Gamma(k+1 + \nl + N)}
+%            {\Gamma(k+1 + \nl (1 - y) + N - s) \Gamma(\nu (1 - y) + N - s) \Gamma(\nl + N) \Gamma(k+1 + \nu + N)} \\
+%    &= \frac{(k + \nu (1 - y) + N - s) (k + \nl + N)}{(k + \nl (1 - y) + N - s) (k + \nu + N)}\,\mathcal{L}(0 \mid m = k)
+%  \end{align*}
+%  So a sufficient condition (but maybe not necessary, since it is possible that $\mathcal{L}(0 \mid m = k) \ll 1$) is
+%  \begin{align*}
+%    \frac{(m-1 + \nu (1 - y) + N - s) (m-1 + \nl + N)}{(m-1 + \nl (1 - y) + N - s) (m-1 + \nu + N)} &\le 1 \\
+%    \iff \quad (\nl - \nu) (y (N + m - 1) - s) &\le 1 \\
+%    \iff \quad y &\le \frac{s}{N + m - 1}
+%  \end{align*}
+%  
+%  This sufficient condition does not provide sharper bounds than 
+%  those implied by likelihood ratio ordering.
+%  
+%  \medskip
+%  \noindent{\emph{iii) Right tail condition $\mathcal{L}(m) \ge 1$}}
+%  
+%  The second condition is that
+%  \begin{align*}
+%    \mathcal{L}(m) 
+%    &= \frac{\Gamma(m + \nu y + s) \Gamma(\nl y + s) \Gamma(\nu+N) \Gamma(m+\nl+N)}
+%            {\Gamma(m + \nl y + s) \Gamma(\nu y + s) \Gamma(\nl+N) \Gamma(m+\nu+N)} \ge 1 \\
+%  \end{align*}
+%
+%  Again, letting, $m=1$, it's minimal possible value,
+%  \begin{align*}
+%    &\frac{\Gamma(1 + \nu y + s) \Gamma(\nl y + s) \Gamma(\nu+N) \Gamma(1+\nl+N)}
+%            {\Gamma(1 + \nl y + s) \Gamma(\nu y + s) \Gamma(\nl+N) \Gamma(1+\nu+N)} \\
+%    &= \frac{(\nu y + s)(\nl + N)}{(\nl y + s)(\nu + N)}
+%  \end{align*}
+%  But,
+%  \[ \frac{(\nu y + s)(\nl + N)}{(\nl y + s)(\nu + N)} \ge 1 \quad\iff\quad y \ge \frac{s}{N} \]
+%  
+%  Assume $y \ge s / N$ and $\mathcal{L}(m \mid m = k) \ge 1$.  Then, for $m=k+1$
+%  \begin{align*}
+%    &\frac{\Gamma(k+1 + \nu y + s) \Gamma(\nl y + s) \Gamma(\nu+N) \Gamma(k+1+\nl+N)}
+%            {\Gamma(k+1 + \nl y + s) \Gamma(\nu y + s) \Gamma(\nl+N) \Gamma(k+1+\nu+N)} \\
+%    &= \frac{(k + \nu y + s) (k+\nl+N)}{(k + \nl y + s) (k+\nu+N)}\,\mathcal{L}(m \mid m = k)
+%  \end{align*}
+%  So a sufficient condition (but maybe not necessary, since it is possible that $\mathcal{L}(m \mid m = k) \gg 1$) is
+%  \begin{align*}
+%    \frac{(m-1 + \nu y + s) (m-1+\nl+N)}{(m-1 + \nl y + s) (m-1+\nu+N)} &\ge 1 \\
+%    \iff \quad (\nu - \nl) (y (N + m - 1) - s - m + 1) &\le 1 \\
+%    \iff \quad y &\le \frac{s + m - 1}{N + m - 1}
+%  \end{align*}
+%  
+%  This sufficient condition does not provide sharper bounds than 
+%  those implied by likelihood ratio ordering.
+%  
+%  \medskip
+%  \noindent{\emph{Conclusion}}
+%
+%  Thus,
+%  \[ \frac{s}{N+m-1} < y < \frac{s+m+1}{N+m-1} \implies \beta_{\nl} \sim_{\mathrm{hmlr}} \beta_{\nu} \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
+%  by \cite[Proposition 2.1, p.399]{klenke2010}.
 

### 2016-01-24 ijar-npb-ms.tex

--- 2016-01-24 ijar-npb-ms.tex
@@
 
+%\begin{lemma}
+%  \label{lm:ineq}
+%  Let $a, b > 0$.  Then, \[ b > a \quad \iff \quad \frac{a}{b} < \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \quad \forall \  \xi, \varepsilon > 0 \]
+%\end{lemma}
+%\begin{proof}
+%  Since everything is strictly positive, the proof follows trivially:
+%  \begin{align*}
+%    \frac{a}{b} &< \frac{a \xi + \varepsilon}{b \xi + \varepsilon} \\
+%    \iff \quad a b \xi + a \varepsilon &< a b \xi + b \varepsilon \\
+%    \iff \quad a &< b
+%  \end{align*}
+%\end{proof}
+
 \begin{proof}[\textbf{Proof of Theorem \ref{thm:n}, p\pageref{thm:n}}]

### 2016-01-25 bridgesystem.R
bridge system figures: move rightlegend down so 'Item' does not appear in the legend

@@ -70,7 +70,7 @@ b3df$Part <- ordered(b3df$Part, levels=c("T1", "T2", "T3", "System"))
 
 # + scale_colour_manual(values = c("red","blue"))
 # + scale_fill_brewer(palette="Set3")
-p3 <- ggplot(b3df, aes(x=Time)) + rightlegend + theme_bw()
+p3 <- ggplot(b3df, aes(x=Time)) + theme_bw()
 p3 <- p3 + scale_fill_manual(values = c("#b2df8a", "#1f78b4")) + scale_colour_manual(values = c("#b2df8a", "#1f78b4"))
 p3 <- p3 + geom_line(aes(y=Upper, group=Item, colour=Item)) + geom_line(aes(y=Lower, group=Item, colour=Item))
 p3 <- p3 + geom_ribbon(aes(ymin=Lower, ymax=Upper, group=Item, colour=Item, fill=Item), alpha=0.5)
@@ -78,7 +78,7 @@ p3 <- p3  + facet_wrap(~Part, nrow=2) + geom_rug(aes(x=x), data=b3dat) + xlab("T
 pdf("bridge-latefailures.pdf", width=8, height=5)
 pdf("bridge-earlyfailures.pdf", width=8, height=5)
 pdf("bridge-fittingfailures.pdf", width=8, height=5)
-p3
+p3 + rightlegend
 dev.off()
 
 b3sigtable <- b3sig[b3sig$T3 == 1,]

### 2016-01-31 ijar-npb-ms.tex
Fix inequality for half-monotonicity.
Finalised edits to Section 6 -- feel free to roll back any/all of them!

@@
 is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
-enabling diagnoses of prior-data conflict which is consequential at the system
+enabling diagnosis of prior-data conflict which is consequential at the system
 level, via sets of system reliability functions.
@@
 
-We therefore start by proving the following result, where indices are suppressed for readability.
+We therefore start by providing the following result, where indices are suppressed for readability.
 We use $\ge_{\mathrm{st}}$ to denote first-order stochastic dominance.
@@
 If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
-Theorem 2 cannot determine stochastic dominance.  The following slightly
-more computationally costly Lemma may be able to determine first-order
+Theorem 2 cannot determine stochastic dominance.  The following Lemma which is slightly
+more computationally costly, but still much faster than an exhaustive search, may be able to determine first-order
 stochastic dominance in such situations.
@@
 
-\td{*** Louis: I've edited to here so far, will continue editing rest of this section if we are happy with the above! ***}
-
+The result for $\uRsys(\cdot)$ is completely analogous.  It is interesting
+to note that if $m_k=1$ the bounds are sharp on stochastic dominance.
+In particular, when $m_k=1$, $\yktzl < \frac{s^k_t}{n_k}$ indicates the 
+lower bound is not in conflict with the observed data, whilst
+$\yktzl > \frac{s^k_t}{n_k}$ is in conflict since the observed
+empirical probability of functioning at time $t$ is below the
+prior lower bound.  Consequently, note that $\nktzl$ is 
+used only when the prior comes into conflict with the data.
+Since $\nktz$ controls the prior certainty, this accords with
+the intuition that the least certain prior bound is invoked
+when in a conflict setting and the more certain prior bound used when the data agrees.
+
+\subsection{Prior parameter choice}
 In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
 which define the set of prior discrete reliability functions for components of type $k$.
-We think this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
-%***How to choose the sets of priors for the survival function of type $k$ components,
-%i.e. how to choose $\PkZi{1}, \ldots \PkZi{\tmax}$?***
-
-As mentioned in Section~\ref{sec:nonparamapproach}, for the actual functioning probabilities $\ptk$
-it should hold that $p^k_{t_j} \ge p^k_{t_{j+1}}$. (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
+We advocate that this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.
+
+As mentioned in Section~\ref{sec:nonparamapproach}, the functioning probabilities $\ptk$
+must satisfy $p^k_{t_j} \ge p^k_{t_{j+1}}$.% (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
 %***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
@@
 %but does this need to hold for the prior guess range bound $\yktzu$?)***
-This naturally translates to conditions on the prior guess for $\ptk$,
-such that we propose that 
+This naturally translates to conditions on the prior for $\ptk$,
+so that for example 
 $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
-Due to $s^k_t/n_k$ decrasing in $t$ and the weighted average property of the update step for $\ykt$,
-this ensures that 
+Because $s^k_t/n_k$ is decreasing in $t$, the weighted average property of the update step in
+equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
 $\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
-In a situation where we are quite sure about the functioning probability for low $t$,
-but are unsure about what happens for larger $t$ and so want to be maximally cautious for those $t$,
-then we can let $\yktzl$ drop to (almost) 0, but $\yktzu$ should not increase.
+In situations where one has a high degree of certainty about the functioning probability for low $t$,
+but less certainty about what happens for larger $t$,
+then one can let $\yktzl$ drop to (almost) 0, but clearly $\yktzu$ should not increase.
 %***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
@@
 
-We think it is not advisable to express certainty about expected functioning probabilities
-with $\nktz$ bounds that vary strongly over $t$.
+It is inadvisable to express certainty in the expected functioning probabilities
+with $\nktz$ bounds that vary substantially over the range of $t$.
 %***Better to express certainty of prior guess via $\nktz$ bounds?\\
-With (strongly) differing $\nktz$ bounds, monotonicty for $\yktn$ bounds cannot be ensured.
+With (strongly) differing $\nktz$ bounds, monotonicity of the $\yktn$ bounds cannot be guaranteed.
 %it can happen that, e.g., $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$!\\
-E.g., when $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
-and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (so there is no prior-data conflict),
-and furthermore no failures happening in $[t_j, t_{j+1}]$, i.e., $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
-\begin{itemize}
-\item for $\nzu_{k,t_j} < \nzu_{k,t_{j+1}}$ we get $\ynu_{k,t_j} < \ynu_{k,t_{j+1}}$, and
-\item for $\nzu_{k,t_j} > \nzu_{k,t_{j+1}}$ we get $\ynl_{k,t_j} < \ynl_{k,t_{j+1}}$.
-\end{itemize}
-Again, this follows from the weighted average property of $\yktn$;
-for constant $\yktz$, the lower $\nktz$ the closer $\yktn$ is to $s^k_t/n_k$.
-% one can think of the update between interval and precise value: the lower $n$, the 'faster' the interval will shrink!)\\
-It is possible to construct similar examples also with regard to the lower bound $\nzl_{k,t_j}$.
-Therefore, we propose to take the same $\nktz$ bounds for all $t$, or, at most, to let them change with $t$ gradually only.
+For example, if $\yzu_{k,t_j} = \yzu_{k,t_{j+1}}$, $\yzl_{k,t_j} = \yzl_{k,t_{j+1}}$,
+and $s^k_{t_j}/n_k \in [\yzl_{k,t_j}, \yzu_{k,t_j}]$ (meaning there is no prior-data conflict),
+then should there be no observed failures in $[t_j, t_{j+1}]$, so that $s^k_{t_{j+1}}/n_k = s^k_{t_{j}}/n_k$, then
+\begin{align*}
+  \nzu_{k,t_j} < \nzu_{k,t_{j+1}} \quad&\implies\quad\ynu_{k,t_j} < \ynu_{k,t_{j+1}} \quad\mbox{and} \\
+  \nzu_{k,t_j} > \nzu_{k,t_{j+1}} \quad&\implies\quad\ynl_{k,t_j} < \ynl_{k,t_{j+1}}
+\end{align*}
+Again, this follows from \eqref{eq:nyupdate}, the weighted average property.
+It is possible to construct similar examples with regard to the lower bound $\nzl_{k,t_j}$.
+Therefore, we advise taking the same $\nktz$ bounds for all $t$ as far as possible.
+If they do change, it must be very gradual and we recommend diagnosing 
+any problems as above.
 
@@
 and the location of posterior intervals $[\yktnl, \yktnu]$ will be dominated by the location of $s^k_t/n_k$.
-Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values;
+Furthermore, the length of $[\yktnl, \yktnu]$ is shorter for low $\nktz$ values.  Specifically, 
 in a no-conflict situation, when $\nktzu = n_k$ then $[\yktnl, \yktnu]$ has half the length of $[\yktzl, \yktzu]$.
@@
 For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
-this can lead to improper posterior predictive distributions
-due to zero arguments for the Beta functions in the denominator of \eqref{eq:LwrSysPost}.
+this can lead to improper posterior predictive distributions.
 %Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
-But it is possible to choose values close to $0$ and $1$, respectively,
-and due to the linear update step for $\yktn$ (see Eq.~\eqref{eq:nyupdate}),
+However, it is possible to choose values close to $0$ and $1$, respectively,
+and due to the linear update step for $\yktn$ (see Equation~\eqref{eq:nyupdate}),
 posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
@@
 %How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
-Likewise, our nonparametric method does not bring unintuitive tail behaviour
+Likewise, our nonparametric method does not cause unintuitive tail behaviour
 as some parametric methods do;
-there is no problem in, e.g., assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.
+there is no problem, for example, with assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.
 
@@
 as then failure times in the test data are rounded up to the next $t \in {\cal T}$.
-We rather propose to elicit bounds for a subset of ${\cal T}$ only,
-and to fill up the time grid with the least committal bounds, i.e.,
+In the examples here we elicit bounds for a subset of ${\cal T}$
+and fill up the time grid with the least committal bounds, i.e.,
 taking $\yktzu$ equal to last (in the time sequence) elicited $\yktzu$,
@@
 l)(\eu - l - 1)}
-    &> 1 \\
+    &< 1 \\
     \iff \qquad \frac{\pl + l}{\pu + l} \cdot \frac{\el - l - 1}{\eu - l - 1} 
-    &> \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
+    &< \frac{\pl + l + 1}{\pu + l + 1} \cdot \frac{\el -
 l}{\eu - l}
@@
   \[
-    \frac{\pl + l}{\pu + l} > \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} > \frac{\el -
+    \frac{\pl + l}{\pu + l} < \frac{\pl + l + 1}{\pu + l + 1} \qquad\mbox{and}\qquad \frac{\el - l - 1}{\eu - l - 1} < \frac{\el -
 l}{\eu - l} \qquad \forall\ l \in \{0,\dots,m\}
   \]
-  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone increasing.
+  Thus we can conclude that $\mathcal{L}(\cdot)$ is half monotone decreasing.
 

### 2016-01-31 ijar-npb-ms.tex
Edits to Section 7 and 8 -- feel free to roll back any/all of them!

@@
 
-\section{Computations \& Examples}
+\section{Practical Usage and Examples}
 
@@
 and $\uRsys$ at different time points are performed in parallel
-automatically where the CPU has multiple cores.
+automatically where the CPU has multiple cores and making automatic
+use of the theoretical results in Section \ref{sec:setsofrel} where
+applicable, performing exhaustive search in the few cases they are not.
 
@@
 functions have been used in computing all the following examples for
-reproducibility.  \ref{ap:software} details how to use this software.
+reproducibility.  See Appendix \ref{ap:software} for further details of how to use this software.
 
 \subsection{Examples}
+
+\subsubsection{Toy example}
 
@@
 The posterior set of reliability functions for each component type and the whole system
-is considerably smaller as compared to the prior set
+is considerably smaller compared to the prior set
 (due to the low prior strength intervals
@@
 or a drop in the prior functioning probability bounds.
-Note that the lower bound for prior system reliability function is zero
+Note that the lower bound for the prior system reliability function is zero
 due to the prior lower bound of zero for T1;
@@
 Note that the posterior system functioning probability is constant for $t \in [1,2]$
-because the prior functioning probability is constant for $t \in [1,2]$
-and there are no failure times $\in [1,2]$ in the test data.
+because in that interval the prior functioning probability is constant
+and there are no observed failures.
 
@@
 where we see wider bounds as compared to the other two scenarios
-especially between $t=2$ and $t=4$.
+especially between $t=2$ and $t=4$.  In particular, also note
+that at the system level prior data conflict ceases after
+$t \approx 2.6$, although the prior data conflict for the 
+individual component type T3 extends well beyond $t=4$.  This 
+demonstrates the power of this technique to identify prior
+data conflict which is actually consequential at the system 
+level, not just the component level --- in other words, for 
+mission times $t>2.6$, we can diagnose that the prior data conflict 
+need not be of concern for this system viewed as a whole.
 
@@
 
-As example to illustrate the potential of our model,
-we consider a simplified automotive brake system.
+\subsubsection{Automotive brake system}
+
+We also consider a simplified automotive brake system.
 The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
@@
 derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.
-
-***We see that posterior lower and upper functioning probabilities drop at those times $t$
-for which there is a failure time in the test data,
-or a drop in the prior functioning probability bounds.
-The lower bound for prior system reliability drops to zero at $t=5$
-since the prior lower bound for P drops to zero at $t=5$;
-for the system to function, at least one brake pad assembly must function.***
 
@@
 
+It is also interesting to note that the prior data conflict 
+which is consequential at the system level occurs over 
+roughly the same range in $t$ as there is prior data 
+conflict for component type P.  Indeed, this occurs despite there being 
+prior data conflict in both M and C over much larger ranges, 
+giving valuable insight into which prior requires further 
+expert attention --- thus the technique avoids wasted time 
+addressing prior data conflict in components which may not 
+be relevant when propagated to the uncertainty in the whole system.
+
 %***calculate and show $\Rsys(t)$ plots for a range of examples (keep system layout fixed?):
@@
 
-***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
-(could nicely illustrate challenges in decision making with intervals:
-do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
-or do I rather add redundancy such that effect is smaller but more certain?***
-
-***Other interesting extra illustration:
-show effect of replacement of components in system at certain time points
-(could be corrective (component failed) or preventive replacement),
-replaced components constitute a new type with shifted component reliability function***
-
-\section{Conclusions and Outlook}
-
-Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
-However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
-and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.
-
-The survival signature and its use for uncertainty quantification for system
-reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
-For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
-to reflect uncertainty about system functioning for known states of its components, with a further
-generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
-survival signature to multi-state systems such that it again summarizes the structure function
-in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
-
-***Extend the model to deal with right-censored observations which are common in the reliability setting.
-The minimal assumption that a component can either fail immediately after censoring or live forever
-will be simple to implement but will lead to high imprecision,
-whereas assuming exchangeability with other surviving components at moment of censoring
-will be more complex to accomodate but will lead to less imprecision.
-This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
-and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
-
-***right-censoring will also allow to use data from running system,
-to calculate its remaining useful life (RUL).
+%***Some extra illustrations? E.g. the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper?
+%(could nicely illustrate challenges in decision making with intervals:
+%do I prefer adding redundancy such that there is a chance for a large effect, but high uncertainty for it,
+%or do I rather add redundancy such that effect is smaller but more certain?***
+%
+%***Other interesting extra illustration:
+%show effect of replacement of components in system at certain time points
+%(could be corrective (component failed) or preventive replacement),
+%replaced components constitute a new type with shifted component reliability function***
+
+\section{Conclusions}
+
+In this paper we have contributed an imprecise Bayesian nonparametric approach
+to system reliability with multiple types of components.
+The approach allows modeling partial or imperfect prior knowledge on component failure distributions
+in a flexible way through bounds on the functioning probability for a grid of time points, 
+and combines this information with test data in an imprecise Bayesian framework.
+Component-wise predictions on the number of functioning components
+are then combined to bounds for the system survival probability by means of the survival signature.
+New results on first-order stochastic dominance for the Beta-Binomial distribution
+enable closed-form solutions for these bounds in most cases and 
+avoid exponential growth in the complexity of computing the estimate
+as the number of components grows.
+The widths of the resulting system reliability bounds
+reflect the amount of test data, the precision of prior knowledge,
+and crucially provide an easily used method to identify 
+whether these two information sources are in conflict in a
+way which is of consequence to the whole system reliability
+estimate.
+
+These methodological contributions can be immediately used in
+applications by reliability practitioners as a result of the 
+easy to use software tools which have been provided.
+
+%% LOUIS: do we really want outlook?  I am inclined not to
+%% discuss this in a non-review/tutorial paper because we
+%% don't want to alert others and get scooped on future
+%% ideas!
+%Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
+%However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
+%and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.  
+%
+%The survival signature and its use for uncertainty quantification for system
+%reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
+%For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
+%to reflect uncertainty about system functioning for known states of its components, with a further
+%generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
+%survival signature to multi-state systems such that it again summarizes the structure function
+%in a manner that is sufficient for a range of uncertainty quantifications for the system reliability. 
+%
+%
+%***Extend the model to deal with right-censored observations which are common in the reliability setting.
+%The minimal assumption that a component can either fail immediately after censoring or live forever
+%will be simple to implement but will lead to high imprecision,
+%whereas assuming exchangeability with other surviving components at moment of censoring
+%will be more complex to accomodate but will lead to less imprecision.
+%This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
+%and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
+%
+%***right-censoring will also allow to use data from running system,
+%to calculate its remaining useful life (RUL).
+%
 

### 2016-01-31 ijar-npb-ms.tex
My acknowledgements
minor tweaks in section 6 and computation of bounds in separate subsection

@@
 providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
-is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
-enabling diagnosis of prior-data conflict which is consequential at the system
-level, via sets of system reliability functions.
+is extended to sets of system reliability functions
+by incorporating the sets of priors approach of \citet{2009:WalterAugustin}.
+This allows for partial or vague specification of prior component reliability functions,
+and enables diagnosis of prior-data conflict which is consequential at the system level.
+
+\subsection{Computation of bounds}
 
@@
 find the minima/maxima.
-In practise, in the examples to be presented in the sequel, Theorem 
+In practice, in the examples to be presented in the sequel, Theorem 
 \ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
@@
 \subsection{Prior parameter choice}
+
 In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
@@
 Because $s^k_t/n_k$ is decreasing in $t$, the weighted average property of the update step in
-equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
+Equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
 $\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
@@
 However, it is possible to choose values close to $0$ and $1$, respectively,
-and due to the linear update step for $\yktn$ (see Equation~\eqref{eq:nyupdate}),
+and due to the linear update step \eqref{eq:nyupdate} for $\yktn$,
 posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
@@
 as some parametric methods do;
-there is no problem, for example, with assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.
+there is no problem, for example, with assigning $\yktnu$ near-zero for large $t$ if prior knowledge suggests so.
 
@@
 
+\section*{Acknowledgements}
+
+Louis Aslett was supported by the i-like project (EPSRC grant reference number EP/K014463/1).
+
 % ------------ bibliography -------------

### 2016-01-31 ijar-npb-ms.tex
acknowledgements Gero
Abstract and intro (done but maybe incomplete if too compact?)  Lots of text left lying round in intro until decision if it is ok or not.

--- 2016-01-31 ijar-npb-ms.tex
@@
 \begin{abstract}
-Imprecise Bayesian nonparametric approach to system reliability with multiple types of components,
-sets of priors through sets of canonical parameters,
-leading to sets of system reliability functions,
-reflection of prior-data conflict
+An imprecise Bayesian nonparametric approach
+to system reliability with multiple types of components
+is developed.
+This allows modelling partial or imperfect prior knowledge on component failure distributions
+in a flexible way through bounds on the functioning probability.
+Given component level test data these bounds are propagated 
+to bounds on the posterior predictive distribution for the reliability of
+a new system containing components exchangeable with those 
+used in testing.  The method further enables identification 
+of prior data conflict at the system level based on component level test data.
+
+There are new results on first-order stochastic dominance for the Beta-Binomial distribution
+which make the technique computationally tractable.  These methodological contributions can be immediately used in
+applications by reliability practitioners using the freely available
+software tools which are provided.
 \end{abstract}
@@
 
-(some sentences may be useful for the abstract instead)
-
-System with components of $k=1,\ldots,K$ different types.
-There are $m_k$ components of type $k$ in the system.
-Components of the same type are i.i.d.\ and independent of components of other types.
-Arbitrary system layout, i.e.\ any series / parallel combination, $k$ out of $n$ etc.
+A critique of the methodological approach to a reliability 
+analysis may often encompass a few common concerns.
+First, in a parametric 
+setting, there may be no particularly strong reason to
+believe that the small part of component model
+space covered by a particular probability distribution 
+necessarily contains the `true' component lifetime distribution.
+Further, Bayesian methods may be invoked in order to 
+incorporate expert opinion or other knowledge which falls
+outside the specific testing data under consideration.  The 
+classic concern here is in whether one can truly express 
+ones beliefs with the exactness a prior requires.  Finally,
+it would be valuable in application to have a means of identifying when the
+prior choice is having a strong effect and when not.  Any method 
+hoping to address these concerns must do so whilst enabling 
+realistic system models (with heterogeneous component types)
+and remain computationally tractable.
+
+Herein, we make steps toward addressing these concerns by developing
+a nonparametric method which utilises imprecise probability 
+to encapsulate more vague or imperfect prior beliefs using
+upper and lower probabilities.  This overcomes the concern
+about component lifetimes being outside a particular 
+parametric family, uses a more flexible prior modelling 
+framework and leads to an easy method of detecting prior-data
+conflict which should be of concern at the system level.
+
+Furthermore, the method is based on the survival signature, a 
+recent development which naturally accommodates 
+heterogeneous component types laid out in any arbitrary
+manner which maintains coherency of the system.  As will be 
+seen in the sequel, the method remains computationally tractable.
+
+\td{*** Some more words on the benefits?}
+
+In Section \ref{sec:survsign} we review the survival 
+signature and in Section \ref{sec:nonparamapproach} we 
+review the nonparametric approach to Bayesian reliability analysis
+upon which our work builds 
+\cite{2015:bayessurvsign}.  Section \ref{sec:reparam} details
+the reparameterisation of that approach which enables the natural
+formulation of the system reliability bounds and which leads to
+nice closed form results in some later theory.
+Section \ref{sec:setsofbetapriors} lays the ground work to incorporate imprecise probability,
+culminating in the main results and contributions of this 
+work, detailed in Section \ref{sec:setsofrel}.  Section 
+\ref{sec:examples} provides details on the software contributions
+of this work and shows two worked examples
+demonstrating the practicality and usefulness of the method.
+
+\td{*** LOUIS: Not sure if the above is too compact or ok and whether we need to be more expansive in the orange bit above?
+Thoughts appreciated!
+I've left text below which you may want to draw from?
+***}
 
@@
 Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
-naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
+a Bayesian model for the functioning probability at each time point naturally arises (see Section~\ref{sec:nonparamapproach}).
 To account for uncertainty in the choice of prior
@@
 or by taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.
-
-\td{***illustrate discrete distribution with a graph of R, f, h?***}
 
@@
 \section{Practical Usage and Examples}
-
+\label{sec:examples}
 %***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
@@
 to system reliability with multiple types of components.
-The approach allows modeling partial or imperfect prior knowledge on component failure distributions
+The approach allows modelling partial or imperfect prior knowledge on component failure distributions
 in a flexible way through bounds on the functioning probability for a grid of time points, 
@@
 %
+
+\section*{Acknowledgements}
+
+Louis Aslett was supported by the i-like project (EPSRC grant reference number EP/K014463/1).
 

### 2016-01-31 ijar-npb-ms.tex
tweaks in Section 7

--- 2016-01-31 ijar-npb-ms.tex
@@
 In Figure~\ref{fig:bridge-early},
-test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
+test data of component type T3 is $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
 and so earlier than expected.
@@
 In Figure~\ref{fig:bridge-late}, 
-test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
+test data of component type T3 is $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
 and so observed failures are later than expected.
@@
 especially between $t=2$ and $t=4$. In particular, also note
-that at the system level prior data conflict ceases after
-$t \approx 2.6$, although the prior data conflict for the 
+%that at the system level prior data conflict ceases after
+that at the system level posterior bounds are a subset of prior bounds after
+$t = 2.6$, although prior-data conflict for the 
 individual component type T3 extends well beyond $t=4$.  This 
-demonstrates the power of this technique to identify prior
-data conflict which is actually consequential at the system 
+demonstrates the power of this technique to identify prior-data conflict
+which is actually consequential at the system 
 level, not just the component level --- in other words, for 
-mission times $t>2.6$, we can diagnose that the prior data conflict 
-need not be of concern for this system viewed as a whole.
+mission times $t>2.6$, we can diagnose that the prior-data conflict 
+need not be of elevated concern for this system viewed as a whole.
+%mission times $t>2.6$, we see that posterior system reliability bounds
+%are in line with prior expectations and so need not be of elevated concern. 
+Nevertheless, the posterior system reliability bounds are wider than in the no-conflict case for $t \in [1, 4.4]$,
+signalising the general need for caution in this scenario.
 
@@
 derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.
-
+%
 For H, near-noninformative prior functioning probability bounds have been selected;
@@
 
-It is also interesting to note that the prior data conflict 
+It is also interesting to note that the prior-data conflict 
 which is consequential at the system level occurs over 
-roughly the same range in $t$ as there is prior data 
-conflict for component type P.  Indeed, this occurs despite there being 
-prior data conflict in both M and C over much larger ranges, 
+roughly the same range in $t$ as there is prior-data 
+conflict for component type P.
+%It is also interesting to note that the range in $t$
+%for which posterior system reliability bounds are not a subset of prior bounds
+%is roughly the same as there is prior-data conflict for component type P.
+Indeed, this occurs despite there being 
+prior-data conflict in both M and C over much larger ranges, 
 giving valuable insight into which prior requires further 
 expert attention --- thus the technique avoids wasted time 
-addressing prior data conflict in components which may not 
+addressing prior-data conflict in components which may not 
 be relevant when propagated to the uncertainty in the whole system.
@@
 \section*{Acknowledgements}
+
+Gero Walter was supported by the DINALOG project
+``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).
 

### 2016-01-31 ijar-npb-ms.tex
Section 8 (with outlook) and only first name initials in Biblography

@@
 
+%\subsection{Summary}
 In this paper we have contributed an imprecise Bayesian nonparametric approach
@@
 These methodological contributions can be immediately used in
-applications by reliability practitioners as a result of the 
-easy to use software tools which have been provided.
+applications by reliability practitioners as %a result of the 
+%easy to use software tools which have been provided.
+we provide easy to use software tools.
+%for the computation of the survival signature and system reliability bounds.
 
@@
 %% ideas!
-%Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
-%However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
-%and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.  
-%
-%The survival signature and its use for uncertainty quantification for system
-%reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
-%For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
-%to reflect uncertainty about system functioning for known states of its components, with a further
-%generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
+%\subsection{Outlook}
+%On further avenues for research,
+An important next step is to extend the model to include right-censored observations which are common in the reliability setting.
+In particular, this allows to use component failure observations from a running system
+to calculate its remaining useful life.
+%For treatment of censored observations
+We see two potential approaches.
+First, to obtain lower and upper system reliability bounds 
+one can assume that a component either fails immediately after censoring or
+continues to function during the entire time horizon.
+This minimal assumption will be simple to implement but will lead to high imprecision.
+Alternatively, one can assume exchangeability with other surviving components at the moment of censoring.
+This approach will be more complex to accomodate but will lead to less imprecision.
+Indeed, this assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
+and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
+
+Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
+However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
+and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.
+
+The survival signature and its use for uncertainty quantification for system
+reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
+For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
+to reflect uncertainty about system functioning for known states of its components, with a further
+generalization to imprecise probabilities possible.
+% It is also conceptually easy to generalize the
 %survival signature to multi-state systems such that it again summarizes the structure function
 %in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
-%
-%
-%***Extend the model to deal with right-censored observations which are common in the reliability setting.
-%The minimal assumption that a component can either fail immediately after censoring or live forever
-%will be simple to implement but will lead to high imprecision,
-%whereas assuming exchangeability with other surviving components at moment of censoring
-%will be more complex to accomodate but will lead to less imprecision.
-%This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
-%and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
-%
-%***right-censoring will also allow to use data from running system,
-%to calculate its remaining useful life (RUL).
-%
 

### 2016-01-31 ijar-npb-ms.tex
Intro section done (hopefully)

@@
 
-\author[ein]{Gero Walter\fnref{fn1}}
+\author[ein]{Gero Walter}
 \ead{g.m.walter@tue.nl}
@@
 \address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}
-
-\fntext[fn1]{Gero Walter was supported by the Dinalog project
-``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).}
 
@@
 Given component level test data these bounds are propagated 
-to bounds on the posterior predictive distribution for the reliability of
+to bounds on the posterior predictive distribution for the functioning probability of
 a new system containing components exchangeable with those 
 used in testing.  The method further enables identification 
-of prior data conflict at the system level based on component level test data.
-
-There are new results on first-order stochastic dominance for the Beta-Binomial distribution
-which make the technique computationally tractable.  These methodological contributions can be immediately used in
-applications by reliability practitioners using the freely available
-software tools which are provided.
+of prior-data conflict at the system level based on component level test data.
+%
+New results on first-order stochastic dominance for the Beta-Binomial distribution
+make the technique computationally tractable.
+Our methodological contributions can be immediately used in
+applications by reliability practitioners
+as we provide easy to use software tools.
 \end{abstract}
@@
 Imprecise probability \sep
-Bayesian Nonparametrics \sep
+Bayesian nonparametrics \sep
 Prior-data conflict
@@
 \section{Introduction}
+
+System reliability analysis is concerned with
+estimating the lifetime $\Tsys$ of complex systems.
+Usually, the goal is to determine the system reliability function $\Rsys(t) = P(\Tsys > t)$
+based on the lifetime distributions of system components.
 
@@
 classic concern here is in whether one can truly express 
-ones beliefs with the exactness a prior requires.  Finally,
+ones beliefs with the exactness a prior distribution requires.  Finally,
 it would be valuable in application to have a means of identifying when the
@@
 Herein, we make steps toward addressing these concerns by developing
-a nonparametric method which utilises imprecise probability 
-to encapsulate more vague or imperfect prior beliefs using
+a nonparametric method which utilises imprecise probability \cite{itip,1991:walley}
+to model more vague or imperfect prior beliefs using
 upper and lower probabilities.  This overcomes the concern
@@
 parametric family, uses a more flexible prior modelling 
-framework and leads to an easy method of detecting prior-data
-conflict which should be of concern at the system level.
-
-Furthermore, the method is based on the survival signature, a 
-recent development which naturally accommodates 
-heterogeneous component types laid out in any arbitrary
-manner which maintains coherency of the system.  As will be 
-seen in the sequel, the method remains computationally tractable.
-
-\td{*** Some more words on the benefits?}
+framework and leads to an easy method of detecting 
+conflicts between prior assumptions and observed failure times in test data.
+In the general context of Bayesian methods,
+this phenomenon is known as \emph{prior-data conflict},
+see, e.g., \cite{2006:evans} or \cite{2015:bickel}.
+% which should be of concern at the system level.
+
+Furthermore, the method is based on the survival signature \cite{2012:survsign},
+a recent development which naturally accommodates 
+heterogeneous component types laid out in any arbitrary manner.
+%which maintains coherency of the system.
+By separating the (time-invariant) system structure from the time-dependent failure probabilities of components,
+it allows straightforward and efficient computation of $\Rsys(t)$.
+%by partitioning the event $\Tsys > t$ according to the number of functioning components of each type at time $t$.
+
+Our imprecise probability approach provides bounds for $\Rsys(t)$
+by computing, for each $t$ in an arbitrarily fine grid of time points ${\cal T}$,
+the posterior predictive probability interval for the event $\Tsys > t$. %that the system will function at time $t$.
+Assuming the number of functioning components for each type and time $t$ as binomially distributed, 
+the intervals are derived from an imprecise Bayesian model using sets of conjugate Beta priors
+which allow to specify weak or partial prior information in an intuitive way.
+The width of the resulting posterior predictive probability intervals
+reflects the precision of the corresponding probability statements:
+a short range indicates that the system functioning probability can be quantified quite precisely,
+while a large range will indicate that our (probabilistic) knowledge is indeterminate.
+In particular, prior-data conflict leads to more cautious probability statements:
+When there is not enough data to overrule the prior,
+it is unclear whether to put more trust to prior assumptions or to the observations,
+and posterior inferences clearly reflect this state of uncertainty by larger ranges.
+
+While the use of imprecise probability methods can often lead to tractability issues,
+new results on first-order stochastic dominance for the Beta-Binomial distribution
+keep the need for numerical optimization in our model to a minimum.
+%make the technique computationally tractable.
+%As will be seen in the sequel, the method remains computationally tractable.
+%\td{*** Some more words on the benefits?}
 
@@
 the reparameterisation of that approach which enables the natural
-formulation of the system reliability bounds and which leads to
+formulation of the system reliability bounds, leading to
 nice closed form results in some later theory.
@@
 
+\iffalse
 \td{*** LOUIS: Not sure if the above is too compact or ok and whether we need to be more expansive in the orange bit above?
@@
 In Section~\ref{sec:survsign}, we describe ***
+\fi
 
@@
 in a new system, based on the lifetime data and the prior information,
-is then a so-called Beta-Binomial distribution,
+is then given by a so-called Beta-Binomial distribution,
 $C^k_t \mid s^k_t \sim \bebin(m_k, \alpha^k_t + s^k_t, \beta^k_t + n_k - s^k_t)$.
@@
 the prior mean $\yz$ and $s/n$ (the fraction of functioning components in the data),
-with weights $\nz$ and $n$, respectively.
+with weights proportional to $\nz$ and $n$, respectively.
 Therefore $\nz$ takes on the same role for the prior mean $\yz$
@@
 
-Functions which make it easy to use the methods of this paper have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
-There are two functions of particular note: \texttt{computeSystemSurvivalSignature} and \texttt{nonParBayesSystemInferencePriorSets}
+Functions which make it easy to use the methods of this paper
+have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
+There are two functions of particular note: \texttt{computeSystemSurvivalSignature}
+and, implementing the result from Appendix~\ref{ap:proofs} above, \texttt{nonParBayesSystemInferencePriorSets}.
 

### 2016-06-12 ijar-npb-ms.tex
par on dependence modelling by Frank

@@
 to simplify computations.
+
+While there are, as mentioned above, no restrictions on dependence of failure times of components of different types that can be reflected by the survival signature method, some possible dependencies will require thoughtful consideration.
+For example, it may be the case that components that are near to each other in the system have a stronger dependency of their failure times than components that are further apart.
+If this is the case there are several options, the two main ones are as follows.
+First, if there is detailed knowledge about such dependence (as e.g.
+modelled in popular spatial statistics approaches) then there are probably no components that can be grouped, hence one has to use the full structure function.
+In practice, this may be feasible for small systems, but for large systems one would probably still wish to make some exchangeability assumptions in order to enable analysis, where it is understood that this is only approximate.
+The second case results from this, namely that one can still define groups of components which have exchangeable failure times and which are related in the same way to other groups of components to facilitate the dependence modelling.
+For example, one might consider components in a large electricity network to have differing failure time characteristics depending on physical location, e.g.
+windturbines near hills or at sea, while apart from the location aspect one would consider their failure times exchangeable.
+In such cases, these are represented by different groups in the survival signature approach.
 

### 2016-06-18 answer-to-reviewers.tex
set up answers to reviewers, Frank's suggetions for Reviewer 2 worked into the paper

\documentclass[12pt, a4paper]{elsarticle}

\usepackage[utf8]{inputenc}
\usepackage[OT1]{fontenc}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{etoolbox}
\usepackage{url}
%\usepackage{tikz}
%\usetikzlibrary{shapes.misc,fit}

\usepackage[bookmarks]{hyperref}

% ------------ custom defs -------------

\usepackage{mathtools}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\posrealszero}{\reals_{\ge 0}}
\newcommand{\naturals}{\mathbb{N}}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bs#1}}

\newcommand{\uz}{^{(0)}} % upper zero
\newcommand{\un}{^{(n)}} % upper n
\newcommand{\ui}{^{(i)}} % upper i

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\Rsys}{R_\text{sys}}
\newcommand{\lRsys}{\ul{R}_\text{sys}}
\newcommand{\uRsys}{\ol{R}_\text{sys}}

\newcommand{\Fsys}{F_\text{sys}}
\newcommand{\lFsys}{\ul{F}_\text{sys}}
\newcommand{\uFsys}{\ol{F}_\text{sys}}

\def\Tsys{T_\text{sys}}

\newcommand{\E}{\operatorname{E}}
\newcommand{\V}{\operatorname{Var}}

\newcommand{\indic}{\mathbb{I}}

\newcommand{\ber}{\operatorname{Bernoulli}} 
\newcommand{\bin}{\operatorname{Binomial}}
\newcommand{\be}{\operatorname{Beta}} 
\newcommand{\bebin}{\operatorname{Beta-Binomial}}

\def\tmax{t_\text{max}}
\def\tnow{t_\text{now}}
\def\tpnow{t^+_\text{now}}

\newcommand{\ptk}{p^k_t}

\input{nydefs.tex}

%\newcommand{\comments}[1]{{\small\color{gray} #1}}
\newtoggle{td}
\newcommand{\td}[1]{%
  \iftoggle{td}{%
    \todo[inline]{#1}%
  }{}%
}

% ------------ options -------------

\allowdisplaybreaks

\toggletrue{td} % show todo's
%\togglefalse{td} % hide todo's

%\biboptions{longnamesfirst,angle,semicolon}

\journal{IJAR}

\begin{document}

\begin{frontmatter}
\title{Answer to Reviewers' Comments on our Manuscript ``Bayesian Nonparametric System Reliability\\ using Sets of Priors''}

\author[ein]{Gero Walter}
\ead{g.m.walter@tue.nl}
\author[oxf]{Louis J.M. Aslett}
\ead{louis.aslett@stats.ox.ac.uk}
\author[dur]{Frank P.A. Coolen}
\ead{frank.coolen@durham.ac.uk}

\address[ein]{School of Industrial Engineering, Eindhoven University of Technology, Eindhoven, NL}
\address[oxf]{Department of Statistics, University of Oxford, Oxford, UK}
\address[dur]{Department of Mathematical Sciences, Durham University, Durham, UK}

\begin{abstract}
The reviewers' comments reproduced here, with our answers interlaced. Our answers are printed in \emph{italic}.
\end{abstract}
\end{frontmatter}

\section*{Reviewer 1}

\section*{Reviewer 2}

This paper introduces an extension of a non-parametric Bayesian method used in reliability assessment to include sets of priors in the assessment of posterior probabilities. The goal is to detect conflict between prior information and observed data, this conflict impacting the imprecision of the inferences. The used method is based on the use of survival signature combined with an assumption of component independence.

The paper is very nicely written, with an incremental and illustrative introduction of various concepts. I think it is accessible to most readers with basic knowledge in reliability and in probability, and presents both worked out examples and software implementation tools. The theoretical results used to speed up computations, while not especially impressive and deep, are interesting and useful. I would therefore recommend to accept the paper, possibly after some minor changes integrating my (very) few comments.

Specific comments:

* My main (and only substantial) comment about the paper is that it starts by seeling advantages of the survival signature, which are then completely forgotten since all mathematical developments concern independent components. Also, it seems to me that some points are a bit "oversold", for instance while I agree that the dependence of identical component types or between component types can easily be integrated, some other kind of dependence are impossible to implement (for instance, dependencies related to the position of components within the system, which are quite likely to occur in practice). I would therefore like the authors to 1) perhaps also explain the limitations of the survival signature and 2) add some (small?) discussion about what becomes of the current problem when independence between all components do not hold anymore. More specifically:

\medskip
\emph{We think the reviewer does not fully acknowledge the central benefit of the survival signature, which is present also for independent components: Information on the system layout (which does not change over time) is fully separated from (time-dependent) component failure probabilities.}
\medskip

- top of P5: it would be fair to mention that dependencies related to component positions cannot easily be integrated to the signature (or at least I do not see how, if this is doable a reference/explanation should be provided.

\medskip
\emph{We added a paragraph at the end of Section 2 to address this point.}
\medskip

- P6, 38/40: from here independence is assumed in the rest of the paper. It would be fair to discuss what extensions to non-independent cases are easy/difficult to produce, otherwise the advantage previously put forward of survival signatures simply disappears when adopting the author proposal.

\medskip
\emph{The crucial advantage of the survival signature approach is used throughout the paper, namely that it ensures all aspects of the system design are taken into account. It is indeed assumed, from the location indicated on, that components of the same type have conditionally independent and identically distributed failure times, conditional on the parameters $p_t^k$. This is a pretty standard assumption in reliability theory and we feel it is appropriate in this paper. However, crucially the approach presented enables learning about the parameters $p_t^k$ and keeps a dependence between the failure times of the components of the same type in the system, as common in Bayesian predictive distributions for multiple future observations.}
\medskip

* Perhaps mention somewhere (P19 or somewhere after?) that the elicited prior somehow correspond to a p-box? During my reading, I was actually reading to which extent results concerning p-boxes in general could not be useful in this setting.

* P19, L56: where $\to$ when

\medskip
\emph{Fixed, thanks.}
\medskip

* Figures 5,6,7: since T1,T2 always follow the same behaviour, perhaps put them only once?

\medskip
\emph{\textbf{*** not sure} I would just leave it as it is if there is no page limit.
It helps people to see where the jumps in the system function all come from.}
\medskip

\end{document}

### 2016-06-18 ijar-npb-ms.tex
set up answers to reviewers, Frank's suggetions for Reviewer 2 worked into the paper

@@
 and $\uRsys$ at different time points are performed in parallel
-automatically where the CPU has multiple cores and making automatic
+automatically when the CPU has multiple cores and making automatic
 use of the theoretical results in Section \ref{sec:setsofrel} where

### 2016-06-19 answer-to-reviewers.tex
comments reviewer 1 in answer document, rest of comments by Frank worked into manuscript

@@
 \begin{abstract}
-The reviewers' comments reproduced here, with our answers interlaced. Our answers are printed in \emph{italic}.
+The reviewers' comments are reproduced here, with our answers interlaced. Our answers are printed in \emph{italic}.
 \end{abstract}
@@
 \section*{Reviewer 1}
+
+This is a paper on reliability analysis within the framework of imprecise probabilities.
+The authors consider the optimization task required to estimate the bounds of the failure probability wrt an imprecise specification of the prior distributions of the components.
+I see good reasons to use IPs in this field and the contribution is not trivial.
+Moreover the paper is generally well written and easy to follow.
+
+For all these reasons I think the paper should be accepted.
+
+Yet, I see at least two big issues to be addressed before the paper being published.
+
+\medskip
+\textbf{Complexity issues}\\
+The authors derive an analytical expression (corresponding to a polynomial time solution algorithm) for the bounds of the 'signature'.
+
+Unfortunately, the derived formula only holds for particular values of the parameters, while a brute-force approach taking exponential time is required in the worst case.
+
+This is expected as the general task considered by the authors is probably NP-hard (e.g.
+it should be possible to map it somehow to an inference in a credal network, see for instance Maua' et al., JAIR 2014).
+Yet, I miss a deeper discussion about the values of the parameters of the problem for which a brute-force computation of $\tilde{n}$ in Eq.
+10 can be avoided.
+The authors say that this is the case in the 'vast majority' of the time points, but this is a strong claim, which deserves a discussion.
+
+Of course, the discussion in S6.2 and the examples in S7 are doing something in this direction, but this is not enough.
+
+A theoretical or empirical analysis should be necessarily added to convince the reader about the practical applicability of the result.
+An idea might be a non-brute-force, approximate, approach (e.g., some sampling-based inner approximation).
+In the discrete case, such sampling can be drastically improved by sampling only on the extreme distribution (of the convex credal sets).
+This is less straightforward with continuous parameter, but it should be possible to do something even in this case (and I guess some paper by Alessio Benavoli can give direction about that).
+
+\medskip
+\emph{*** empirical analysis by Louis? give computation times for examples?\\
+*** by considering only the parametric Beta distributions, we are already working with the extreme points of the credal set}
+%in this continuous setting, the extreme points of the prior parameter set
+%are the four Beta priors corresponding to combinations of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ with $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$,
+%but the posterior parameter set is not convex
+%
+%most work by Alessio Benavoli concerns near-noninformative sets of priors, while we deal with ***
+\medskip
+
+\textbf{Existing work}\\
+Another point to be addressed by the authors in the final version is the existing work in the field.
+Some pointers about reliability analysis with IPs can be found in many papers by Christophe Simon (within the framework of evidence theory) and Didier Dubois (within the framework of possibilistic theory) as well as in the paper about the imprecise noisy-OR gate by Alessandro Antonucci (withing the framework of credal sets and networks).
+Some words should be also spent about the independence assumptions in the underlying model.
+It is true that the discussion here is very general, but the specific notion of independence might have a strong impact on the corresponding complexity of the inferences.
+Moreover, Gert de Cooman has some papers on the impact of the exchangeability assumption on imprecise probabilistic models.
+The relation with the current model also deserves some comment.
+
+\medskip
+\emph{***}
+\medskip
+
+\textbf{Presentation}\\
+- The core of the paper is (in my opinion) S6 and, more specifically, E10.
+I would give more emphasis to this result and also to LM3 which is crucial as well as TH2 (while TH1 is more a preparatory result.
+In the proofs of both Th 1 and Th 2 some results from [18] and [15] are cited.
+I would better shape them as preparatory lemmas (with no need of explicit proof, but with an explicit statement).
+This would be a chance to explicitly formalize the two notions of dominance considered here.
+I would also remove the first part of the proof of Th 2 by saying that it is totally analogous to that of Th 1.
+
+\medskip
+\emph{***}
+\medskip
+
+- The expression ''in an arbitrarily fine grid of time points'' in the introduction might sound a bit obscure
+
+\medskip
+\emph{***}
+\medskip
+
+- \verb+\overline{x}+ for arrays might be a bit confusive in a IP paper, why not to use \verb+\vec{}+ or \verb+\bm{}+?
+
+\medskip
+\emph{***}
+\medskip
+
+- The term 'natural extension' at page 6 should be clarified
+
+\medskip
+\emph{***}
+\medskip
+
+- Typo in ''$p_t^k$,s can''(page 6)
+
+\medskip
+\emph{***}
+\medskip
+
+- $n^{(n)}$ is weird (page 7)
+
+\medskip
+\emph{***}
+\medskip
+
+- Sec 4, why not to cite that the re-parametrization is based on the re-parametrization a' la Walley for the Dir distribution?
+
+\medskip
+\emph{***}
+\medskip
+
+- I would shape the example at the end of S4 in an example environment
+
+\medskip
+\emph{***}
+\medskip
+
+- I see the issues related to the improper priors in the vacuous case, yet in the discussion of this issue I miss a link with Walley's IDM (or IBM …).
+
+\medskip
+\emph{***}
+\medskip
+
+- Why bold R for the R software?
+
+\medskip
+\emph{***}
+\medskip
 
@@
 \medskip
-\emph{We think the reviewer does not fully acknowledge the central benefit of the survival signature, which is present also for independent components: Information on the system layout (which does not change over time) is fully separated from (time-dependent) component failure probabilities.}
+\emph{We think that here the reviewer does not fully acknowledge the central benefit of the survival signature,
+which is present also for independent components:
+%Information on the system layout (which does not change over time) is fully separated from (time-dependent) component failure probabilities.}
+It allows straightforward and efficient computation of the system survival by separating the (time-invariant) system structure from the time-dependent failure probabilities of components.}
 \medskip
@@
 
+\medskip
+\emph{The sequence of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ may seem indeed similar to a p-box.
+However, we do not model prior knowledge about the reliability function of component type $k$
+as the set of reliability functions bounded by $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$.
+Instead, we assume a set of Beta priors at each time point $t_j$ with means bounded by $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$
+and prior strengths bounded by $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$.
+This set of Beta priors for each $t_j$ can well be seen as a parametric p-box.
+The parametric choice has the advantage that observed component lifetime data can be taken into account via the Generalized Bayes Rule update,
+and that posterior predictive probabilities $P(C^k_t = l_k \mid \yktz, \nktz, s^k_t)$ needed for computation of system survival
+are easily obtained as Beta-Binomial probabilities.
+One could indeed use any p-box in place of our set of Beta priors,
+but we doubt that it would be nearly as tractable as our approach.
+}
+\medskip
+
 * P19, L56: where $\to$ when
@@
 \emph{\textbf{*** not sure} I would just leave it as it is if there is no page limit.
-It helps people to see where the jumps in the system function all come from.}
+It helps people to see where the jumps in the system function all come from, without having to switch between figures.}
 \medskip

### 2016-06-19 ijar-npb-ms.tex
comments reviewer 1 in answer document, rest of comments by Frank worked into manuscript

@@
 % which should be of concern at the system level.
+
+*** add references to existing work on reliability with IP, including \cite{UC07} here or in par above?***
 
@@
 Alternatively, one can assume exchangeability with other surviving components at the moment of censoring.
-This approach will be more complex to accomodate but will lead to less imprecision.
+This approach will be more complex to accommodate but will lead to less imprecision.
 Indeed, this assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
@@
 reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
-For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
+For example, one may generalize the system structure function from a binary function to a probability \citep[see][]{CCM16},
 to reflect uncertainty about system functioning for known states of its components, with a further
@@
 \section*{Acknowledgements}
+
+The authors are grateful for support of their work from two anonymous reviewers and for their comments which led to improved presentation.
 

### 2016-06-28 ijar-npb-ms.tex
literature suggestions by reviewer 1

@@
 
-*** add references to existing work on reliability with IP, including \cite{UC07} here or in par above?***
-
 Furthermore, the method is based on the survival signature \cite{2012:survsign},
@@
 %\td{*** Some more words on the benefits?}
+
+In contrast to previous work on reliability with IP, our focus is on learning component reliabilities***
+
+*** add references to existing work on reliability with IP, including \cite{UC07} here ***
+
+\cite{2011:antonucci::noisyor}
 
@@
 and similarly maximising for $\uRsys(\cdot)$.
+In doing so, we assume components of the same type $k$ to be exchangeable given $\PtZi{k}$
+\citep[see][\S 3.4 on extending exchangeability to imprecise probability]{itip},
+and components of different types to follow \emph{strong independence}
+\citep[see][\S 3.2.4]{itip}.
 

### 2016-06-29 ijar-npb-ms.tex
addressing reviewer 1 on existing work

@@
 
-While the use of imprecise probability methods can often lead to tractability issues,
+%While the use of imprecise probability methods can often lead to tractability issues,
+%new results on first-order stochastic dominance for the Beta-Binomial distribution
+%keep the need for numerical optimization in our model to a minimum.
+
+Our approach extends the literature on reliability with imprecise probability
+\citep[for an overview see][]{UC07}
+by integrating the learning of component reliabilities based on test data,
+in combination with the use of the survival signature.
+Approaches to system reliability based on generalizations of Bayesian networks
+like evidential networks \citep{2008:simon-weber-evsukoff}
+and credal networks \cite{2011:antonucci::noisyor}
+do usually not include test data in the model.
+Doing so is certainly possible in these frameworks, 
+but this would add further to the complexity of the Bayesian network representation,
+in which updating (i.e., calculating posterior reliabilities) for each time $t$
+is generally NP-hard \cite{2014:maua-decampos-benavoli-antonucci}.
+While determining the survival signature is also NP-hard,
+this has to be done only once in our approach.
+Furthermore,
 new results on first-order stochastic dominance for the Beta-Binomial distribution
 keep the need for numerical optimization in our model to a minimum.
-%make the technique computationally tractable.
-%As will be seen in the sequel, the method remains computationally tractable.
-%\td{*** Some more words on the benefits?}
-
-In contrast to previous work on reliability with IP, our focus is on learning component reliabilities***
-
-*** add references to existing work on reliability with IP, including \cite{UC07} here ***
-
-\cite{2011:antonucci::noisyor}
 

### 2016-06-30 answer-to-reviewers.tex
literature suggestions by reviewer 1
addressing reviewer 1 on existing work
addressing reviewer 1 cont.

@@
 \medskip
-\emph{***}
+\emph{We now refer to existing work in the introduction section and clarify the contribution of our work.
+In Section~6, we now also state clearly the assumptions regarding independence and exchangeability
+underlying our imprecise probability model.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{We do not see Theorem~1 as preparatory result, but as equally essential as Theorem~2 and Lemma~3
+for ensuring the tractability of our approach.
+We also do not feel that writing out the definitions of first-order stochastic dominance and likelihood ratio order is necessary,
+as the former is a standard notion, and the latter is made explicit within the proof of Theorem~1.
+We thus prefer to leave presentation here as it is.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{We wanted to express here that there are no restrictions on time grid density,
+and do not see the need to phrase this otherwise.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{We changed the notation in Section~2 to use $\vec{x}$ in place of $\underline{x}$ for state vectors.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{To avoid confusion with the notion of `natural extension' from imprecise probability literature,
+we changed the wording to `simple extension' here.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{We now write `The sequence of $\ptk$'s can, in theory, be directly chosen \ldots' to emphasize the plural here.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{Agreed, but we wish to be consistent with previous literature on sets of conjugate priors and so prefer to keep this notation.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{***Walley uses this parametrization for the IDM / IBM, but it has been known before that as natural or canonical parametrization, ***}
 \medskip
@@
 
-- I see the issues related to the improper priors in the vacuous case, yet in the discussion of this issue I miss a link with Walley's IDM (or IBM …).
+- I see the issues related to the improper priors in the vacuous case, yet in the discussion of this issue I miss a link with Walley's IDM (or IBM \ldots).
 

### 2016-06-30 ijar-npb-ms.tex
addressing reviewer 1 cont.

@@
 \emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
-$\underline{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
-and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\underline{x}$. 
-The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\underline{x}$, takes 
-the value 1 if the system functions and 0 if the system does not function for state vector $\underline{x}$. 
-Most practical systems are coherent, which means that $\phi(\underline{x})$ 
-is non-decreasing in any of the components of $\underline{x}$, so system functioning cannot be improved by worse performance 
+$\vec{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
+and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\vec{x}$. 
+The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
+the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$. 
+Most practical systems are coherent, which means that $\phi(\vec{x})$ 
+is non-decreasing in any of the components of $\vec{x}$, so system functioning cannot be improved by worse performance 
 of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
-quantification for system reliability. It is further logical to assume that $\phi(\underline{0})=0$ and $\phi(\underline{1})=1$, 
+quantification for system reliability. It is further logical to assume that $\phi(\vec{0})=0$ and $\phi(\vec{1})=1$, 
 so the system fails if all its components fail and it functions if all its components function.
@@
 leading to a state vector that can be written as 
-$\underline{x} = (\underline{x}^1,\underline{x}^2,\ldots,\underline{x}^K)$, with 
-$\underline{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.
+$\vec{x} = (\vec{x}^1,\vec{x}^2,\ldots,\vec{x}^K)$, with 
+$\vec{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.
 
@@
 For calculating the survival signature based on the structure function, observe that
-there are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
+there are $\binom{m_k}{l_k}$ state vectors $\vec{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
 denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
@@
 exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
-$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
+$\vec{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
 \begin{align}
@@
 \Phi(l_1,\ldots,l_K)
- &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
+ &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\vec{x} \in S_{l_1,\ldots,l_K}} \phi(\vec{x})\,.
 \end{align}
@@
 The time grid $\cal T$ can be chosen to be appropriately dense for the application at hand,
-with the natural extension between grid points by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
+where a simple extension between grid points can be made by taking $R^k(\cdot)$ to be the right continuous step function induced by the grid values,
 $R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
@@
 
-The $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
+The sequence of $\ptk$'s can, in theory, be directly chosen to arbitrarily closely approximate any valid lifetime pdf on
 $[0,\infty)$, for example matching a bathtub curve for the corresponding hazard rate $h^k(t_j)$.

### 2016-07-01 answer-to-reviewers.tex
all reviewers' remarks addressed except the computational complexity remark

@@
 \medskip
-\emph{*** empirical analysis by Louis? give computation times for examples?\\
-*** by considering only the parametric Beta distributions, we are already working with the extreme points of the credal set}
+\emph{***We have added some first considerations on the question of how often we have to resort to numerical optimization in Appendix~C,
+and now also give computation times for our examples in Section~7.2.}\\
+
+\emph{***On the last note, by considering only the parametric Beta distributions,
+we are already working with the extreme points of the credal sets induced by $\PktZ$.}
 %in this continuous setting, the extreme points of the prior parameter set
@@
 \medskip
-\emph{We changed the notation in Section~2 to use $\vec{x}$ in place of $\underline{x}$ for state vectors.}
+\emph{Agreed, we changed the notation in Section~2 to use $\vec{x}$ in place of $\underline{x}$ for state vectors.}
 \medskip
@@
 \medskip
-\emph{***Walley uses this parametrization for the IDM / IBM, but it has been known before that as natural or canonical parametrization, ***}
+\emph{Agreed. This parametrization for conjugate priors in exponential families has been known for a long time
+(see, e.g., Diaconis \& Ylvisaker 1979),
+but Walley (1991, \S 5.3) showed its usefulness for the imprecise Beta model, and then for the IDM.
+}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{As we have our main examples in Section~7 in a separate subsection,
+putting the example at the end of Section~4 would be awkward as
+it would remain be the sole example in an example environment.}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{Agreed, we now refer to the literature on near-noninformative sets of priors (second-to-last paragraph of Section~5).}
 \medskip
@@
 \medskip
-\emph{***}
+\emph{Agreed, we now use} \verb+\textsf{R}+ \emph{which seems to be the standard.}
 \medskip
@@
 \medskip
-\emph{We added a paragraph at the end of Section 2 to address this point.}
+\emph{We added a paragraph at the end of Section~2 to address this point.}
 \medskip
@@
 are easily obtained as Beta-Binomial probabilities.
-One could indeed use any p-box in place of our set of Beta priors,
-but we doubt that it would be nearly as tractable as our approach.
-}
+One could indeed use any p-box in place of our set of Beta priors for each $t_j$,
+but we doubt that it would be nearly as tractable as our approach.}
 \medskip
@@
 \medskip
-\emph{\textbf{*** not sure} I would just leave it as it is if there is no page limit.
-It helps people to see where the jumps in the system function all come from, without having to switch between figures.}
+\emph{We decided to leave the figures as they are, to allow them to be interpreted on their own,
+without the need to switch between different figures.
+Specifically, each complete figure allows to relate any jump in the system reliability function bounds
+to the corresponding jump in either of the component reliability function bounds.}
 \medskip

### 2016-07-01 ijar-npb-ms.tex
all reviewers' remarks addressed except the computational complexity remark

@@
 hypothetical numbers of functioning and failed components of type $k$ at time $t$, respectively.
-However, when we generalise to sets of priors in the sequel,
+However, as recognized by \citep[\S 5.3]{1991:walley}, when we generalise to sets of priors in the sequel,
 it is useful to consider a different parametrisation.
@@
 for some or all $t \in {\cal T}$.
+Such models are called \emph{near-noninformative} or \emph{near-ignorance models} in the imprecise probability literature
+(see \citet[\S5.3.2]{1991:walley} for Beta priors,
+and \citet{2012:benavolizaffalon,2015:benavolizaffalon} for exponential family priors),
+as they provide vacuous bounds only for a certain class of inferences,
+and the choice for the prior strength parameter $\nktz$ influences posterior inferences.
 (Note that it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
@@
 in the denominator of \eqref{eq:postpredCny} being zero.)
-These limits for $\yktz$ imply we are only prepared to give trivial bounds for the functioning probability
+The limits $\yktzl \to 0$ and $\yktzu \to 1$ imply we are only prepared to give trivial bounds for the functioning probability
 and do not wish to commit to any specific knowledge about $p^k_t$ \emph{a priori}.
@@
 \label{sec:examples}
-%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},
 
@@
 
-The methods of this paper have been implemented in the \textbf{R}
+The methods of this paper have been implemented in the \textsf{R}
 \citep{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT},
@@
 
-Gero Walter was supported by the DINALOG project
-``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).
+Gero Walter was supported by the DINALOG project CAMPI
+(``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'').
 
@@
 Functions which make it easy to use the methods of this paper
-have been added to the \textbf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
+have been added to the \textsf{R} package \texttt{ReliabilityTheory} \citep{2015:aslett-RT}.
 There are two functions of particular note: \texttt{computeSystemSurvivalSignature}

### 2016-07-01 answer-to-reviewers.tex
thanks to reviewers in answer plus minor tweaks

@@
 \begin{abstract}
-The reviewers' comments are reproduced here, with our answers interlaced. Our answers are printed in \emph{italic}.
+We would like to thank the two anonymous reviewers for their positive and constructive feedback,
+which has helped us to improve presentation in a number of crucial points, and hope that with these changes,
+the manuscript can be considered for publication.
+
+The reviewers' comments are reproduced below, with our answers interlaced. Our answers are printed in \emph{italic}.
 \end{abstract}
@@
 Specifically, each complete figure allows to relate any jump in the system reliability function bounds
-to the corresponding jump in either of the component reliability function bounds.}
+to the corresponding jump in either of the three component reliability function bounds.}
 \medskip

### 2016-07-03 answer-to-reviewers.tex
Added 3 pages of appendix on how often the theory helps. Added a few sentences in main body of paper on the same. Updated answer to reviewers on the computational aspect. New R file which generates the plots for Appendix B.

@@
 \medskip
-\emph{***We have added some first considerations on the question of how often we have to resort to numerical optimization in Appendix~C,
-and now also give computation times for our examples in Section~7.2.}\\
+\emph{We have added just under 3 pages of analysis with detailed graphical plots on the question of how often one has to resort to numerical optimisation in Appendix~B in a manner that should be useful in illuminating the practical applicability of the method for readers interested in applying it.
+We also reran the automotive brake example and measured precisely how often the theory helps for the automotive brake example in Section~7.2.2 adding a short comment in place and more detail in the same Appendix.}\\
 

### 2016-07-03 ijar-npb-ms.tex
Added 3 pages of appendix on how often the theory helps. Added a few sentences in main body of paper on the same. Updated answer to reviewers on the computational aspect. New R file which generates the plots for Appendix B.

@@
 
+Appendix \ref{ap:needtoopt} provides a detailed discussion of exactly how often these bounds hold and how often one must resort to numerical optimisation.
+
 Thus,
@@
 \subsubsection{Automotive brake system}
+\label{sec:brakeex}
 
@@
 be relevant when propagated to the uncertainty in the whole system.
+
+In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
+Further detail is in Appendix \ref{ap:needtoopt}.
 
@@
 
+\section{Theory versus optimisation}
+\label{ap:needtoopt}
+
+The above theory substantially reduces the amount that numerical optimisation must be used.
+Herein, we examine more carefully precisely how often the theory cannot be applied resulting in numerical optimisation being used.
+
+Given some unknown failure probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
+\begin{align*}
+  &P(y(N+m-1)-m+1 < s < y(N+m-1)) \\
+  &\qquad \qquad \qquad \qquad = \sum_{i = \lceil y(N+m-1)-m+1 \rceil}^{\lfloor y(N+m-1) \rfloor} \binom{N}{i} p^i (1-p)^{N-i}
+\end{align*}
+Likewise the probability that Lemma 3 does not apply is
+\begin{align*}
+  &P(\mathcal{L}_{\nu,\nl}(0) \lesseqgtr 1 \cap \mathcal{L}_{\nu,\nl}(m) \gtreqless 1) = \sum_{s \in \mathcal{S}} \binom{N}{s} p^s (1-p)^{N-s} \\
+  &\qquad\mbox{where}\quad \mathcal{S} = \left\{ s : \frac{p(0 \mid y, \nu, m, s, N)}{p(0 \mid y, \nl, m, s, N)} \lesseqgtr 1 \cap \frac{p(m \mid y, \nu, m, s, N)}{p(m \mid y, \nl, m, s, N)} \gtreqless 1 \right\}
+\end{align*}
+
+\subsection{Some example scenarios}
+
+With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown failure probability $p$, which gives rise under repeated experiments to an observed number of failures, $s$.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{need-to-opt-1}
+\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown failure probability, $p$.}
+\label{fig:need-to-opt-1}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{need-to-opt-2}
+\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown failure probability, $p$.}
+\label{fig:need-to-opt-2}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\textwidth]{need-to-opt-3}
+\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of component in the system, $m$, as a function of the unknown failure probability, $p$.}
+\label{fig:need-to-opt-3}
+\end{figure}
+
+Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show under long term repeated use of this technique how often optimisation would be required.
+
+The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of failure, $p$.
+Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of the same component in a system (increasing $m$).
+Not shown is that $\nl$ and $\nu$ clearly do not affect the probability that Theorem 2 does not apply, but also the impact on Lemma 3 is negligible.
+
+\subsection{Worst case scenario}
+
+Clearly the true failure probability, $p$, is unknown.
+Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{need-to-opt-4}\includegraphics[width=0.5\textwidth]{need-to-opt-5}
+\caption{Plots of the worst case probability that numerical optimisation is required for different choices of $y$, when $m=3$ (left), $N=100$ (right), $\nl=1$ and $\nu=5$.
+There are some artefacts due to the underlying discrete Binomial probabilities.}
+\label{fig:need-to-opt-45}
+\end{figure}
+
+Especially given the upper and lower choices of $y$, it may be reasonable to suppose that it is unlikely that the prior probability will all that often exactly equal the true failure probability (at least not for long stretches of time).
+Therefore, a final pair of plots replicates the analysis in Figure \ref{fig:need-to-opt-45}, but where the worst case $p$ is subject to the constraint $|y-p|>0.1$.
+This is shown in Figure \ref{fig:need-to-opt-67}
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{need-to-opt-6}\includegraphics[width=0.5\textwidth]{need-to-opt-7}
+\caption{Plots of the worst case probability that numerical optimisation is required for different choices of $y$, when $m=3$ (left), $N=100$ (right), $\nl=1$ and $\nu=5$, subject to the constraint $|y-p|>0.1$.
+There are some artefacts due to the underlying discrete Binomial probabilities.}
+\label{fig:need-to-opt-67}
+\end{figure}
+
+Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ computed.
+Of relevance to the overall compute time is the behaviour over time, so that is seems unlikely the worst case scenario will be occur for long runs of the times under analysis.
+
+\subsection{Theoretical analysis for brake system example}
+
+By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section \ref{sec:brakeex}.
+
+Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.
+Note in particular that when $m=1$, Lemma 3 is always applies and optimisation is never required.
+This is true for all values of $N$ and $y$.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{need-to-opt-8}
+\caption{Plots of the worst case probability that numerical optimisation is required over time in the brake example, subject to the constraint $|y-p|>0.1$.}
+\label{fig:need-to-opt-8}
+\end{figure}
+
+As explained in section \ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of component, meaning a stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.
+In total, theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$, while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.
+
 \section{Software details}

### 2016-07-03 need-to-opt.R

@@ -1,0 +1,328 @@
+library(ggplot2)
+
+p <- seq(0, 1, length.out = 100)
+
+prob.s <- function(y, p, N, m) {
+  if(p<0)
+    return(NA)
+  if(p>1)
+    return(NA)
+  pbinom(floor(y*(N+m-1)), N, p) - pbinom(ceiling(y*(N+m-1)-m+1) - 1, N, p)
+}
+prob <- Vectorize(prob.s, "p")
+
+prob2.s <- function(y, p, N, m, n.u, n.l) {
+  if(p<0)
+    return(NA)
+  if(p>1)
+    return(NA)
+
+  s.bad <- NULL
+  for(s in 0:N) {
+    L0 <- (prod(0:(m-1)+n.u*(1-y)+N-s)*prod(0:(m-1)+n.l+N)) /
+      (prod(0:(m-1)+n.l*(1-y)+N-s)*prod(0:(m-1)+n.u+N))
+    Lm <- (prod(0:(m-1)+n.u*y+s)*prod(0:(m-1)+n.l+N)) /
+      (prod(0:(m-1)+n.l*y+s)*prod(0:(m-1)+n.u+N))
+    if(is.nan(Lm) || is.nan(L0) || (!(L0<=1 && Lm>=1) && !(L0>=1 && Lm<=1))) {
+      s.bad <- c(s.bad, s)
+    }
+  }
+  if(length(s.bad)==0)
+    return(0)
+  sum(dbinom(s.bad, N, p))
+}
+prob2 <- Vectorize(prob2.s, "p")
+
+# Plot 1
+y <- 0.1; N <- 100; m <- 3; n.l <- 1; n.u <- 5
+
+y <- 0.1
+d1 <- data.frame(p=rep(p, 2),
+                 popt=c(prob(y, p, N, m), prob2(y, p, N, m, n.u, n.l)),
+                 lab=rep(c("Theorem 2", "Lemma 3"), each=length(p)),
+                 y=y)
+y <- 0.25
+d2 <- data.frame(p=rep(p, 2),
+                 popt=c(prob(y, p, N, m), prob2(y, p, N, m, n.u, n.l)),
+                 lab=rep(c("Theorem 2", "Lemma 3"), each=length(p)),
+                 y=y)
+y <- 0.5
+d3 <- data.frame(p=rep(p, 2),
+                 popt=c(prob(y, p, N, m), prob2(y, p, N, m, n.u, n.l)),
[…]

### 2016-07-03 need-to-opt.R
Missing dplyr dependency for script file to run without error.

@@ -317,6 +317,7 @@ ggplot() +
   geom_line(data=P, aes(x=t, y=popt, lty=lab))
 dev.off()
 
+library(dplyr)
 mean(c(mean(t(M %>% filter(lab=="Lower") %>% select(popt))),
        mean(t(H %>% filter(lab=="Lower") %>% select(popt))),
        mean(t(C %>% filter(lab=="Lower") %>% select(popt))),

### 2016-07-03 need-to-opt-testfn.R
Modified ReliabilityTheory function which measures number of optimisations.

@@ -1,0 +1,288 @@
+test <- function (at.times, survival.signature, test.data, nLower = 2,
+                  nUpper = 2, yLower = 0.5, yUpper = 0.5)
+{
+  OPTl <- OPTu <- 0
+  THYl <- THYu <- 0
+  K <- ncol(survival.signature) - 1
+  if (any(at.times < 0)) {
+    stop("all at.times must be non-negative")
+  }
+  if (!any(prob.col <- (names(survival.signature) == "Probability"))) {
+    stop("survival signature must contain a variable named 'Probability'")
+  }
+  if (!is.list(test.data) || length(test.data) != K) {
+    stop("test.data must be a named list containing the same number of components as specified by the survival signature")
+  }
+  if (!all(sort(names(test.data)) == sort(names(survival.signature)[!prob.col]))) {
+    stop("component names in survival.signature and test.data must match exactly")
+  }
+  if (is.vector(nLower) && is.vector(nUpper) && is.vector(yLower) &&
+      is.vector(yUpper)) {
+    if (!all.equal(length(nLower), length(nUpper), length(yLower),
+                   length(yUpper))) {
+      stop("nLower, nUpper, yLower and yUpper prior parameter vectors must be the same length")
+    }
+    if (length(nLower) != 1 && length(nLower) != length(at.times)) {
+      stop("prior parameter vectors, nLower, nUpper, yLower and yUpper, must be either length 1 (for time homogeneous prior) or of the same length as at.times argument (where the prior parameters at time at.times[i] are now nLower[i], nUpper[i], yLower[i] and yUpper[i])")
+    }
+    nLower <- as.data.frame(matrix(rep(nLower, K), nrow = length(at.times),
+                                   ncol = K, byrow = FALSE))
+    names(nLower) <- names(survival.signature[!prob.col])
+    nUpper <- as.data.frame(matrix(rep(nUpper, K), nrow = length(at.times),
+                                   ncol = K, byrow = FALSE))
+    names(nUpper) <- names(survival.signature[!prob.col])
+    yLower <- as.data.frame(matrix(rep(yLower, K), nrow = length(at.times),
+                                   ncol = K, byrow = FALSE))
+    names(yLower) <- names(survival.signature[!prob.col])
+    yUpper <- as.data.frame(matrix(rep(yUpper, K), nrow = length(at.times),
+                                   ncol = K, byrow = FALSE))
[…]

### 2016-07-04 ijar-npb-ms.tex
some minor tweaks in Louis' additions

@@
 the number of different components).
-
+%
 Appendix \ref{ap:needtoopt} provides a detailed discussion of exactly how often these bounds hold and how often one must resort to numerical optimisation.
 
-Thus,
+Thus, due to Theorems~\ref{thm:y}, \ref{thm:n} and Lemma~\ref{lem:n}, \eqref{eq:LwrSysPostA} transforms to
 %For $\lRsys(\cdot)$, the minimum is achieved at
@@
 where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
-We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
+We consider $301$ evenly spaced time points $t$ on $[0, 10]$,
+assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
 and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
@@
 the prior upper system reliability bound for $t \le 5$ is close to one, too,
-since the system can function on H and one of P1 -- P4 alone.
+since the system can function on H and one of P3 and P4 alone.
 Note that the posterior functioning probability interval for M
@@
 
-In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
+In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
+for 91.9\% and 95.7\% of the $301$ considered time points for $\lRsys(\cdot)$ and $\uRsys(\cdot)$, respectively.
 Further detail is in Appendix \ref{ap:needtoopt}.
@@
 
-Given some unknown failure probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
+Given some unknown functioning probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
 \begin{align*}
@@
 \includegraphics[width=\textwidth]{need-to-opt-3}
-\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of component in the system, $m$, as a function of the unknown failure probability, $p$.}
+\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of components in the system, $m$, as a function of the unknown failure probability, $p$.}
 \label{fig:need-to-opt-3}
@@
 The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of failure, $p$.
-Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of the same component in a system (increasing $m$).
+Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of components of the same type in a system (increasing $m$).
 Not shown is that $\nl$ and $\nu$ clearly do not affect the probability that Theorem 2 does not apply, but also the impact on Lemma 3 is negligible.
@@
 
-Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ computed.
-Of relevance to the overall compute time is the behaviour over time, so that is seems unlikely the worst case scenario will be occur for long runs of the times under analysis.
+Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ is computed.
+Of relevance to the overall compute time is the behaviour over time, so that seems unlikely that the worst case scenario will occur for long runs of the times under analysis.
 
@@
 Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.
-Note in particular that when $m=1$, Lemma 3 is always applies and optimisation is never required.
+Note in particular that when $m=1$, Lemma 3 *** always applies and optimisation is never required.
 This is true for all values of $N$ and $y$.

### 2016-07-04 ijar-npb-ms.tex
Fit failure -> functioning probability.

@@
 
-With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown failure probability $p$, which gives rise under repeated experiments to an observed number of failures, $s$.
+With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown functioning probability $p$, which gives rise under repeated experiments to an observed number of functioning components, $s$.
 
@@
 \includegraphics[width=\textwidth]{need-to-opt-1}
-\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown failure probability, $p$.}
+\caption{Plots of the probability that numerical optimisation is required when $N=100$, $m=3$, $\nl=1$ and $\nu=5$ for changing choices of prior, $y$, as a function of the unknown functioning probability, $p$.}
 \label{fig:need-to-opt-1}
@@
 \includegraphics[width=\textwidth]{need-to-opt-2}
-\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown failure probability, $p$.}
+\caption{Plots of the probability that numerical optimisation is required when $y=0.1$, $m=3$, $\nl=1$ and $\nu=5$ for changing amounts of test data, $N$, as a function of the unknown functioning probability, $p$.}
 \label{fig:need-to-opt-2}
@@
 \includegraphics[width=\textwidth]{need-to-opt-3}
-\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of components in the system, $m$, as a function of the unknown failure probability, $p$.}
+\caption{Plots of the probability that numerical optimisation is required when $y=0.4$, $N=100$, $\nl=1$ and $\nu=5$ for differing numbers of components in the system, $m$, as a function of the unknown functioning probability, $p$.}
 \label{fig:need-to-opt-3}
@@
 
-The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of failure, $p$.
+The worst case scenario is that the prior, $y$, is exactly equal to the true unknown probability of functioning, $p$.
 Regardless of $y$, optimisation is required less frequently with larger test dataset sizes (increasing $N$), but offset by increasing numbers of components of the same type in a system (increasing $m$).
@@
 
-Clearly the true failure probability, $p$, is unknown.
+Clearly the true functioning probability, $p$, is unknown.
 Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.

### 2016-07-04 ijar-npb-ms.tex
Lemma 3 statement sharpened.
revert to 'cases' at end of sec 7.2.2

@@
 In this example, the theory presented in Section \ref{sec:setsofrel} enabled avoiding numerical optimisation
-for 91.9\% and 95.7\% of the $301$ considered time points for $\lRsys(\cdot)$ and $\uRsys(\cdot)$, respectively.
+in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
 Further detail is in Appendix \ref{ap:needtoopt}.
@@
 Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.
-Note in particular that when $m=1$, Lemma 3 *** always applies and optimisation is never required.
+Note in particular that when $m=1$, Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.
 This is true for all values of $N$ and $y$.

### 2016-07-05 answer-to-reviewers.tex
different colours for figures B.12 and B.13, rewriting appendix B.3, and minor tweaks

@@
 \emph{We have added just under 3 pages of analysis with detailed graphical plots on the question of how often one has to resort to numerical optimisation in Appendix~B in a manner that should be useful in illuminating the practical applicability of the method for readers interested in applying it.
-We also reran the automotive brake example and measured precisely how often the theory helps for the automotive brake example in Section~7.2.2 adding a short comment in place and more detail in the same Appendix.}\\
+We also reran the automotive brake example and measured precisely how often the theory helps for the automotive brake example in Section~7.2.2, adding a short comment in place and more detail in the same Appendix.}
 
-\emph{***On the last note, by considering only the parametric Beta distributions,
-we are already working with the extreme points of the credal sets induced by $\PktZ$.}
-%in this continuous setting, the extreme points of the prior parameter set
-%are the four Beta priors corresponding to combinations of $\yzl_{k,t_j}$ and $\yzu_{k,t_j}$ with $\nzl_{k,t_j}$ and $\nzu_{k,t_j}$,
-%but the posterior parameter set is not convex
-%
-%most work by Alessio Benavoli concerns near-noninformative sets of priors, while we deal with ***
 \medskip
@@
 \emph{As we have our main examples in Section~7 in a separate subsection,
-putting the example at the end of Section~4 would be awkward as
-it would remain be the sole example in an example environment.}
+putting the example at the end of Section~4 in an example environment would be awkward as
+it would remain the sole example formatted in that way.}
 \medskip

### 2016-07-05 ijar-npb-ms.tex
different colours for figures B.12 and B.13, rewriting appendix B.3, and minor tweaks

@@
 \cite{2015:bayessurvsign}.  Section \ref{sec:reparam} details
-the reparameterisation of that approach which enables the natural
+the reparametrisation of that approach which enables the natural
 formulation of the system reliability bounds, leading to
@@
 in 91.9\% of cases for $\lRsys(\cdot)$ and in 95.7\% of cases for $\uRsys(\cdot)$.
-Further detail is in Appendix \ref{ap:needtoopt}.
+Further detail is in Appendix \ref{ap:needtoopt-brake}.
 
@@
 
-Given some unknown functioning probability $p$, which gives rise to the observed data $s$, the probability that Theorem 1 does not apply is
+Given some unknown functioning probability $p$, which gives rise to the observed data $s$, the probability that Theorem~2 does not apply is
 \begin{align*}
@@
 \end{align*}
-Likewise the probability that Lemma 3 does not apply is
+Likewise the probability that Lemma~3 does not apply is
 \begin{align*}
@@
 Note that all these analyses are for evaluation of a single fixed time point at which $\lRsys(\cdot)$ or $\uRsys(\cdot)$ is computed.
-Of relevance to the overall compute time is the behaviour over time, so that seems unlikely that the worst case scenario will occur for long runs of the times under analysis.
+Of relevance to the overall compute time is the behaviour over time, and it seems unlikely that the worst case scenario will occur for long runs of the times under analysis.
 
 \subsection{Theoretical analysis for brake system example}
-
-By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section \ref{sec:brakeex}.
-
-Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.
+\label{ap:needtoopt-brake}
+
+By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section~\ref{sec:brakeex}.
+%
+%Figure \ref{fig:need-to-opt-8} shows the changing worst case probability (subject to $|y-p|>0.1$) that optimisation will be required over time for the actual choice of prior and the values of $m, N, \nu$ and $\nl$ in the brake example from the main body of the paper.
 Note in particular that when $m=1$, Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.
+This is true for all values of $N$ and $y$.
+As noted in Section~\ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of components,
+meaning stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.
+
+Figure~\ref{fig:need-to-opt-8} shows the worst case probabilities (subject to $|y-p|>0.1$)
+as they change over time in the brake example from the main body of the paper.
+Displayed are the worst case probabilities that optimisation will be required for the choice of prior and the values of $m$ and $N$
+as in Section~\ref{sec:brakeex}, but without using the test data (which define $s$).
+Note in particular that when $m=1$ (as is the case for component types M and H),
+Lemma 3 always applies for $y \in (0,1)$ and so optimisation is never required.
 This is true for all values of $N$ and $y$.
@@
 
-As explained in section \ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of component, meaning a stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.
-In total, theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$, while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.
+For the test data as used in Section~\ref{sec:brakeex},
+theory could not determine stochastic dominance in 98 (or 8.1\%) of cases for $\lRsys(\cdot)$,
+while it was in 52 (or 4.3\%) of cases for $\uRsys(\cdot)$.
 

### 2016-07-05 need-to-opt.R

@@ -2,6 +2,7 @@ library(ggplot2)
 
 p <- seq(0, 1, length.out = 100)
 
+# probaliity that theorem 2 does not apply
 prob.s <- function(y, p, N, m) {
   if(p<0)
     return(NA)
@@ -11,6 +12,7 @@ prob.s <- function(y, p, N, m) {
 }
 prob <- Vectorize(prob.s, "p")
 
+# probability that lemma 3 does not apply
 prob2.s <- function(y, p, N, m, n.u, n.l) {
   if(p<0)
     return(NA)
@@ -118,8 +120,8 @@ ggplot(rbind(d1, d2, d3)) +
 dev.off()
 
 # Extra function defs
-prob.p <- Vectorize(prob.s, c("y","p"))
-prob2.p <- Vectorize(prob2.s, c("y", "p"))
+prob.p <- Vectorize(prob.s, c("y","p")) # Theorem 2
+prob2.p <- Vectorize(prob2.s, c("y", "p")) # Lemma 3
 
 # Plot 4
 y <- seq(0, 1, length.out = 51)
@@ -129,27 +131,26 @@ N <- 100; m <- 3; n.l <- 1; n.u <- 5
 N <- 50
 d1 <- data.frame(p=rep(y, 2),
                  popt=c(prob.p(y, y, N, m), prob2.p(y, y, N, m, n.u, n.l)),
-                 lab=rep(c("Theorem 2", "Lemma 3"), each=length(y)),
+                 lab=factor(rep(c("Theorem 2", "Lemma 3"), each=length(y)), levels=c("Theorem 2", "Lemma 3")),
                  N="10")
 N <- 100
 d2 <- data.frame(p=rep(y, 2),
                  popt=c(prob.p(y, y, N, m), prob2.p(y, y, N, m, n.u, n.l)),
-                 lab=rep(c("Theorem 2", "Lemma 3"), each=length(y)),
+                 lab=factor(rep(c("Theorem 2", "Lemma 3"), each=length(y)), levels=c("Theorem 2", "Lemma 3")),
                  N="100")
 N <- 1000
 d3 <- data.frame(p=rep(y, 2),
                  popt=c(prob.p(y, y, N, m), prob2.p(y, y, N, m, n.u, n.l)),
-                 lab=rep(c("Theorem 2", "Lemma 3"), each=length(y)),
[…]

### 2016-07-05 ijar-npb-ms.tex
final tweaks

@@
 (see \citet[\S5.3.2]{1991:walley} for Beta priors,
+\cite{1996:walley::IDM} for Dirichlet priors,
 and \citet{2012:benavolizaffalon,2015:benavolizaffalon} for exponential family priors),

### 2016-07-05 ijar-npb-ms.tex
final tweaks

@@
 
-Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show under long term repeated use of this technique how often optimisation would be required.
+Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show how often optimisation would be required
+under long term repeated use of this technique.
 

### 2016-07-05 ijar-npb-ms.tex
getting figures B.9, B.10 and B.11 on one page again

@@
 
-\subsection{Some example scenarios}
-
-With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown functioning probability $p$, which gives rise under repeated experiments to an observed number of functioning components, $s$.
-
 \begin{figure}
@@
 
+\subsection{Some example scenarios}
+
+With the prior value $y$ (upper or lower) fixed, the above expressions depend only on the unknown functioning probability $p$, which gives rise under repeated experiments to an observed number of functioning components, $s$.
+
 Thus, Figures \ref{fig:need-to-opt-1}, \ref{fig:need-to-opt-2} and \ref{fig:need-to-opt-3} show how often optimisation would be required
@@
 Clearly the true functioning probability, $p$, is unknown.
-Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.
+Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for any choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.
 

### 2016-07-05 ijar-npb-ms.tex
more final tweaks

@@
 The above theory substantially reduces the amount that numerical optimisation must be used.
-Herein, we examine more carefully precisely how often the theory cannot be applied resulting in numerical optimisation being used.
+Herein, we examine more carefully precisely how often the theory cannot be applied, resulting in numerical optimisation being used.
 
@@
 
-By way of example, a temporal analysis of the constrained worst case analysis is now presented for the real example in Section~\ref{sec:brakeex}.
+Such temporal aspects are now considered by analysing the brake system example from Section~\ref{sec:brakeex}.
+%By way of example, a temporal analysis of the constrained worst case analysis is now presented for the example in Section~\ref{sec:brakeex}.
 %
@@
 This is true for all values of $N$ and $y$.
-As noted in Section~\ref{sec:brakeex}, the grid contained 301 time points and the system has 4 types of components,
+As noted in Section~\ref{sec:brakeex}, the grid contains 301 time points and the system has 4 types of components,
 meaning stochastic dominance must be verified via theory or optimisation $1,204$ times for each of $\lRsys(\cdot)$ and $\uRsys(\cdot)$.
@@
 Figure~\ref{fig:need-to-opt-8} shows the worst case probabilities (subject to $|y-p|>0.1$)
-as they change over time in the brake example from the main body of the paper.
+as they change over time in the brake system example. %from the main body of the paper.
 Displayed are the worst case probabilities that optimisation will be required for the choice of prior and the values of $m$ and $N$

### 2016-07-06 coverletter.tex
updated coverletter for resubmission, approaches to get eps figure files if necessary, tidying up

\documentclass[12pt]{letter}

\usepackage[latin1]{inputenc}
\usepackage{url}
\usepackage[bookmarks]{hyperref}

\name{Gero Walter}
\signature{Gero Walter,\\ Louis Aslett,\\ Frank Coolen}
\address{Gero Walter\\ P.O. Box 513\\ 45600 MB Eindhoven\\ The Netherlands\\[2ex] Tel.\ +31 40 247 7316\\ \url{g.m.walter@tue.nl}}
%\telephone{}

\date{06.07.2016}
\location{Eindhoven}

\begin{document}
\longindentation=0pt
\begin{letter}{}
\opening{Dear Editors,}
please find enclosed our revised manuscript for the IJAR Special Issue on Bayesian Nonparametrics,
``Bayesian Nonparametric System Reliability using Sets of Priors''.
We would like to thank you for allowing us to resubmit a few days past the deadline.
We would also like to thank the two anonymous reviewers who provided valuable comments,
and hope that our revised manuscript can be considered for publication.
\closing{Best regards,}
\end{letter}
\end{document}

### 2016-07-06 embedfonts.R

@@ -1,0 +1,12 @@
+# to embed fonts in figure pdfs
+# (trying to avoid redoing all graphs as eps)
+# http://blog.revolutionanalytics.com/2012/09/how-to-use-your-favorite-fonts-in-r-charts.html
+
+#install.packages("extrafont")
+library(extrafont)
+font_import()
+loadfonts()
+
+embed_fonts("need-to-opt-1.pdf") # does not work
+
+#

### 2016-07-06 how-to-make-eps.R

@@ -1,0 +1,22 @@
+# how to make eps files for submission of figures if necessary
+
+# first run this
+library(grDevices)
+# then use the (commented out) lines with "cairo_ps(...)" instead of the "pdf(...)" lines
+# (so far only made for figures in file "pdc-illu.R")
+# NB: simply using postscript(...) does not work for transparency
+
+# figures "singleprior-pdc2" (Fig 1), "betaset-binomset1" (Fig 3) and "paramsets" (Fig 2)
+# are in file "pdc-illu.R".
+
+# Figure 4 is pure tikz, so no pdf/eps file
+
+# figures "bridge-fittingfailures" (Fig 5), "bridge-earlyfailures" (Fig 6)
+# and "bridge-latefailures" (Fig 7)
+# are in file "bridgesystem.R".
+
+# figure "brakingsystem-2" is in file "brakingsystem.R"
+
+# figures "need-to-opt-x", x = 1:8, are in file "need-to-opt.R"
+
+#

### 2016-07-06 need-to-opt-manipulatefig.R

@@ -1,0 +1,37 @@
+p <- seq(0, 1, length.out = 100)
+
+prob.s <- function(y, p, N, m) {
+  pbinom(floor(y*(N+m-1)), N, p) - pbinom(ceiling(y*(N+m-1)-m+1) - 1, N, p)
+}
+prob <- Vectorize(prob.s, "p")
+
+prob2.s <- function(y, p, N, m, n.u, n.l) {
+  s.bad <- NULL
+  for(s in 0:N) {
+    L0 <- (prod(0:(m-1)+n.u*(1-y)+N-s)*prod(0:(m-1)+n.l+N)) /
+      (prod(0:(m-1)+n.l*(1-y)+N-s)*prod(0:(m-1)+n.u+N))
+    Lm <- (prod(0:(m-1)+n.u*y+s)*prod(0:(m-1)+n.l+N)) /
+      (prod(0:(m-1)+n.l*y+s)*prod(0:(m-1)+n.u+N))
+    if(is.nan(Lm) || is.nan(L0) || (!(L0<=1 && Lm>=1) && !(L0>=1 && Lm<=1))) {
+      s.bad <- c(s.bad, s)
+    }
+  }
+  if(length(s.bad)==0)
+    return(0)
+  sum(dbinom(s.bad, N, p))
+}
+prob2 <- Vectorize(prob2.s, "p")
+
+manipulate(
+{
+  plot(p, prob(y, p, N, m), type="l", ylim=c(0,1), ylab="Probability must optimise")
+  points(p, prob2(y, p, N, m, n.u, n.l), type="l", col="red")
+  abline(v = y)
+},
+y = slider(0, 1, step=0.1, initial = 0.1),
+N = slider(5, 100, step=5, initial = 20),
+m = slider(1, 10, initial = 3),
+n.l = slider(1, 20),
+n.u = slider(1, 20, initial = 5)
+)
+

### 2016-07-06 pdc-illu.R

@@ -156,6 +156,7 @@ dev.off()
 betapdfcdf      <- betapdfcdf    + theme(plot.margin = unit(c(0,0.5,0,-0.75), "lines")) + theme_bw()
 pdcillupmfcmf   <- pdcillupmfcmf + theme(plot.margin = unit(c(0,0,  0,-0.75), "lines"),
                                     legend.margin = unit(-0.5, "cm")) + theme_bw()
+#cairo_ps("singleprior-pdc2.eps", width=8, height=5)
 pdf("singleprior-pdc2.pdf", width=8, height=5)
 grid.arrange(betapdfcdf, pdcillupmfcmf, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
@@ -337,6 +338,7 @@ betaset1  <- betaset1 + theme_bw() + theme(plot.margin = unit(c(0,0.5,0,-0.0), "
   guides(linetype="none", fill="none", group="none", colour="none")
 bebinset1 <- bebinset1 + theme_bw() + theme(plot.margin = unit(c(0,0,  0,-0.0), "lines"),
                                          legend.margin = unit(-0.0, "cm"))
+#cairo_ps("betaset-binomset1.eps", width=8, height=5)
 pdf("betaset-binomset1.pdf", width=8, height=5)
 grid.arrange(betaset1, bebinset1, nrow=1, ncol=2, widths=c(1,1.2))
 dev.off()
@@ -381,15 +383,16 @@ paramset2 <- paramset2 + xlab(expression(n^(0))) + ylab(expression(y^(0)))
 paramset2
 
 # plot with parameter sets only
-pdf("paramsets.pdf", width=6, height=5)
-paramset2 + theme(plot.margin = unit(c(0,0.5,0,-0.25), "lines"), legend.margin = unit(-0.5, "cm"))
-dev.off()
+#pdf("paramsets.pdf", width=6, height=5)
+#paramset2 + theme(plot.margin = unit(c(0,0.5,0,-0.25), "lines"), legend.margin = unit(-0.5, "cm"))
+#dev.off()
 
 # in two separate facets
 paramset3 <- ggplot(paramsetdf) + geom_ribbon(aes(x=n0, ymin=Lower, ymax=Upper, group=Item2, colour=Item2, fill=Item2), alpha=0.3)
[…]
